
\let\oldbibitem\bibitem
%\def\bibitem{\vfill\oldbibitem}


%\vspace{1em}

\vspace{2pt}

\begin{thebibliography}{99}


\phantomsection \label{References}
\addcontentsline{toc}{section}{References}
{\fontfamily{lmtt}\fontsize{8}{8}\selectfont

\setlength{\parskip}{0pt}
\setlength{\itemsep}{3.75pt}

\vspace{-4pt}


%!!
%\begin{minipage}{.98\columnwidth}

\bibitem{FedaaAli}{%
Fedaa Ali, \textit{et al.},
\cq{The New SARS-CoV-2 Strain Shows a Stronger Binding Affinity to
ACE2 Due to N501Y Mutation}.
\bibtitle{Briefings in Bioinformatics}, Volume 22, 
ArXiv, 2021.
\biburl{https://arxiv.org/pdf/2101.01791.pdf}}


\bibitem{AliFAlsulami}{%
Ali F. Alsulami, \textit{et al.},
\cq{SARS-CoV-2 3D Database: Understanding
the coronavirus proteome and evaluating
possible drug targets}.
\bibtitle{Briefings in Bioinformatics}, Volume 22, 
Number 2 (2021), pages 769-780.
\biburl{https://academic.oup.com/bib/article-pdf/22/2/769/36655605/bbaa404.pdf}}


\bibitem{DonaldJBenton}{%
Donald J. Benton, \textit{et al.},
\cq{The Effect of the D614G Substitution on the 
Structure of the Spike Glycoprotein of SARS-CoV-2}.
\bibtitle{PNAS}, Volume 118, Number 9 (2021).
\biburl{https://www.pnas.org/content/118/9/e2022586118}}


\bibitem{JCBlader}
JC Blader, \textit{et al.}, 
\cq{Can Keeping Clinical Trial Participants Blind to their Study Treatment 
Adversely Affect Subsequent Care?}
\bibtitle{Contemporary Clinical Trials}, Volume 26, Number 3 (2005), 
pages 290-299.
\biburl{https://europepmc.org/article/med/15911463}


\bibitem{YongfeiCai}{%
Yongfei Cai, \textit{et al.},
\cq{Distinct Conformational States of SARS-CoV-2 Spike Protein}.
\bibtitle{Science}, Volume 369 (2020), pages 1586-1592.
\biburl{https://science.sciencemag.org/content/369/6511/1586}}

 %% anti 
\bibitem{CheMaiChang}{%
Che-Mai Chang, \textit{et al.},
\cq{Profiling of T Cell Repertoire in 
SARS-CoV-2-Infected COVID-19 Patients Between Mild Disease and Pneumonia}.
\bibtitle{Journal of Clinical Immunology}, Volume 41 (2021), pages 1131-1145.
\biburl{https://link.springer.com/article/10.1007/s10875-021-01045-z}}


\bibitem{SandipanChakraborty}
Sandipan Chakraborty, 
\cq{Evolutionary and Structural Analysis Elucidates 
Mutations on SARS-CoV-2 Spike Protein with 
Altered Human ACE2 Binding Affinity}.
\bibtitle{Biochemical and Biophysical Research Communications},
Volume 534 (2021), pages 374-380.
\biburl{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7699163/pdf/main.pdf}


\bibitem{BethanyDearlove}{%
Bethany Dearlove, \textit{et al.},
\cq{A SARS-CoV-2 vaccine candidate would likely match all currently circulating variants
 View ORCID Profile}.
\bibtitle{Proceedings of the National Academy of Sciences}, Volume 117 (2020), 
pages 23652-23662.
\biburl{https://www.pnas.org/content/117/38/23652}}


\bibitem{LiangweiDuan}{%
Liangwei Duan, \textit{et al.},
\cq{The SARS-CoV-2 Spike Glycoprotein Biosynthesis, Structure, Function, and Antigenicity: Implications for the Design of Spike-Based Vaccine Immunogens}.
\bibtitle{Frontiers in Immunology}, 2020.
\biburl{https://www.frontiersin.org/articles/10.3389/fimmu.2020.576622/full}}


\bibitem{KatjaFink}{%
Katja Fink, 
\cq{Can We Improve Vaccine Efficacy by Targeting T and B Cell Repertoire Convergence?}.
\bibtitle{Frontiers in Immunology}, 2019.
\biburl{https://www.frontiersin.org/articles/10.3389/fimmu.2019.00110/full}}


\bibitem{NataliaTFreund}
Natalia T. Freund, \textit{et al.}, 
\cq{Multi-Clonal SARS-CoV-2 Neutralization by Antibodies Isolated 
from Severe COVID-19 Convalescent Donors}.
\bibtitle{PLOS Pathogens}, 2021.
\biburl{https://journals.plos.org/plospathogens/article?id=10.1371/journal.ppat.1009165}


\bibitem{SimonFriedensohn}
Simon Friedensohn, \textit{et al.}, 
\cq{Synthetic Standards Combined With 
Error and Bias Correction Improve the Accuracy and Quantitative 
Resolution of Antibody Repertoire Sequencing in Human Naive and Memory B Cells}.
\bibtitle{Frontiers in Immunology} (special issue on ``B Cell Biology''), 2018.
\biburl{https://www.frontiersin.org/Journal/10.3389/fimmu.2018.01401/full}


\bibitem{JacobDGalson}
Jacob D. Galson, \textit{et al.}, 
\cq{Deep Sequencing of B Cell Receptor Repertoires 
From COVID-19 Patients Reveals Strong Convergent Immune Signatures}.
\bibtitle{Frontiers in Immunology}, 2020.
\biburl{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7769841}


\bibitem{RishiRGoel}
Rishi R. Goel, \textit{et al.}, 
\cq{Distinct Antibody and Memory B Cell Responses in SARS-CoV-2 Naive and Recovered Individuals after mRNA Vaccination}.
\bibtitle{Science Immunology}, Volume 6, Issue 58 (2021).
\biburl{https://immunology.sciencemag.org/content/6/58/eabi6950}


\bibitem{CheolminKim}{%
Cheolmin Kim, \textit{et al.},
\cq{A Therapeutic Neutralizing Antibody Targeting Receptor 
Binding Domain of SARS-CoV-2 Spike Protein}. 
\bibtitle{Nature Communications}, Volume 12 (2021).
\biburl{https://pubmed.ncbi.nlm.nih.gov/33436577}}


\bibitem{BetteKorber}{%
Bette Korber, \textit{et al.},
\cq{Tracking Changes in SARS-CoV-2 Spike: Evidence
that D614G Increases Infectivity of the COVID19 Virus}. 
\bibtitle{Cell}, Volume 182 (2020), pages 812-827.
\biburl{https://www.cell.com/cell/pdf/S0092-8674(20)30820-5.pdf}}


\bibitem{LauraLopezSantibanezJacome}{%
Laura L\'{o}pez-Santib\'{a}\~{n}ez-J\'{a}come, \textit{et al.},
\cq{The Pipeline Repertoire for Ig-Seq Analysis}. 
\bibtitle{Frontiers in Immunology}, 2019.
\biburl{https://www.frontiersin.org/articles/10.3389/fimmu.2019.00899/full}}


\bibitem{AuroreLyon}
Aurore Lyon, \textit{et al.}, 
\cq{Computational Techniques for ECG Analysis and Interpretation in Light of Their Contribution to Medical Advances}.
\bibtitle{Journal of the Royal Society Interface}, Volume 15 (2018).
\biburl{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5805987}


\bibitem{MarksDeane}
Claire Marks and Charlotte M. Deane,  
\cq{How Repertoire Data are Changing Antibody Science}.
\bibtitle{Journal of Biological Chemistry}, Volume 295 (2020), 
pages 9823-9837.
\biburl{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7380193}


\bibitem{IvanMercurio}{%
Ivan Mercurio, \textit{et al.},
\cq{Protein Structure Analysis of the Interactions between SARS-CoV-2 Spike 
Protein and the Human ACE2 receptor: From 
conformational changes to novel neutralizing antibodies}. 
\bibtitle{Cellular and Molecular Life Sciences}, Voume 78, Number 4 (2021), 
pages 1501-1522.
\biburl{https://pubmed.ncbi.nlm.nih.gov/32623480}}


\bibitem{AnastasiaAMinervina}{%
Anastasia A Minervina, \textit{et al.}, 
\cq{Longitudinal High-Throughput TCR Repertoire Profiling Reveals the Dynamics 
of T-Cell Memory Formation after Mild COVID-19 Infection}. 
\bibtitle{eLife}, 2021.
\biburl{https://elifesciences.org/articles/63502}}


\bibitem{AnshumaliMittal}{%
Anshumali Mittal, \textit{et al.}, 
\cq{COVID-19 Pandemic: Insights into structure, 
function, and hACE2 receptor recognition by SARS-CoV-2}. 
\bibtitle{PLOS Pathogens}, 2020.
\biburl{https://journals.plos.org/plospathogens/article?id=10.1371/journal.ppat.1008762}}


\bibitem{AnwarMohammad}{%
Anwar Mohammad, \textit{et al.}, 
\cq{Higher Binding Affinity of Furin for SARS-CoV-2 Spike (S) 
Protein D614G Mutant Could be Associated with Higher SARS-CoV-2
Infectivity.}
\bibtitle{International Journal of Infectious Diseases}, Volume 103 (2021), 
pages 611-616.
\biburl{https://www.ijidonline.com/article/S1201-9712(20)32237-2/pdf}}


\bibitem{HanhTNguyen}{%
Hanh T. Nguyen, \textit{et al.},
\cq{Spike Glycoprotein and Host Cell Determinants of SARS-CoV-2
Entry and Cytopathic Effects}. 
\bibtitle{Journal of Virology}, Voume 95, Issue 5 (2021).
\biburl{https://journals.asm.org/doi/pdf/10.1128/JVI.02304-20}}


\bibitem{XiuyuanOu}{%
Xiuyuan Ou, \textit{et al.}, 
\cq{Characterization of spike glycoprotein of SARS-CoV-2 on virus entry and its immune cross-reactivity with SARS-CoV},
\bibtitle{Nature Communications}, Volume 11 (2020).
\biburl{https://www.nature.com/articles/s41467-020-15562-9}}


\bibitem{VictorPadillaSanchez}{%
Victor Padilla-Sanchez, 
\cq{\i{In Silico} Analysis of SARS-CoV-2 Spike Glycoprotein
and Insights into Antibody Binding},
\bibtitle{Research Ideas and Outcomes}, Volume 6 (2020).
\biburl{https://riojournal.com/article/55281/}}


\bibitem{UtsavPandey}{%
Utsav Pandey, \textit{et al.}, 
\cq{High Prevalence of SARS-CoV-2 Genetic Variation and
D614G Mutation in Pediatric Patients With COVID-19}, 
\bibtitle{Open Forum Infectious Diseases}, Volume 8, 6 (2020). 
\biburl{https://academic.oup.com/brain/advance-article/doi/10.1093/brain/awaa240/5868408}}


\bibitem{SumanPokhrel}{%
Suman Pokhrel, \textit{et al.}, 
\cq{Increased Elastase Sensitivity and Decreased
Intramolecular Interactions in the More 
Transmissible 501Y.V1 and 501Y.V2 SARS-CoV2 Variants' 
Spike Protein -- An \i{in silico} analysis}, 
\bibtitle{PLoS ONE}, Volume 16 (2021). 
\biburl{https://doi.org/10.1371/journal.pone.0251426}}


\bibitem{SupriyaRavichandran}
Supriya Ravichandran, \textit{et al.}, 
\cq{Longitudinal Antibody Repertoire in \q{Mild} Versus \q{Severe} COVID-19 
Patients Reveals Immune Markers Associated with Disease Severity and Resolution}.
\bibtitle{Science Advances}, Volume 7, Number 19 (2021).
\biburl{https://advances.sciencemag.org/content/7/10/eabf2467}


\bibitem{ChristophSchultheiss}{%
Christoph Schulthei\ss{}, \textit{et al.}, 
\cq{Next-Generation Sequencing of T and B Cell Receptor Repertoires from COVID-19 Patients Showed Signatures Associated with Severity of Disease}, 
\bibtitle{Immunity}, Volume 53, Number 2 (2020), pages 442-445. 
\biburl{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7324317}}


\bibitem{OsmanShabir}{%
Osman Shabir,
\cq{The Phylogenetic Tree of the SARS-CoV-2 Virus}.
\bibtitle{News Medical}
\biburl{https://www.news-medical.net/health/The-Phylogenetic-Tree-of-the-SARS-CoV-2-Virus.aspx}}


\bibitem{GentleSunderShrestha}
Gentle Sunder Shrestha, \textit{et al.}, 
\cq{Precision Medicine for COVID-19: A call for better clinical trials}.
\bibtitle{Critical Care}, Volume 24 (2020).
\biburl{https://ccforum.biomedcentral.com/articles/10.1186/s13054-020-03002-5}


\bibitem{GiwanSeo}{%
Giwan Seo, \textit{et al.}, 
\cq{Rapid Detection of COVID-19 Causative Virus
(SARS-CoV-2) in Human Nasopharyngeal
Swab Specimens Using Field-Effect Transistor-Based Biosensor}. 
\bibtitle{ACS Nano}, Volume 14, Number 4 (2020), pages 5135-5142. 
\biburl{https://pubs.acs.org/doi/10.1021/acsnano.0c02823}}


\bibitem{JoshuaBSinger}
Joshua B Singer, \textit{et al.}, 
\cq{GLUE: A flexible software system for virus sequence data}.
\bibtitle{bioRxiv}, 2018.
\biburl{https://www.biorxiv.org/content/10.1101/269274v3.full.pdf}


\bibitem{LizSzabo}{%
Liz Szabo,
\cq{Unraveling the Mysterious Mutations that Make Delta 
the Most Transmissible Covid Virus Yet}.
\bibtitle{Quartz}, 2021.
\biburl{https://qz.com/2039772/why-delta-variant-spreads-twice-as-fast}}


\bibitem{MatthieuVanTilbeurgh}
Matthieu Van Tilbeurgh, \i{et al.}, 
\cq{Predictive Markers of Immunogenicity and Efficacy for Human Vaccines}.
\bibtitle{Vaccines}, Volume 9, Number 6 (2021).
\biburl{https://pubmed.ncbi.nlm.nih.gov/34205932}


\bibitem{MartijnMVanDuijn}
Martijn M. VanDuijn, \i{et al.}, 
\cq{Immune Repertoire after Immunization 
As Seen by Next-Generation Sequencing and Proteomics}.
\bibtitle{Frontiers in Immunology}, 2017.
\biburl{https://www.frontiersin.org/articles/10.3389/fimmu.2017.01286/full}


\bibitem{GennadyMVerkhivker}
Gennady M Verkhivker, \i{et al.}, 
\cq{Landscape-Based Mutational Sensitivity 
Cartography and Network Community Analysis 
of the SARS-CoV-2 Spike Protein Structures: 
Quantifying Functional Effects of the Circulating D614G Variant}.
\bibtitle{ACS Omega}, Volume 6, Number 24 (2021), pages 16216-16233.
\biburl{https://pubmed.ncbi.nlm.nih.gov/34179666}


\bibitem{ErikVolz}
Erik Volz, \i{et al.}, 
\cq{Evaluating the Effects of SARS-CoV-2 
Spike Mutation D614G on Transmissibility and Pathogenicity}.
\bibtitle{Cell}, Volume 184 (2021), pages 64-75.
\biburl{https://www.sciencedirect.com/science/article/pii/S0092867420315373}



\bibitem{WilliamNVoss}
William N. Voss, \i{et al.}, 
\cq{Prevalent, Protective, and Convergent IgG 
Recognition of SARS-CoV-2 Non-RBD Spike Epitopes}.
\bibtitle{Science}, Volume 372 (2021), pages 1108-1112.
\biburl{https://science.sciencemag.org/content/372/6546/1108}


\bibitem{AleksandraMWalczak}
Aleksandra M. Walczak, \i{et al.}, 
\cq{Inferring the Immune Response from Repertoire Sequencing}.
\bibtitle{PLOS Computational Biology}, 2020.
\biburl{https://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1007873}


\bibitem{AlexandraCWalls}
Alexandra C. Walls, \i{et al.}, 
\cq{Structure, Function, and Antigenicity of the SARS-CoV-2 Spike Glycoprotein}.
\bibtitle{Cell}, Volume 184 (2021), pages 64-75.
\biburl{https://www.sciencedirect.com/science/article/pii/S0092867420302622}


\bibitem{YasunoriWatanabe}
Yasunori Watanabe, \i{et al.}, 
\cq{Native-like SARS-CoV-2 Spike Glycoprotein Expressed by 
ChAdOx1 nCoV-19/AZD1222 Vaccine}.
\bibtitle{ACS Central Science}, Volume 7, Number 4 (2021), 
pages 594-602. 
\biburl{https://pubs.acs.org/doi/10.1021/acscentsci.1c00080}


\bibitem{WingerCaspari}
Anna Winger and Thomas Caspari, 
\cq{The Spike of Concern -- The Novel Variants of SARS-CoV-2}.
\bibtitle{Viruses}, Volume 13, Number 6 (2021).
\biburl{https://www.mdpi.com/1999-4915/13/6/1002/pdf}


\bibitem{IanDWolfe}
Ian D. Wolfe, \textit{et al.}, 
\cq{Exploration and Ethical Analysis of 
Open-Label Pediatric Vaccine Trials in a Pandemic}.
\bibtitle{Clinical Therapeutics}, 2021.
\biburl{https://www.sciencedirect.com/science/article/abs/pii/S0149291821002046}


\bibitem{YanlingWu}
Yanling Wu, \textit{et al.}, 
\cq{Deep Mining of Human Antibody Repertoires: 
Concepts, Methodologies, and Applications}.
\bibtitle{Small Methods}, 2020.
\biburl{https://onlinelibrary.wiley.com/doi/full/10.1002/smtd.202000451}


\bibitem{QiongqiongAngelaZhou}
Qiongqiong Angela Zhou, \textit{et al.}, 
\cq{Potential Therapeutic Agents and Associated Bioassay Data for
COVID-19 and Related Human Coronavirus Infections}.
\bibtitle{ACS Pharmacology \& 
Translational Science}, Volume 3, Number 5 (2020), pages 813-834.
\biburl{https://pubs.acs.org/doi/10.1021/acsptsci.0c00074}


\bibitem{LizhouZhang}
Lizhou Zhang, \i{et al.}, 
\cq{SARS-CoV-2 Spike-Protein D614G Mutation Increases 
Virion Spike Density and Infectivity}.
\bibtitle{Nature Communications}, 
Volume 11, Number 1 (2020). 
\biburl{https://pubmed.ncbi.nlm.nih.gov/33243994}


\bibitem{ShiZhao}
Shi Zhao, \i{et al.}, 
\cq{Modelling the Association Between 
COVID-19 Transmissibility and D614G Substitution in SARS-CoV-2 Spike 
Protein: Using the surveillance data in California as an example}.
\bibtitle{Theoretical Biology and Medical Modelling}, 2020. 
\biburl{https://tbiomed.biomedcentral.com/articles/10.1186/s12976-021-00140-3}


\bibitem{GuanghongZuo}
Guanghong Zuo, \textit{et al.}, 
\cq{CVTree: A Parallel Alignment-free Phylogeny and 
Taxonomy Tool based on Composition Vectors of Genomes}.
\bibtitle{bioRxiv}, 2021.
\biburl{https://www.biorxiv.org/content/10.1101/2021.02.04.429726v1.full.pdf}



\vfill{}

%\end{minipage}



}
\end{thebibliography}

