
\let\oldbibitem\bibitem
%\def\bibitem{\vfill\oldbibitem}


%\vspace{1em}

\vspace{-10pt}

\begin{thebibliography}{99}
\phantomsection \label{References}
\addcontentsline{toc}{section}{References}
{\fontfamily{lmtt}\fontsize{8}{8}\selectfont

\setlength{\parskip}{0pt}
\setlength{\itemsep}{3.75pt}

\vspace{13pt}


\begin{minipage}{.97\columnwidth}

\bibitem{DavidAClunie}
David A. Clunie, 
\cq{DICOM Structured Reporting}.
\biburl{http://www.dclunie.com/pixelmed/DICOMSR.book.pdf}


\bibitem{AndreasFabri}
Andreas Fabri, \i{et al.},
\cq{On the Design of CGAL, the Computational Geometry Algorithms Library}.
Max Planck Institute, 1998.
\biburl{https://core.ac.uk/download/pdf/210674597.pdf}


\bibitem{DavidJuncker}
David Juncker, \textit{et al.}, 
\cq{Multipurpose Microfluidic Probe}.
\bibtitle{Nature Materials}, Volume 4, Issue 8 (2005), pages 622-628.
\biburl{https://pubmed.ncbi.nlm.nih.gov/16041377/}


\bibitem{AdityaKashyap}
Aditya Kashyap, \i{et al.}, 
\cq{Quantitative Microimmunohistochemistry for the Grading of Immunostains on Tumour Tissues}.
\bibtitle{Nature Biomedical Engineering}, Volume 3 (2019), pages 478-490.
\biburl{https://www.nature.com/articles/s41551-019-0386-3}


\bibitem{RobertLeif}
Robert C. Leif,  
\cq{CytometryML with DICOM and FCS}.
\bibtitle{SPIE} (International Society for Optics 
and Photonics), Proceedings (2018).
\biburl{https://spie.org/Publications/Proceedings/Paper/10.1117/12.2295220?SSO=1}


\bibitem{LovchikEtAl}
Robert D. Lovchik, \textit{et al.}, 
\cq{Rapid Micro-Immunohistochemistry}.
\bibtitle{Microsystems \& Nanoengineering}, Volume 6 (2020).
\biburl{https://www.nature.com/articles/s41378-020-00205-2.pdf}  


\bibitem{PattanasakMongkolwat}
Pattanasak Mongkolwat, \i{et al.}, 
\cq{The National Cancer Informatics Program (NCIP) Annotation
and Image Markup (AIM) Foundation Model}
\bibtitle{Journal of Digit Imaging}, Volume 27 (2014), pages 692-701.
\biburl{https://europepmc.org/backend/ptpmcrender.fcgi?accid=PMC4391072&blobtype=pdf}



% biomarkers ...
%\bibitem{JamesOConnor}
%James O'Connor, \textit{et al.}, 
%\cq{Imaging tumour hypoxia with oxygen-enhanced MRI
%and BOLD MRI}.
%\bibtitle{British Journal of Radiolology}  
%Volume 92 (2019).
%\biburl{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6540855/pdf/bjr.20180642.pdf}

\bibitem{ODonnellEtAl}
Erika A O'Donnell, \textit{et al.}, 
\cq{Multiparameter Flow Cytometry: Advances in High Resolution
Analysis}.
\bibtitle{Immune Network}, Volume 13, Number 2 (2013), pages 43-54.
\biburl{https://www.immunenetwork.org/pdf/10.4110/in.2013.13.2.43}  


\bibitem{ParadowskiEtAl}
Mariusz Paradowski, \i{et al.},
\cq{Capillary Blood Vessel Tracking Using Polar Coordinates Based Model Identification}.
\bibtitle{Computer Recognition Systems}, Volume 3, pages 499-50.
\biburl{https://link.springer.com/chapter/10.1007/978-3-540-93905-4_59}


\bibitem{ThomasMPearce}
Thomas M. Pearce, \textit{et al.}, 
\cq{Integrated Microelectrode Array and Microfluidics for Temperature Clamp 
of Sensory Neurons in Culture}.
\bibtitle{Lab on a Chip}, 2005, Issue 5, pages 97-101.
\biburl{https://pubs.rsc.org/en/content/articlehtml/2005/lc/b407871c}


\bibitem{QasaimehEtAl}
Mohammad A. Qasaimeh, \textit{et al.}, 
\cq{Microfluidic Probes for Use in Life Sciences and Medicine}.
\bibtitle{Lab on a Chip}, 2013, Issue 1.
\burl{https://pubs.rsc.org/en/content/articlelanding/2013/lc/c2lc40898h}


\bibitem{KentaShinha}
Kenta Shinha, \textit{et al.}, 
\cq{A Microfluidic Probe Integrated Device for
Spatiotemporal 3D Chemical Stimulation in Cells}
\bibtitle{IEEE Transactions on Visualization and Computer Graphics}, 2021.
\biburl{https://www.mdpi.com/2072-666X/11/7/691}


\bibitem{ATraverso}
A. Traverso, \i{et al.}, 
\cq{FAIR Quantitative Imaging in Oncology: How Semantic
Web and Ontologies will support reproducible science}.
\biburl{http://ceur-ws.org/Vol-2849/paper-14.pdf}


\bibitem{JohanVanSoest}
Johan Van Soest, \i{et al.}, 
\cq{Towards a semantic PACS: Using Semantic Web technology to represent imaging data}.
\bibtitle{Studies in Health Technology and Informatics}, Volume 205 
(2014), pages 166-179, 
\biburl{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5119276/}


\bibitem{Vining}
David J. Vining, \i{et al.}, 
\cq{Development of the ViSion Ontology}.
\biburl{https://www.semanticscholar.org/paper/Development-of-the-Vision-Ontology.-Vining-Salem/84201e9bd58348bcc5356e0c154a629cc524c778}


\bibitem{WangHoffman}
Lili Wang and Robert A. Hoffman, \i{et al.}, 
\cq{Standardization, Calibration, and Control in Flow Cytometry}.
\bibtitle{Current Protocols in Cytometry},
Voume 79 (2017).
\biburl{https://tsapps.nist.gov/publication/get_pdf.cfm?pub_id=921423}


\bibitem{EdyWijaya}
Edy Wijaya, \i{et al.},
\cq{Surface Plasmon Resonance-Based Biosensors: From the development of different
SPR structures to novel surface functionalization strategies}.
\bibtitle{Current Opinion in Solid State and Materials Science}, 
Volume 15, Issue 5 (2011), pages 208-224.
\biburl{http://www.ffh.bg.ac.rs/wp-content/uploads/2017/05/Wijaya.pdf}







\vfill{}

\end{minipage}


}
\end{thebibliography}



