
\let\oldbibitem\bibitem
%\def\bibitem{\vfill\oldbibitem}


%\vspace{1em}

\vspace{6pt}

\begin{thebibliography}{99}
\phantomsection \label{References}
\addcontentsline{toc}{section}{References}
{\fontfamily{lmtt}\fontsize{8}{8}\selectfont

\setlength{\parskip}{0pt}
\setlength{\itemsep}{3.75pt}

\vspace{12pt}

\begin{minipage}{.98\columnwidth}

\bibitem{RaubalAdams}
Benjamin Adams and Martin Raubal, 
\cq{A Metric Conceptual Space Algebra}.
\bibtitle{International Conference on Spatial Information Theory}, 
2009, Proceedings, pages 51-68.
\biburl{https://pdfs.semanticscholar.org/521a/cbab9658df27acd9f40bba2b9445f75d681c.pdf}


\bibitem{BleekerEtAl}
Elli Bleeker, \textit{et al.},
\cq{Between Flexibility and Universality: Combining TAGML
and XML to Enhance the Modeling of Cultural Heritage
Text}.
\biburl{http://ceur-ws.org/Vol-2723/short39.pdf}


\bibitem{MeHBTT}
Nathaniel Christen, 
\cq{Hypergraph Type Theory for 
Specifications-Conformant Code and 
Generalized Lambda Calculus}.
In Amy Neustein (Ed.),  \intitle{Advances in Ubiquitous Computing: Cyber-Physical Systems, Smart Cities, and Ecological Monitoring} (Elsevier 2019). 



\bibitem{InteractingConceptualSpaces}
Bob Coecke, \i{et al.}, 
\cq{Interacting Conceptual Spaces I:
Gram\-matical Composition of Concepts}.
Extended version of \intitle{Proceedings of
the 2016 Workshop on Semantic Spaces at the 
Intersection of NLP, Physics and Cognitive Science}, 
pages 11-19.
\biburl{https://arxiv.org/pdf/1703.08314.pdf}



\bibitem{IvanCukic}
Ivan \v{C}uki\'{c},  
\cq{Functional and Imperative Reactive Programming Based on a 
Generalization of the Continuation Monad in the C++ Programming Language}.
Dissertation, University of Belgrade, 2018.
\biburl{http://www.math.rs/files/ivan-cukic-phd.pdf}



\bibitem{DonglinDi}
Donglin Di, \textit{et al.}, 
\cq{Hypergraph Learning for Identification of COVID-19 with CT Imaging}.
\bibtitle{Medical Image Analysis}, Volume 68 (2021).
\biburl{https://pubmed.ncbi.nlm.nih.gov/33285483}


\bibitem{ToniFarley}
Toni Farley, \textit{et al.}, 
\cq{The BioIntelligence Framework: A new computational platform for biomedical knowledge computing}.
\bibtitle{Journal of the American Medical Informatics Association 
(JAMIA)}, Volume 20, Number 1 (2013), pages 128-133.
\biburl{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3555311}


\bibitem{EricaMarcos}
Erica Marcos, \textit{et al.}, 
\cq{The Ontology of Vaccine Adverse Events (OVAE) and its Usage in 
Representing and Analyzing Adverse Events Associated with US-Licensed Human Vaccines}.
\bibtitle{Journal of Biomedical Semantics}, Volume 4 (2013).
\biburl{https://jbiomedsem.biomedcentral.com/articles/10.1186/2041-1480-4-40}



\end{minipage}
}
\end{thebibliography}


