
\let\oldbibitem\bibitem
%\def\bibitem{\vfill\oldbibitem}


%\vspace{1em}

\vspace{-10pt}

\begin{thebibliography}{99}
\phantomsection \label{References}
\addcontentsline{toc}{section}{References}
{\fontfamily{lmtt}\fontsize{8}{8}\selectfont

\setlength{\parskip}{0pt}
\setlength{\itemsep}{3.75pt}

\vspace{13pt}


\begin{minipage}{\columnwidth}
\bibitem{RaubalAdams}
Benjamin Adams and Martin Raubal, 
\cq{A Metric Conceptual Space Algebra}.
\biburl{https://pdfs.semanticscholar.org/521a/cbab9658df27acd9f40bba2b9445f75d681c.pdf}


\bibitem{RaubalAdamsCSML}
\_\_\_\_\_, %Benjamin Adams and Martin Raubal, 
\cq{Conceptual Space Markup Language (CSML): Towards the Cognitive Semantic Web}.
\biburl{http://idwebhost-202-147.ethz.ch/Publications/RefConferences/ICSC_2009_AdamsRaubal_Camera-FINAL.pdf}



\bibitem{ECL}
Giuseppe Attardi,
\cq{The Embeddable Common Lisp}
\biburl{https://common-lisp.net/project/ecl/static/files/papers/ecl-1995-attardi.pdf}

\bibitem{LucasBechberger}
Lucas Bechberger and Kai-Uwe K\"uhnberger, %\_\_\_\_\_, %Lucas Bechberger and Kai-Uwe K\"uhnberger, 
\cq{Measuring Relations between Concepts in Conceptual Spaces}.%
\biburl{https://arxiv.org/pdf/1707.02292.pdf}


\bibitem{Cazzola}
Walter Cazzola, \textit{et al.},
\cq{Semantic Join Point Models:
Motivations, Notions and Requirements}
\biburl{https://hal.inria.fr/inria-00542782/document}


\bibitem{ChanninEtAl}
David S. Channin, \i{et al.}, 
\cq{The caBIG Annotation and Image Markup Project}.
\bibtitle{Journal of Digit Imaging}, Volume 23, 
Number 2 (2010), pages 217-225.
\biburl{https://pubmed.ncbi.nlm.nih.gov/19294468/}



\bibitem{BobCoecke}
Bob Coecke,  
\cq{The Mathematics of Text Structure}.
\biburl{https://arxiv.org/pdf/1904.03478.pdf}



\bibitem{InteractingConceptualSpaces}
Bob Coecke, \i{et al.}, 
\cq{Interacting Conceptual Spaces I:
Gram\-matical Composition of Concepts}.
Extended version of \intitle{Proceedings of
the 2016 Workshop on Semantic Spaces at the 
Intersection of NLP, Physics and Cognitive Science}, 
pages 11-19.
\biburl{https://arxiv.org/pdf/1703.08314.pdf}



\bibitem{DebusmannEtAl}
Ralph Debusmann, \i{et al.},  
\cq{A Relational Syntax-Semantics Interface Based on Dependency Grammar}
\biburl{https://www.aclweb.org/anthology/C04-1026.pdf}


\bibitem{KeithDevlin}
Keith Devlin,
\cq{Situation Theory and Situation Semantics}



\bibitem{JerryFodor}
Jerry Fodor, 
\cq{Language, Thought and Compositionality}.
\bibtitle{Mind and Language}, Volume 16, Issue 1 (2001)
\biburl{https://onlinelibrary.wiley.com/doi/abs/10.1111/1468-0017.00153}



\bibitem{FriedOstman}
Mirjam Fried and Jan-Ola \"Ostman, 
\cq{Construction Grammar: A thumbnail sketch}
\biburl{https://www.researchgate.net/publication/280291354_Construction_Grammar_A_thumbnail_sketch}


\bibitem{GallegoOrus}
\'Angel J. Gallego and Rom\'an Or\'us, 
\cq{Language Design as Information Renormalization}.
\biburl{https://arxiv.org/abs/1708.01525}



\bibitem{GardenforsEtAl}
Peter \Gardenfors{}, \i{et al.},
\cq{Event Boards as Tools for Holistic AI}.
\biburl{http://ceur-ws.org/Vol-2418/paper1.pdf}


\bibitem{Zenker}
Peter \Gardenfors{} and Frank Zenker,  
\cq{Theory Change as Dimensional Change: Conceptual Spaces 
	Applied to the Dynamics of Empirical Theories}.
\bibtitle{Synthese 190}, Volume 6 (2013), pages. 1039-1058.  
\biburl{http://lup.lub.lu.se/record/1775234}



\bibitem{GayoEtAl}
Jose Emilio Labra Gayo, \i{et al.}, 
\cq{Validating and Describing Linked Data Portals using
Shapes}.%
\biburl{https://arxiv.org/pdf/1701.08924.pdf}

\bibitem{JosephGoguen}
Joseph Goguen, 
\cq{An Introduction to Algebraic Semiotics, with Application to User Interface Design}.
In Nehaniv, C. (ed.), 
\intitle{Computation for Metaphors, Analogy, and Agents}, Springer, 1999, pages 242-9.%
\biburl{https://cseweb.ucsd.edu/~goguen/pps/as.pdf}

\bibitem{PaulaGudwin}
Suelen M. de Paula and Ricardo R. Gudwin,   
\cq{Evolving Conceptual Spaces for Symbol Grounding in
Language Games}.
\bibtitle{Biologically Inspired Cognitive Architectures},
Volume 14 (2015), pages 73-85.
\biburl{https://www.sciencedirect.com/science/article/pii/S2212683X15000493}

\bibitem{GustUmbach}
Helmar Gust and Carla Umbach,
\cq{A Qualitative Similarity Framework for the
Interpretation of Natural Language Similarity
Expressions}.
In Lucas Bechberger, \i{et al.} (Eds.),
\intitle{Concepts in Action -- Representation, Learning, and Application}, 
Springer 2021.
\biburl{http://www.carla-umbach.de/publications/Gust&Umbach_QualitativeSimilarityFramework.pdf}

\bibitem{ThomasHartmann}
Thomas Hartmann,
\cq{Validation Framework for RDF-based Constraint Languages}
Dissertation, Karlsruhe, 2016.
\biburl{https://www.semanticscholar.org/paper/Validation-Framework-for-RDF-based-Constraint-Hartmann/aff416d1e971fb55ea405a1967619263fbe8be9e}


\bibitem{RamsonHirschfeld}
Stefan Ramson and Robert Hirschfeld,
\bibtitle{Active Expressions: Basic Building Blocks for Reactive Programming}.
\biburl{https://arxiv.org/abs/1703.10859}


\bibitem{HovavLevin}
Malka Rappaport Hovav and Beth Levin,  
\cq{The Syntax-Semantics Interface}.
In Shalom Lappin and Chris Fox (Eds.), 
\intitle{The Handbook of Contemporary Semantic Theory},
Wiley 2015, chapter 19, pages 593-624.
\biburl{https://onlinelibrary.wiley.com/doi/pdf/10.1002/9781118882139.ch19}



\bibitem{CorentinJabot}
Corentin Jabot, 
\cq{Strongly-Typed Reflection on Attributes}
\biburl{http://open-std.org/JTC1/SC22/WG21/docs/papers/2019/p1887r0.pdf}

\bibitem{WolfgangJeltsch}
Wolfgang Jeltsch, 
\bibtitle{Categorical Semantics for Functional Reactive 
Programming with Temporal Recursion and Corecursion}.
\tinyurl{https://arxiv.org/pdf/1406.2062.pdf}

\end{minipage}
%\begin{minipage}{\columnwidth}


\begin{minipage}{\columnwidth}
\bibitem{KloseOstermann}
Karl Klose and Klaus Ostermann,
\cq{A Classification Framework for Pointcut
Languages in Runtime Monitoring}.
\biburl{https://link.springer.com/chapter/10.1007/978-3-642-02571-6_17}

\bibitem{MichaelisLambrech}
Laura A. Michaelis and Knud Lambrech, \cq{Toward a Construction-Based Theory of Language Function: The Case of Nominal Extraposition}
\biburl{https://spot.colorado.edu/~michaeli/documents/Michaelis_Lambrecht_NE_LG.pdf}


%\bibitem{KohliEtAl}
%Mark D. Kohli, \i{et al.},
%\cq{Medical Image Data and Datasets in the Era of Machine
%Learning --- Whitepaper from the 2016 C-MIMI Meeting}
%\bibtitle{Journal of Digit Imaging}, 2017.
%\biburl{https://d-nb.info/1132883164/34}


\bibitem{KorenblumEtAl}
Daniel Korenblum, \i{et al.}, 
\cq{Managing Biomedical Image Metadata for Search and Retrieval
of Similar Images}.
\bibtitle{Journal of Digital Imaging}, Volume 24, Number 4 (2011), 
pages 739-748.
\biburl{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3138941/}


\bibitem{KubotaLevine}
Yusuke Kubota and Robert Levine,
\cq{The Syntax-Semantics Interface of \sq{Respective} Predication:
A unified analysis in Hybrid Type-Logical Categorial Grammar}
\biburl{https://www.asc.ohio-state.edu/levine.1/publications/kl-resp.pdf}

%\end{minipage}

%\setlength{\itemsep}{6pt}

%\vspace{1em}
%\begin{minipage}{\columnwidth}

%\vspace{3pt}

\bibitem{LawryTang}
Jonathan Lawry and Yongchuan Tang, 
\cq{Uncertainty Modelling for Vague Concepts: A prototype theory approach}.  
\biburl{https://www.sciencedirect.com/science/article/pii/S0004370209000903}


\bibitem{LewisLawry}
Martha Lewis and Jonathan Lawry, 
\cq{Hierarchical Conceptual Spaces for Concept Combination}.  
\biburl{https://www.sciencedirect.com/science/article/pii/S0004370216300492}

\bibitem{LiCunningham}
Yaoyong Li and Hamish Cunningham, 
\cq{Geometric and Quantum Methods for
Information Retrieval}.  
In \intitle{Association for Computing Machinery Forum}, New York, 
Volume 42, Number 2, 2008, pages 22-32.
\biburl{https://dl.acm.org/doi/10.1145/1480506.1480510}



\bibitem{IlyaMakarov}
Ilya Makarov, \i{et al.},
\cq{Quantum Logic and Natural Language Processing}.  
\biburl{http://ceur-ws.org/Vol-1886/paper_16.pdf}


\bibitem{Meichanetzidis}
Konstantinos Meichanetzidis, \i{et al.}, 
\cq{Quantum Natural Language Processing on Near-Term Quantum Computers}
\biburl{https://arxiv.org/abs/2005.04147}


\bibitem{FriederikeMoltmann}
Friederike Moltmann, 
\cq{Parts and Wholes in Semantics}.
Oxford University Press, 1997.\biburl{https://www.researchgate.net/publication/244487318}


%`cite<DanielLRubin>;,  `cite<KohliEtAl>;,

\bibitem{PattanasakMongkolwat}
Pattanasak Mongkolwat, \i{et al.}, 
\cq{The National Cancer Informatics Program (NCIP) Annotation
and Image Markup (AIM) Foundation Model}
\bibtitle{Journal of Digit Imaging}, Volume 27 (2014), pages 692-701.
\biburl{https://europepmc.org/backend/ptpmcrender.fcgi?accid=PMC4391072&blobtype=pdf}



\bibitem{LJOriordon}
Lee J O'Riordan, \i{et al.},
\cq{A Hybrid Classical-Quantum Workflow for 
Natural Language Processing}.
Machine Learning: Science and Technology, Volume 2 (2021).
\biburl{https://iopscience.iop.org/article/10.1088/2632-2153/abbd2e/pdf}

\bibitem{ParetiEtAl}
Paolo Pareti, \i{et al.}, 
\cq{SHACL Constraints with Inference Rules
Paolo Pareti}.
In C. Ghidini, \i{et al.} (Eds.),
\intitle{International Semantic Web Conference 2019}, 
pages 539–557.
\biburl{https://www.southampton.ac.uk/~gk1e17/shacl-inference.pdf}

\bibitem{WalterPedriali}
Walter B. Pedriali, 
\cq{The Routes of Sense: Thought, semantic inderdeterminacy and compositionality}.
Dissertation, St. Andrews University, 2011.
\biburl{https://research-repository.st-andrews.ac.uk/handle/10023/3142}

\bibitem{MartinRaubal}
Martin Raubal,
\cq{Formalizing Conceptual Spaces}.
\biburl{http://www.raubal.ethz.ch/Courses/288MR_Spring08_Papers/Raubal_FormalizingConceptualSpaces_FOIS04.pdf}


%\end{minipage}

%\begin{minipage}{\columnwidth}

%\end{minipage}

% or https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3138941/pdf/10278_2010_Article_9328.pdf ??

%\bibitem{DanielLRubin}
%Daniel L. Rubin, 
%\cq{Finding the Meaning in Images: Annotation and Image Markup}.
%\bibtitle{Philosophy, Psychiatry, & Psychology}, Volume 18, Number 4 (2011), pages 311-318.
%\biburl{https://web.stanford.edu/group/rubinlab/pubs/18.4.rubin.pdf}

\bibitem{RubinSupekar}
Daniel L. Rubin and Kaustubh Supekar, 
\cq{Annotation and Image Markup: Accessing and Interoperating 
with the Semantic Content in Medical Imaging}.
\bibtitle{Intelligent Systems}, Volume 24, Number 1 (2009), pages 57-65.
\biburl{https://web.stanford.edu/group/rubinlab/pubs/Rubin-IEEEIntelSys-2009.pdf}


\bibitem{VahidSalari}
Vahid Salari, \i{et al.}, 
\cq{Parametrized Quantum Circuits of Synonymous
Sentences in Quantum Natural Language
Processing}.\biburl{https://assets.researchsquare.com/files/rs-220713/v1_stamped.pdf}



\bibitem{Schafmeister}
Christian Schafmeister and Alex Wood,
\cq{Clasp Common Lisp Implementation and Optimization}.
\biburl{https://dl.acm.org/doi/10.5555/3323215.3323223}

\bibitem{SchaerEtAl}
Roger Schaer, \i{et al.},
\cq{Web-Based Tools for Exploring the Potential of Quantitative Imaging
Biomarkers in Radiology: 
Intensity and Texture Analysis on the ePAD Platform}.
In Adrien Depeursinge, \i{et al.} (Eds), 
\intitle{Biomedical Texture Analysis: Fundamentals, 
Tools, and Challenes}, Academic Press, 2017.
\biburl{http://bigwww.epfl.ch/publications/schaer1701.pdf}


\bibitem{teleaVission}
Alexandru Telea and Jarke J. van Wijk,
\cq{VISSION: An Object Oriented Dataflow System for Simulation and Visualization}.
\biburl{https://pure.rug.nl/ws/portalfiles/portal/3178139/1999ProcVisSymTelea.pdf}


\bibitem{UrbanGrzelinska}
Roman Urban and Megdalena Grzelinska, 
\cq{A Potential Theory Approach to an Algorithm of Conceptual
Space Partitioning}.  In 
\intitle{Cognitive Studies}, Volume 1 (2017).
\biburl{https://ispan.waw.pl/journals/index.php/cs-ec/article/download/cs.1310/3065}


\bibitem{JuanUriagereka}
Juan Uriagereka, 
\cq{Syntactic Anchors: On Semantic Structuring}.
Cambridge University Press, 2008.
\biburl{https://assets.cambridge.org/97805218/65326/frontmatter/9780521865326_frontmatter.pdf}

\bibitem{vanTrijp}
Remi van Trijp, 
\cq{Cognitive vs. Generative Construction
Grammar: The case of coercion and
argument structure}.  
\bibtitle{Cognitive Linguistics}, Volime 26, Issue 4 (2015), pages 613-632.
\biburl{https://www.degruyter.com/document/doi/10.1515/cog-2014-0074/html}


\bibitem{FrankZenker}
Frank Zenker,
\cq{From Features via Frames to Spaces: Modeling Scientific Conceptual Change Without Incommensurability or Aprioricity}.
In Thomas Gamerschlag, \i{et al.} (Eds.), 
\intitle{Frames and Concept Types: Applications in Language and Philosophy}, 
Springer, 2014, pages 69-89.  
\biburl{https://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.901.7852&rep=rep1&type=pdf}
\end{minipage}{\columnwidth}




\end{minipage}{\columnwidth}



\vfill{}




}
\end{thebibliography}
