
\let\oldbibitem\bibitem
%\def\bibitem{\vfill\oldbibitem}


%\vspace{1em}

\vspace{-7pt}

\begin{thebibliography}{99}
\phantomsection \label{References}
\addcontentsline{toc}{section}{References}
{\fontfamily{lmtt}\fontsize{8}{8}\selectfont

\setlength{\parskip}{0pt}
\setlength{\itemsep}{3.75pt}

\vspace{12pt}


\begin{minipage}{\columnwidth}
\bibitem{RaubalAdams}
Benjamin Adams and Martin Raubal, 
\cq{A Metric Conceptual Space Algebra}.
\bibtitle{International Conference on Spatial Information Theory}, 
2009, Proceedings, pages 51-68.
\biburl{https://pdfs.semanticscholar.org/521a/cbab9658df27acd9f40bba2b9445f75d681c.pdf}


\bibitem{RaubalAdamsCSML}
\_\_\_\_\_, %Benjamin Adams and Martin Raubal, 
\cq{Conceptual Space Markup Language (CSML): Towards the Cognitive Semantic Web}.
\bibtitle{IEEE International Conference on Semantic Computing}, 2009, 
Proceedings, pages 51-68.
\biburl{https://ieeexplore.ieee.org/document/5298627}

\bibitem{ECL}
Giuseppe Attardi,
\cq{The Embeddable Common Lisp}
\bibtitle{ACM SIGPLAN Lisp Pointers}, Volume 8, Issue 1 (1995), pages 30-41. 
\biburl{https://common-lisp.net/project/ecl/static/files/papers/ecl-1995-attardi.pdf}


\bibitem{SikhaBagui}
Sikha Bagui,
\cq{Achievements and Weaknesses of Object-Oriented Databases}
\bibtitle{Journal of Object Technology}, 2003. 
\biburl{http://www.jot.fm/issues/issue_2003_07/column2.pdf}


\bibitem{LucasBechberger}
Lucas Bechberger and Kai-Uwe K\"uhnberger, %\_\_\_\_\_, %Lucas Bechberger and Kai-Uwe K\"uhnberger, 
\cq{Measuring Relations between Concepts in Conceptual Spaces}.%
\bibtitle{SGAI International Conference on Artificial Intelligence}, 2017.
\biburl{https://arxiv.org/pdf/1707.02292.pdf}


\bibitem{Cazzola}
Walter Cazzola, \textit{et al.},
\cq{Semantic Join Point Models:
Motivations, Notions and Requirements}.
\bibtitle{Software Engineering Properties of Languages and Aspect
Technologies}, 2006, Proceedings.
\biburl{https://hal.inria.fr/inria-00542782/document}


\bibitem{ChanninEtAl}
David Channin, \i{et al.}, 
\cq{The caBIG Annotation and Image Markup Project}.
\bibtitle{Journal of Digit Imaging}, Volume 23%
%, Number 2 
(2010), pages 217-225.%
\hspace{-1pt}\biburl{https://pubmed.ncbi.nlm.nih.gov/19294468}


\bibitem{BobCoecke}
Bob Coecke,  
\cq{The Mathematics of Text Structure}.
\biburl{https://arxiv.org/pdf/1904.03478.pdf}



\end{minipage}

\begin{minipage}{.98\columnwidth}



\bibitem{InteractingConceptualSpaces}
Bob Coecke, \i{et al.}, 
\cq{Interacting Conceptual Spaces I:
Gram\-matical Composition of Concepts}.
Extended version of \intitle{Proceedings of
the 2016 Workshop on Semantic Spaces at the 
Intersection of NLP, Physics and Cognitive Science}, 
pages 11-19.
\biburl{https://arxiv.org/pdf/1703.08314.pdf}



\bibitem{DebusmannEtAl}
Ralph Debusmann, \i{et al.},  
\cq{A Relational Syntax-Semantics Interface Based on Dependency Grammar}.
\bibtitle{20th International Conference on Computational Linguistics}, 
Proceedings, 2004.
\biburl{https://www.aclweb.org/anthology/C04-1026.pdf}


\bibitem{KeithDevlin}
Keith Devlin,
\cq{Situation Theory and Situation Semantics}.
\bibtitle{Handbook of the History of Logic}, 
Volume 7 (2006), pages 601-664.
\biburl{https://web.stanford.edu/~kdevlin/Papers/HHL_SituationTheory.pdf}


\bibitem{HongEisner}
Juneki Hong and Jason Eisner,
\cq{Deriving Multi-Headed Planar Dependency Parses
from Link Grammar Parses}.
\biburl{https://www.cs.jhu.edu/~jason/papers/hong+eisner.tlt14.paper.pdf}



\bibitem{JerryFodor}
Jerry Fodor, 
\cq{Language, Thought and Compositionality}.
\bibtitle{Mind and Language}, Volume 16, Issue 1 (2001)
\biburl{https://onlinelibrary.wiley.com/doi/abs/10.1111/1468-0017.00153}



\bibitem{FriedOstman}
Mirjam Fried and Jan-Ola \"Ostman, 
\cq{Construction Grammar: A thumbnail sketch}.
In Mirjam Fried and Jan-Ola \"Ostman, Eds., \intitle{Construction Grammar in a Cross-Language Perspective} (John Benjamins, 2004),
pages 11-86.
\biburl{https://www.researchgate.net/publication/280291354_Construction_Grammar_A_thumbnail_sketch}


\bibitem{GallegoOrus}
\'Angel J. Gallego and Rom\'an Or\'us, 
\cq{Language Design as Information Renormalization}.
\biburl{https://arxiv.org/abs/1708.01525}



\bibitem{GardenforsEtAl}
Peter \Gardenfors{}, \i{et al.},
\cq{Event Boards as Tools for Holistic AI}.
\bibtitle{6th International Workshop on Artificial Intelligence and Cognition}, 
2019, pages 1-10.
\biburl{http://ceur-ws.org/Vol-2418/paper1.pdf}


\bibitem{Zenker}
Peter \Gardenfors{} and Frank Zenker,  
\cq{Theory Change as Dimensional Change: Conceptual Spaces 
	Applied to the Dynamics of Empirical Theories}.
\bibtitle{Synthese 190}, Volume 6 (2013), pages. 1039-1058.  
\biburl{http://lup.lub.lu.se/record/1775234}



\bibitem{GayoEtAl}
Jose Emilio Labra Gayo, \i{et al.}, 
\cq{Validating and Describing Linked Data Portals using
Shapes}%
\hspace{-.4em}\biburl{https://arxiv.org/pdf/1701.08924.pdf}

\bibitem{JosephGoguen}
Joseph Goguen, 
\cq{An Introduction to Algebraic Semiotics, with Application to User Interface Design}.
In Nehaniv, C. (ed.), 
\intitle{Computation for Metaphors, Analogy, and Agents}, Springer, 1999, pages 242-9.%
\biburl{https://cseweb.ucsd.edu/~goguen/pps/as.pdf}

\bibitem{PaulaGudwin}
Suelen M. de Paula and Ricardo R. Gudwin,   
\cq{Evolving Conceptual Spaces for Symbol Grounding in
Language Games}.
\bibtitle{Biologically Inspired Cognitive Architectures},
Volume 14 (2015), pages 73-85.
\biburl{https://www.sciencedirect.com/science/article/pii/S2212683X15000493}

\bibitem{GustUmbach}
Helmar Gust and Carla Umbach,
\cq{A Qualitative Similarity Framework for the
Interpretation of Natural Language Similarity
Expressions}.
In Lucas Bechberger, \i{et al.} (Eds.),
\intitle{Concepts in Action -- Representation, Learning, and Application}, 
Springer 2021.
\biburl{http://www.carla-umbach.de/publications/Gust&Umbach_QualitativeSimilarityFramework.pdf}

\bibitem{ThomasHartmann}
Thomas Hartmann,
\cq{Validation Framework for RDF-based Constraint Languages}.
Dissertation, Karlsruhe, 2016.
\biburl{https://publikationen.bibliothek.kit.edu/1000056458/3865145}


\bibitem{RadekKoci}
Radek Ko\v{c}\'{\OldI}, \i{et al.},
\cq{Object Oriented Petri Nets -- Modelling Techniques Case Study}.
\bibtitle{Second UKSIM European Symposium on Computer Modeling and Simulation}, 
2008.
\biburl{https://ijssst.info/Vol-10/No-3/paper4.pdf}


\bibitem{KohlerRolke}
Michael K\"ohler and Heiko R\"olke,  
\cq{Properties of Object Petri Nets}.
\bibtitle{International Conference on Application and Theory of Petri Nets},
2004, pages 278-297.
\biburl{https://link.springer.com/chapter/10.1007/978-3-540-27793-4_16}


\bibitem{HovavLevin}
Malka Rappaport Hovav and Beth Levin,  
\cq{The Syntax-Semantics Interface}.
In Shalom Lappin and Chris Fox (Eds.), 
\intitle{The Handbook of Contemporary Semantic Theory},
Wiley 2015, chapter 19, pages 593-624.
\biburl{https://onlinelibrary.wiley.com/doi/pdf/10.1002/9781118882139.ch19}


\bibitem{CorentinJabot}
Corentin Jabot, 
\cq{Strongly-Typed Reflection on Attributes}
\biburl{http://open-std.org/JTC1/SC22/WG21/docs/papers/2019/p1887r0.pdf}


\bibitem{WolfgangJeltsch}
Wolfgang Jeltsch, 
\bibtitle{Categorical Semantics for Functional Reactive 
Programming with Temporal Recursion and Corecursion}.
\biburl{https://arxiv.org/pdf/1406.2062.pdf}


\bibitem{KloseOstermann}
Karl Klose and Klaus Ostermann,
\cq{A Classification Framework for Pointcut
Languages in Runtime Monitoring}.
\bibtitle{International Conference on Objects, Components, Models and Patterns}, 
2009, Proceedings, pages 289-307.
\biburl{https://link.springer.com/chapter/10.1007/978-3-642-02571-6_17}


%\begin{minipage}{\columnwidth}

\bibitem{KorenblumEtAl}
Daniel Korenblum, \i{et al.}, 
\cq{Managing Biomedical Image Metadata for Search and Retrieval
of Similar Images.}
\bibtitle{Journal of Digital Imaging}, Volume 24, Number 4 (2011), 
pages 739-748.
\biburl{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3138941}

\bibitem{KubotaLevine}
Yusuke Kubota and Robert Levine,
\cq{The Syntax-Semantics Interface of \sq{Respective} Predication:
A unified analysis in Hybrid Type-Logical Categorial Grammar}.
\bibtitle{Natural Language \& Linguistic Theory}, Volume 34 (2016), 
pages 911-973. 
\biburl{https://www.asc.ohio-state.edu/levine.1/publications/kl-resp.pdf}


\bibitem{LawryTang}
Jonathan Lawry and Yongchuan Tang, 
\cq{Uncertainty Modelling for Vague Concepts: A prototype theory approach}.  
\bibtitle{Artificial Intelligence}, Volume 173 (2009), 
pages 1539-1558. 
\biburl{https://www.sciencedirect.com/science/article/pii/S0004370209000903}


\bibitem{LewisLawry}
Martha Lewis and Jonathan Lawry, 
\cq{Hierarchical Conceptual Spaces for Concept Combination}. 
\bibtitle{Artificial Intelligence}, Volume 237 (2016), 
pages 204-227.  
\biburl{https://www.sciencedirect.com/science/article/pii/S0004370216300492}

\end{minipage}
\begin{minipage}{\columnwidth}


%\bibitem{KohliEtAl}
%Mark D. Kohli, \i{et al.},
%\cq{Medical Image Data and Datasets in the Era of Machine
%Learning --- Whitepaper from the 2016 C-MIMI Meeting}
%\bibtitle{Journal of Digit Imaging}, 2017.
%\biburl{https://d-nb.info/1132883164/34}


%\end{minipage}

%\setlength{\itemsep}{6pt}

%\vspace{1em}
%\begin{minipage}{\columnwidth}

%\vspace{3pt}


\bibitem{LiCunningham}
Yaoyong Li and Hamish Cunningham, 
\cq{Geometric and Quantum Methods for
Information Retrieval}.  
In \intitle{Association for Computing Machinery Special Interest 
Group on Information Retrieval},  
Volume 42, Number 2, 2008, pages 22-32.\biburl{https://dl.acm.org/doi/10.1145/1480506.1480510}


\bibitem{LuisLopes}
Lu\'\OldI{}s Lopes, \i{et al.},
\cq{A Virtual Machine for a Process Calculus}.  
\bibtitle{International Conference on Principles and 
Practice of Declarative Programming}, 1999, pages 244-260.
\biburl{http://di.fc.ul.pt/~vv/papers/lopes.silva.vasconcelos_virtual-machine-tyco.pdf}


\bibitem{FeiLiu}
Fei Liu, \i{et al.},
\cq{Coloured Petri Nets for Multilevel, Multiscale and
Multidimensional Modelling of Biological Systems}.  
\bibtitle{Briefings in Bioinformatics}, Volume 20, Issue 3, 
(2019), pages 877-886.
\biburl{https://academic.oup.com/bib/article/20/3/877/4590142}


\bibitem{IlyaMakarov}
Ilya Makarov, \i{et al.},
\cq{Quantum Logic and Natural Language Processing}.  
\biburl{http://ceur-ws.org/Vol-1886/paper_16.pdf}


\bibitem{Meichanetzidis}
Konstantinos Meichanetzidis, \i{et al.}, 
\cq{Quantum Natural Language Processing on Near-Term Quantum Computers}%
\biburl{https://arxiv.org/abs/2005.04147}


\bibitem{MichaelisLambrech}
Laura A. Michaelis and Knud Lambrech, \cq{Toward a Construction-Based Theory of Language Function: The Case of Nominal Extraposition}
\bibtitle{Language}, Volume 72, Number 2 (1996), pages 215-247.
\biburl{https://spot.colorado.edu/~michaeli/documents/Michaelis_Lambrecht_NE_LG.pdf}


\bibitem{FriederikeMoltmann}
Friederike Moltmann, 
\i{Parts and Wholes in Semantics}.
Oxford Univ. Press, 1997.\biburl{https://www.researchgate.net/publication/244487318}



%`cite<DanielLRubin>;,  `cite<KohliEtAl>;,

\bibitem{PattanasakMongkolwat}
Pattanasak Mongkolwat, \i{et al.}, 
\cq{The National Cancer Informatics Program (NCIP) Annotation
and Image Markup (AIM) Foundation Model}
\bibtitle{Journal of Digit Imaging}, Volume 27 (2014), pages 692-701.
\biburl{https://europepmc.org/backend/ptpmcrender.fcgi?accid=PMC4391072&blobtype=pdf}



\bibitem{LJOriordon}
Lee J O'Riordan, \i{et al.},
\cq{A Hybrid Classical-Quantum Workflow for 
Natural Language Processing}.
\bibtitle{Machine Learning: Science and Technology}, Volume 2 (2021).
\biburl{https://iopscience.iop.org/article/10.1088/2632-2153/abbd2e/pdf}

\bibitem{ParetiEtAl}
Paolo Pareti, \i{et al.}, 
\cq{SHACL Constraints with Inference Rules
Paolo Pareti}.
In C. Ghidini, \i{et al.} (Eds.),
\intitle{International Semantic Web Conference 2019}, 
pages 539–557.
\biburl{https://www.southampton.ac.uk/~gk1e17/shacl-inference.pdf}


\bibitem{WalterPedriali}
Walter B. Pedriali, 
\cq{The Routes of Sense: Thought, semantic inderdeterminacy and compositionality}.
Dissertation, St. Andrews, 2011.\hspace{-1em}\biburl{https://research-repository.st-andrews.ac.uk/handle/10023/3142}


\bibitem{RamsonHirschfeld}
Stefan Ramson and Robert Hirschfeld,
\cq{Active Expressions: Basic Building Blocks for Reactive Programming}.
\biburl{https://arxiv.org/abs/1703.10859}



\bibitem{MartinRaubal}
Martin Raubal,
\cq{Formalizing Conceptual Spaces}.
\biburl{http://www.raubal.ethz.ch/Courses/288MR_Spring08_Papers/Raubal_FormalizingConceptualSpaces_FOIS04.pdf}


%\end{minipage}

%\begin{minipage}{\columnwidth}

%\end{minipage}

% or https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3138941/pdf/10278_2010_Article_9328.pdf ??

%\bibitem{DanielLRubin}
%Daniel L. Rubin, 
%\cq{Finding the Meaning in Images: Annotation and Image Markup}.
%\bibtitle{Philosophy, Psychiatry, & Psychology}, Volume 18, Number 4 (2011), pages 311-318.
%\biburl{https://web.stanford.edu/group/rubinlab/pubs/18.4.rubin.pdf}

\bibitem{RubinSupekar}
Daniel L. Rubin and Kaustubh Supekar, 
\cq{Annotation and Image Markup: Accessing and Interoperating 
with the Semantic Content in Medical Imaging}.
\bibtitle{Intelligent Systems}, Volume 24, Number 1 (2009), pages 57-65.
\biburl{https://web.stanford.edu/group/rubinlab/pubs/Rubin-IEEEIntelSys-2009.pdf}


\bibitem{VahidSalari}
Vahid Salari, \i{et al.}, 
\cq{Parametrized Quantum Circuits of Synonymous
Sentences in Quantum Natural Language
Processing}.\biburl{https://assets.researchsquare.com/files/rs-220713/v1_stamped.pdf}



\bibitem{Schafmeister}
Christian Schafmeister and Alex Wood,
\cq{Clasp Common Lisp Implementation and Optimization}.
\bibtitle{11th European Lisp Symposium}, 2018, pages 59-64.%
\biburl{https://dl.acm.org/doi/10.5555/3323215.3323223}


\bibitem{SchaerEtAl}
Roger Schaer, \i{et al.},
\cq{Web-Based Tools for Exploring the Potential of Quantitative Imaging
Biomarkers in Radiology: 
Intensity and Texture Analysis on the ePAD Platform}.
In Adrien Depeursinge, \i{et al.} (Eds), 
\intitle{Biomedical Texture Analysis: Fundamentals, 
Tools, and Challenes}, Academic Press, 2017.
\biburl{http://bigwww.epfl.ch/publications/schaer1701.pdf}


\bibitem{SleatorTamperley}
Daniel D. Sleator and Davy Tamperley, 
\cq{Parsing English with a Link Grammar}.
\biburl{https://www.link.cs.cmu.edu/link/ftp-site/link-grammar/LG-IWPT93.pdf}


\bibitem{Schneider}
Gerold Schneider, 
\cq{A Linguistic Comparison of Constituency, Dependency and Link Grammar}.
Zurich University, Diploma, 2008.%
\hspace{-.6em}\biburl{https://files.ifi.uzh.ch/cl/gschneid/papers/FINALSgeroldschneider-latl.pdf}


\bibitem{teleaVission}
Alexandru Telea and Jarke J. van Wijk,
\cq{VISSION: An Object Oriented Dataflow System for Simulation and Visualization}.
\bibtitle{Data Visualization}, Proceedings, 1999, pages 225-234.
\biburl{https://pure.rug.nl/ws/portalfiles/portal/3178139/1999ProcVisSymTelea.pdf}


\bibitem{UrbanGrzelinska}
Roman Urban and Megdalena Grzelinska, 
\cq{A Potential Theory Approach to an Algorithm of Conceptual
Space Partitioning}.  In 
\bibtitle{Cognitive Studies}, Volume 1 (2017).
\biburl{https://ispan.waw.pl/journals/index.php/cs-ec/article/download/cs.1310/3065}


\bibitem{JuanUriagereka}
Juan Uriagereka, 
\i{Syntactic Anchors: On Semantic Structuring}.
Cambridge University Press, 2008.
\biburl{https://assets.cambridge.org/97805218/65326/frontmatter/9780521865326_frontmatter.pdf}

\bibitem{vanTrijp}
Remi van Trijp, 
\cq{Cognitive vs. Generative Construction
Grammar: The case of coercion and
argument structure}.  
\bibtitle{Cognitive Linguistics}, Volime 26, Issue 4 (2015), pages 613-632.
\biburl{https://www.degruyter.com/document/doi/10.1515/cog-2014-0074/html}


\bibitem{FrankZenker}
Frank Zenker,
\cq{From Features via Frames to Spaces: Modeling Scientific Conceptual Change Without Incommensurability or Aprioricity}.
In Thomas Gamerschlag, \i{et al.} (Eds.), 
\intitle{Frames and Concept Types: Applications in Language and Philosophy}, 
Springer, 2014, pages 69-89.  
\biburl{https://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.901.7852&rep=rep1&type=pdf}

\end{minipage}{\columnwidth}



\vfill{}




}
\end{thebibliography}
