
\let\oldbibitem\bibitem
%\def\bibitem{\vfill\oldbibitem}


%\vspace{1em}

\vspace{-10pt}

\begin{thebibliography}{99}
\phantomsection \label{References}
\addcontentsline{toc}{section}{References}
{\fontfamily{lmtt}\fontsize{8}{8}\selectfont

\setlength{\parskip}{0pt}
\setlength{\itemsep}{3.75pt}

\vspace{13pt}

\begin{minipage}{.97\columnwidth}

\bibitem{GregJBadros}
Greg J. Badros, \i{et al.}, 
\cq{A Constraint Extension to Scalable Vector Graphics}.
In \intitle{Proceedings of the 2001 International Conference on the World Wide Web}, pages 489-498. 
\biburl{https://constraints.cs.washington.edu/web/csvg-www10.pdf}


\bibitem{EnriqueMartinezBerti}
Enrique Martinez Berti, \i{et al.}, 
\cq{Dual Quaternions as Constraints in 4D-DPM Models
for Pose Estimation}.
\bibtitle{Sensors}, Volume 17, 2017, 
\biburl{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5579524}


%% angiogenesis data fields ...
\bibitem{MarieLaureBoizeau}
Marie-Laure Boizeau, \textit{et al.}, 
\cq{Automated Image Analysis of In Vitro
Angiogenesis Assay}.
\bibtitle{Journal of Laboratory Automation}, 
Volume 18, pages 411-415.
\biburl{https://journals.sagepub.com/doi/pdf/10.1177/2211068213495204}


%\bibitem{ChakraChennubhotla}
%Chakra Chennubhotla, \i{et al.},
%\cq{An Assessment of Imaging Informatics for Precision Medicine in Cancer}.
%\biburl{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6250996/}


\bibitem{DmitryCherezov}
Dmitry Cherezov, \i{et al.}, 
\cq{Revealing Tumor Habitats from
Texture Heterogeneity Analysis
for Classification of Lung Cancer
Malignancy and Aggressiveness}.
\bibtitle{Scientific Reports}, Volume 9, 2019.
\biburl{https://www.nature.com/articles/s41598-019-38831-0}



\bibitem{AlexandreCarlier}
Alexandre Carlier, \textit{et al.}, 
\cq{DeepSVG: A Hierarchical Generative Network for 
Vector Graphics Animation}.
In \intitle{34th Conference on Neural Information Processing Systems}, 
Proceedings, 2021.
\biburl{https://proceedings.neurips.cc//paper/2020/file/bcf9d6bd14a2095866ce8c950b702341-Paper.pdf}


\bibitem{WeiLunChao}{%
Wei-Lun Chao, 
\cq{Face Recognition}.% 
\biburl{http://disp.ee.ntu.edu.tw/~pujols/Face\%20Recognition-survey.pdf}}


\bibitem{YueqiDuan}{%
Yueqi Duan, et al., 
\cq{Topology Preserving Graph Matching for Partial Face Recognition}.
In \intitle{Proceedings of the IEEE International Conference on 
Multimedia and Expo (ICME)}, 2017.
\biburl{http://ivg.au.tsinghua.edu.cn/people/Yueqi_Duan/ICME17_Topology\%20Preserving\%20Graph\%20Matching\%20for\%20Partial\%20Face\%20Recognition.pdf}}


%% angiogenesis data fields ...
\bibitem{CharalamposNDoukas}
Charalampos N. Doukas, \textit{et al.}, 
\cq{Automated Angiogenesis Quantification through Advanced Image
Processing Techniques}.
\biburl{https://pubmed.ncbi.nlm.nih.gov/17946107}


\bibitem{PantehaEftekhar}
Panteha Eftekhar,  
\cq{Comparative Study of Edge Detection Algorithms}.
Thesis, California State University Northridge, 2019.
\biburl{https://scholarworks.calstate.edu/downloads/ff365796m}  


\bibitem{JosefEhling}
Josef Ehling, \textit{et al.}, 
\cq{Micro-CT Imaging of Tumor Angiogenesis: 
Quantitative Measures Describing Micromorphology and
Vascularization}.
\bibtitle{Biophysical Imaging and Computational Biology}, 
Volume 184, Number 2 (2014), pages 431-441.
\biburl{https://www.sciencedirect.com/science/article/pii/S0002944013007268}


\bibitem{GeorgFuchs}
Georg Fuchs, \textit{et al.}, 
\cq{Progressive imagery with scalable vector graphics}.
In \intitle{SPIE 7881, Multimedia on Mobile Devices}, 
Proceedings, 2011.
\biburl{https://vcg.informatik.uni-rostock.de/~schumann/papers/2010+/Rosenbaum-EI11b.pdf}


\bibitem{JohnGustafson}{%
John Gustafson and Isaac Yonemoto,
\q{Beating Floating Point at its Own Game: Posit Arithmetic}, 
\biburl{http://www.johngustafson.net/pdfs/BeatingFloatingPoint.pdf}}


\bibitem{GaryHuang}{%
Gary B. Huang, \i{et al.},
\cq{Towards Unconstrained Face Recognition}.
In \intitle{2008 IEEE Computer Society Conference on Computer Vision and Pattern Recognition Workshops}, Proceedings.
\biburl{http://vis-www.cs.umass.edu/papers/unconstrained_face_workshop.pdf}}

%% WSI.  Include?
%\bibitem{Farahani}{%
%Farahani N, \textit{et al.}, 
%\cq{Whole Slide Imaging in Pathology: Advantages, limitations, and %emerging perspectives}.
%\biburl{https://www.dovepress.com/whole-slide-imaging-in-pathology-advantages-limitations-and-emerging-p-peer-reviewed-article-PLMI}}


% 8 ...
% NE Protein Expression Is Altered in Many Human tumors
%\bibitem{EdgarGFischer}
%Edgar G. Fischer, 
%\cq{Nuclear Morphology and the Biology of Cancer Cells}.
%\bibtitle{Acta Cytologica}, Volume 64 (2020), pages 511-519. 
%\biburl{https://www.karger.com/Article/Pdf/508780}


\bibitem{KalaiselviNithya}{%
Patchaiah Kalaiselvi and Sivasamy Nithya,
\cq{Face Recognition System under Varying Lighting Conditions}.
In \intitle{IOSR Journal of Computer Engineering}, 
Volume 14, Issue 3 (Sep.-Oct. 2013), pages 79-88.
\biburl{http://www.iosrjournals.org/iosr-jce/papers/Vol14-issue3/M01437988.pdf}}



\bibitem{YangLi}
Yang Li, \i{et al.}, 
\cq{4DComplete: Non-Rigid Motion Estimation Beyond the Observable Surface}.
\biburl{https://arxiv.org/abs/2105.01905}



\bibitem{FengLu}{%
Feng Lu, \i{et al.},
\cq{Adaptive Linear Regression for Appearance-Based Gaze Estimation}.
\bibtitle{IEEE Transactions on Pattern Analysis and Machine Intelligence}, Volume 13, Number 10 (2004), pages 2033-2046.
\biburl{https://www.ncbi.nlm.nih.gov/pubmed/26352633}}


% biomarkers ...
%\bibitem{JamesOConnor}
%James O'Connor, \textit{et al.}, 
%\cq{Imaging tumour hypoxia with oxygen-enhanced MRI
%and BOLD MRI}.
%\bibtitle{British Journal of Radiolology}  
%Volume 92 (2019).
%\biburl{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6540855/pdf/bjr.20180642.pdf}


\bibitem{DanielLRubin}
Daniel L. Rubin, \textit{et al.}, 
\cq{Medical Imaging on the Semantic Web: Annotation and Image Markup}.
\biburl{http://cedarweb.vsp.ucar.edu/wiki/images/d/d9/R_19.pdf}


\bibitem{MichailSchwab}
Michail Schwab, \textit{et al.}, 
\cq{Scalable Scalable Vector Graphics:
Automatic Translation of Interactive
SVGs to a Multithread VDOM for Fast Rendering}.
\bibtitle{Micromachines}, Volume 11, Issue 7 (2020).
\biburl{https://ieeexplore.ieee.org/document/9354592}


\bibitem{MatveySprindzuk}
Matvey Sprindzuk, \textit{et al.}, 
\cq{Computer-aided Image Processing of Angiogenic
Histological Samples in Ovarian Cancer} 
\biburl{https://core.ac.uk/download/pdf/8701857.pdf}


\bibitem{IoannisValavanis}
Ioannis Valavanis, \textit{et al.}, 
\cq{A Novel Image Analysis Methodology for the Evaluation
of Angiogenesis in Matrigel Assays and Screening
of Angiogenesis-Modulating Compounds}. 
\biburl{https://link.springer.com/content/pdf/10.1007\%2F978-3-319-23868-5_5.pdf}


\bibitem{XuPrince}
Chenyang Xu and Jerry L. Prince, 
\cq{Snakes, Shapes, and Gradient Vector Flow}.
\bibtitle{Transactions on Image Processing}, 
Volume 7, Number 3 (1998), pages 359-369.
\biburl{https://pubmed.ncbi.nlm.nih.gov/18276256/}


\bibitem{YangForan}
Lin Yang and David J. Foran, 
\cq{Deformable Models and their Application 
in Segmentation of Imaged Pathology Specimens}.
In Jasjit S. Suri and Aly A. Farag, \intitle{Deformable Models} 
(Springer 2007), pages 75-94.
\biburl{https://link.springer.com/chapter/10.1007/978-0-387-68343-0_3}




\vfill{}

\end{minipage}


}
\end{thebibliography}



