
\let\oldbibitem\bibitem
%\def\bibitem{\vfill\oldbibitem}


%\vspace{1em}

\vspace{-10pt}

\begin{thebibliography}{99}
\phantomsection \label{References}
\addcontentsline{toc}{section}{References}
{\fontfamily{lmtt}\fontsize{8}{8}\selectfont

\setlength{\parskip}{0pt}
\setlength{\itemsep}{3.75pt}

\vspace{13pt}


\bibitem{GregJBadros}
Greg J. Badros, \i{et al.}, 
\cq{A Constraint Extension to Scalable Vector Graphics}.
In \intitle{Proceedings of the 2001 International Conference on the World Wide Web}, pages 489-498. 
\biburl{https://constraints.cs.washington.edu/web/csvg-www10.pdf}


\bibitem{EnriqueMartinezBerti}
Enrique Martinez Berti, \i{et al.}, 
\cq{Dual Quaternions as Constraints in 4D-DPM Models
for Pose Estimation}.
\bibtitle{Sensors}, Volume 17, 2017, 
\biburl{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5579524}


%\bibitem{ChakraChennubhotla}
%Chakra Chennubhotla, \i{et al.},
%\cq{An Assessment of Imaging Informatics for Precision Medicine in Cancer}.
%\biburl{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6250996/}


\bibitem{DmitryCherezov}
Dmitry Cherezov, \i{et al.}, 
\cq{Revealing Tumor Habitats from
Texture Heterogeneity Analysis
for Classification of Lung Cancer
Malignancy and Aggressiveness}.
\bibtitle{Scientific Reports}, Volume 9, 2019.
\biburl{https://www.nature.com/articles/s41598-019-38831-0}



%% angiogenesis data fields ...
\bibitem{MarieLaureBoizeau}
Marie-Laure Boizeau, \textit{et al.}, 
\cq{Automated Image Analysis of In Vitro
Angiogenesis Assay}.
\bibtitle{Journal of Laboratory Automation}, 
Volume 18, pages 411-415.
\biburl{https://journals.sagepub.com/doi/pdf/10.1177/2211068213495204}


\bibitem{AlexandreCarlier}
Alexandre Carlier, \textit{et al.}, 
\cq{DeepSVG: A Hierarchical Generative Network for 
Vector Graphics Animation}.
In \intitle{34th Conference on Neural Information Processing Systems}, 
Proceedings, 2021.
\biburl{https://proceedings.neurips.cc//paper/2020/file/bcf9d6bd14a2095866ce8c950b702341-Paper.pdf}


\bibitem{WeiLunChao}{%
Wei-Lun Chao, 
\cq{Face Recognition}.% 
\biburl{http://disp.ee.ntu.edu.tw/~pujols/Face\%20Recognition-survey.pdf}}


\bibitem{DavidAClunie}
David A. Clunie, 
\cq{DICOM Structured Reporting}.
\biburl{http://www.dclunie.com/pixelmed/DICOMSR.book.pdf}


\bibitem{YueqiDuan}{%
Yueqi Duan, et al., 
\cq{Topology Preserving Graph Matching for Partial Face Recognition}.
In \intitle{Proceedings of the IEEE International Conference on 
Multimedia and Expo (ICME)}, 2017.
\biburl{http://ivg.au.tsinghua.edu.cn/people/Yueqi_Duan/ICME17_Topology\%20Preserving\%20Graph\%20Matching\%20for\%20Partial\%20Face\%20Recognition.pdf}}


%% angiogenesis data fields ...
\bibitem{CharalamposNDoukas}
Charalampos N. Doukas, \textit{et al.}, 
\cq{Automated Angiogenesis Quantification through Advanced Image
Processing Techniques}.
\biburl{https://pubmed.ncbi.nlm.nih.gov/17946107}


\bibitem{JosefEhling}
Josef Ehling, \textit{et al.}, 
\cq{Micro-CT Imaging of Tumor Angiogenesis: 
Quantitative Measures Describing Micromorphology and
Vascularization}.
\bibtitle{Biophysical Imaging and Computational Biology}, 
Volume 184, Number 2 (2014), pages 431-441.
\biburl{https://www.sciencedirect.com/science/article/pii/S0002944013007268}


\bibitem{PantehaEftekhar}
Panteha Eftekhar,  
\cq{Comparative Study of Edge Detection Algorithms}.
Thesis, California State University Northridge, 2019.
\biburl{https://scholarworks.calstate.edu/downloads/ff365796m}  


\bibitem{AndreasFabri}
Andreas Fabri, \i{et al.},
\cq{On the Design of CGAL, the Computational Geometry Algorithms Library}.
Max Planck Institute, 1998.
\biburl{https://core.ac.uk/download/pdf/210674597.pdf}


\bibitem{GeorgFuchs}
Georg Fuchs, \textit{et al.}, 
\cq{Progressive imagery with scalable vector graphics}.
In \intitle{SPIE 7881, Multimedia on Mobile Devices}, 
Proceedings, 2011.
\biburl{https://vcg.informatik.uni-rostock.de/~schumann/papers/2010+/Rosenbaum-EI11b.pdf}


\bibitem{JohnGustafson}{%
John Gustafson and Isaac Yonemoto,
\q{Beating Floating Point at its Own Game: Posit Arithmetic}, 
\biburl{http://www.johngustafson.net/pdfs/BeatingFloatingPoint.pdf}}


\bibitem{GaryHuang}{%
Gary B. Huang, \i{et al.},
\cq{Towards Unconstrained Face Recognition}.
In \intitle{2008 IEEE Computer Society Conference on Computer Vision and Pattern Recognition Workshops}, Proceedings.
\biburl{http://vis-www.cs.umass.edu/papers/unconstrained_face_workshop.pdf}}

%% WSI.  Include?
%\bibitem{Farahani}{%
%Farahani N, \textit{et al.}, 
%\cq{Whole Slide Imaging in Pathology: Advantages, limitations, and %emerging perspectives}.
%\biburl{https://www.dovepress.com/whole-slide-imaging-in-pathology-advantages-limitations-and-emerging-p-peer-reviewed-article-PLMI}}


% 8 ...
% NE Protein Expression Is Altered in Many Human tumors
%\bibitem{EdgarGFischer}
%Edgar G. Fischer, 
%\cq{Nuclear Morphology and the Biology of Cancer Cells}.
%\bibtitle{Acta Cytologica}, Volume 64 (2020), pages 511-519. 
%\biburl{https://www.karger.com/Article/Pdf/508780}


\bibitem{DavidJuncker}
David Juncker, \textit{et al.}, 
\cq{Multipurpose Microfluidic Probe}.
\bibtitle{Nature Materials}, Volume 4, Issue 8 (2005), pages 622-628.
\biburl{https://pubmed.ncbi.nlm.nih.gov/16041377/}


\bibitem{KalaiselviNithya}{%
Patchaiah Kalaiselvi and Sivasamy Nithya,
\cq{Face Recognition System under Varying Lighting Conditions}.
In \intitle{IOSR Journal of Computer Engineering}, 
Volume 14, Issue 3 (Sep.-Oct. 2013), pages 79-88.
\biburl{http://www.iosrjournals.org/iosr-jce/papers/Vol14-issue3/M01437988.pdf}}


\bibitem{AdityaKashyap}
Aditya Kashyap, \i{et al.}, 
\cq{Quantitative Microimmunohistochemistry for the Grading of Immunostains on Tumour Tissues}.
\bibtitle{Nature Biomedical Engineering}, Volume 3 (2019), pages 478-490.
\biburl{https://www.nature.com/articles/s41551-019-0386-3}


\bibitem{RobertLeif}
Robert C. Leif,  
\cq{CytometryML with DICOM and FCS}.
\bibtitle{SPIE} (International Society for Optics 
and Photonics), Proceedings (2018).
\biburl{https://spie.org/Publications/Proceedings/Paper/10.1117/12.2295220?SSO=1}



\bibitem{YangLi}
Yang Li, \i{et al.}, 
\cq{4DComplete: Non-Rigid Motion Estimation Beyond the Observable Surface}.
\biburl{https://arxiv.org/abs/2105.01905}


\bibitem{LovchikEtAl}
Robert D. Lovchik, \textit{et al.}, 
\cq{Rapid Micro-Immunohistochemistry}.
\bibtitle{Microsystems \& Nanoengineering}, Volume 6 (2020).
\biburl{https://www.nature.com/articles/s41378-020-00205-2.pdf}  


\bibitem{FengLu}{%
Feng Lu, \i{et al.},
\cq{Adaptive Linear Regression for Appearance-Based Gaze Estimation}.
\bibtitle{IEEE Transactions on Pattern Analysis and Machine Intelligence}, Volume 13, Number 10 (2004), pages 2033-2046.
\biburl{https://www.ncbi.nlm.nih.gov/pubmed/26352633}}


\bibitem{PattanasakMongkolwat}
Pattanasak Mongkolwat, \i{et al.}, 
\cq{The National Cancer Informatics Program (NCIP) Annotation
and Image Markup (AIM) Foundation Model}
\bibtitle{Journal of Digit Imaging}, Volume 27 (2014), pages 692-701.
\biburl{https://europepmc.org/backend/ptpmcrender.fcgi?accid=PMC4391072&blobtype=pdf}


% biomarkers ...
%\bibitem{JamesOConnor}
%James O'Connor, \textit{et al.}, 
%\cq{Imaging tumour hypoxia with oxygen-enhanced MRI
%and BOLD MRI}.
%\bibtitle{British Journal of Radiolology}  
%Volume 92 (2019).
%\biburl{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6540855/pdf/bjr.20180642.pdf}

\bibitem{ODonnellEtAl}
Erika A O'Donnell, \textit{et al.}, 
\cq{Multiparameter Flow Cytometry: Advances in High Resolution
Analysis}.
\bibtitle{Immune Network}, Volume 13, Number 2 (2013), pages 43-54.
\biburl{https://www.immunenetwork.org/pdf/10.4110/in.2013.13.2.43}  


\bibitem{ParadowskiEtAl}
Mariusz Paradowski, \i{et al.},
\cq{Capillary Blood Vessel Tracking Using Polar Coordinates Based Model Identification}.
\bibtitle{Computer Recognition Systems}, Volume 3, pages 499-50.
\biburl{https://link.springer.com/chapter/10.1007/978-3-540-93905-4_59}


\bibitem{ThomasMPearce}
Thomas M. Pearce, \textit{et al.}, 
\cq{Integrated Microelectrode Array and Microfluidics for Temperature Clamp 
of Sensory Neurons in Culture}.
\bibtitle{Lab on a Chip}, 2005, Issue 5, pages 97-101.
\biburl{https://pubs.rsc.org/en/content/articlehtml/2005/lc/b407871c}


\bibitem{QasaimehEtAl}
Mohammad A. Qasaimeh, \textit{et al.}, 
\cq{Microfluidic Probes for Use in Life Sciences and Medicine}.
\bibtitle{Lab on a Chip}, 2013, Issue 1.
\burl{https://pubs.rsc.org/en/content/articlelanding/2013/lc/c2lc40898h}



\bibitem{DanielLRubin}
Daniel L. Rubin, \textit{et al.}, 
\cq{Medical Imaging on the Semantic Web: Annotation and Image Markup}.
\biburl{http://cedarweb.vsp.ucar.edu/wiki/images/d/d9/R_19.pdf}


\bibitem{MichailSchwab}
Michail Schwab, \textit{et al.}, 
\cq{Scalable Scalable Vector Graphics:
Automatic Translation of Interactive
SVGs to a Multithread VDOM for Fast Rendering}.
\bibtitle{Micromachines}, Volume 11, Issue 7 (2020).
\biburl{https://ieeexplore.ieee.org/document/9354592}


\bibitem{KentaShinha}
Kenta Shinha, \textit{et al.}, 
\cq{A Microfluidic Probe Integrated Device for
Spatiotemporal 3D Chemical Stimulation in Cells}
\bibtitle{IEEE Transactions on Visualization and Computer Graphics}, 2021.
\biburl{https://www.mdpi.com/2072-666X/11/7/691}



\bibitem{MatveySprindzuk}
Matvey Sprindzuk, \textit{et al.}, 
\cq{Computer-aided Image Processing of Angiogenic
Histological Samples in Ovarian Cancer} 
\biburl{https://core.ac.uk/download/pdf/8701857.pdf}



\bibitem{ATraverso}
A. Traverso, \i{et al.}, 
\cq{FAIR Quantitative Imaging in Oncology: How Semantic
Web and Ontologies will support reproducible science}.
\biburl{http://ceur-ws.org/Vol-2849/paper-14.pdf}


\bibitem{IoannisValavanis}
Ioannis Valavanis, \textit{et al.}, 
\cq{A Novel Image Analysis Methodology for the Evaluation
of Angiogenesis in Matrigel Assays and Screening
of Angiogenesis-Modulating Compounds}. 
\biburl{https://link.springer.com/content/pdf/10.1007\%2F978-3-319-23868-5_5.pdf}


\bibitem{JohanVanSoest}
Johan Van Soest, \i{et al.}, 
\cq{Towards a semantic PACS: Using Semantic Web technology to represent imaging data}.
\bibtitle{Studies in Health Technology and Informatics}, Volume 205 
(2014), pages 166-179, 
\biburl{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5119276/}


\bibitem{Vining}
David J. Vining, \i{et al.}, 
\cq{Development of the ViSion Ontology}.
\biburl{https://www.semanticscholar.org/paper/Development-of-the-Vision-Ontology.-Vining-Salem/84201e9bd58348bcc5356e0c154a629cc524c778}


\bibitem{WangHoffman}
Lili Wang and Robert A. Hoffman, \i{et al.}, 
\cq{Standardization, Calibration, and Control in Flow Cytometry}.
\bibtitle{Current Protocols in Cytometry},
Voume 79 (2017).
\biburl{https://tsapps.nist.gov/publication/get_pdf.cfm?pub_id=921423}


\bibitem{XuPrince}
Chenyang Xu and Jerry L. Prince, 
\cq{Snakes, Shapes, and Gradient Vector Flow}.
\bibtitle{Transactions on Image Processing}, 
Volume 7, Number 3 (1998), pages 359-369.
\biburl{https://pubmed.ncbi.nlm.nih.gov/18276256/}


\bibitem{YangForan}
Lin Yang and David J. Foran, 
\cq{Deformable Models and their Application 
in Segmentation of Imaged Pathology Specimens}.
In Jasjit S. Suri and Aly A. Farag, \intitle{Deformable Models} 
(Springer 2007), pages 75-94.
\biburl{https://link.springer.com/chapter/10.1007/978-0-387-68343-0_3}

\bibitem{EdyWijaya}
Edy Wijaya, \i{et al.},
\cq{Surface Plasmon Resonance-Based Biosensors: From the development of different
SPR structures to novel surface functionalization strategies}.
\bibtitle{Current Opinion in Solid State and Materials Science}, 
Volume 15, Issue 5 (2011), pages 208-224.
\biburl{http://www.ffh.bg.ac.rs/wp-content/uploads/2017/05/Wijaya.pdf}







\vfill{}




}
\end{thebibliography}



