
\let\oldbibitem\bibitem
%\def\bibitem{\vfill\oldbibitem}


%\vspace{1em}

\vspace{-17pt}

\begin{thebibliography}{99}


\phantomsection \label{References}
\addcontentsline{toc}{section}{References}
{\fontfamily{lmtt}\fontsize{8}{8}\selectfont

\setlength{\parskip}{0pt}
\setlength{\itemsep}{3.75pt}

\vspace{10pt}


%!!
\begin{minipage}{.95\columnwidth}

\bibitem{ArashAbiri}
Arash Abiri, \i{et al.}, 
\cq{Simulating Developmental Cardiac Morphology in Virtual Reality Using a Deformable Image Registration Approach}.
\bibtitle{Annals of Biomedical Engineering}, Volume 46 (2018), pages 2177-2188.
\biburl{https://link.springer.com/article/10.1007/s10439-018-02113-z}


\bibitem{AsabellaEtAl}
Artor Niccoli Asabella, \i{et al.}, 
\cq{Multimodality Imaging in Tumor Angiogenesis: Present Status 
and Perspectives}.
\bibtitle{International Journal of Molecular Sciences}, 
Volume 18, Number 9 (2017).
\biburl{https://www.mdpi.com/1422-0067/18/9/1864}



\bibitem{SaeedAshrafinia}
Saeed Ashrafinia, 
\cq{Quantitative Nuclear Medicine Imaging Using Advanced 
Image Reconstruction and Radiomics}.
Dissertation, Johns Hopkins University, 2019.
\biburl{https://jscholarship.library.jhu.edu/handle/1774.2/61551}



\bibitem{NayAung}
Nay Aung, \i{et al.}, 
\cq{Genome-Wide Analysis of Left Ventricular Image-Derived Phenotypes Identifies Fourteen Loci Associated With Cardiac Morphogenesis and Heart Failure Development}.
\bibtitle{Circulation}, Volume 140, Number 16 (2019), pages 1318-1330.
\biburl{https://pubmed.ncbi.nlm.nih.gov/31554410/}


\bibitem{BettinaBaessler}
Bettina Baessler, \i{et al.}, 
\cq{Subacute and Chronic Left Ventricular Myocardial 
Scar: Accuracy of Texture Analysis 
on Nonenhanced Cine MR Images}.
\bibtitle{Radiology}, Volume 286 (2018), pages 108-112.
\biburl{https://pubmed.ncbi.nlm.nih.gov/28836886/}


\bibitem{StefanoCanali}
Stefano Canali, 
\cq{Towards a Contextual Approach to Data Quality}.
\bibtitle{Data}, Volume 5, Number 4 (2020).
\biburl{https://www.mdpi.com/2306-5729/5/4/90}




\bibitem{IremCetin}
Irem Cetin, \i{et al.}, 
\cq{A Radiomics Approach to Computer-Aided Diagnosis 
with Cardiac Cine-MRI}.
\biburl{https://arxiv.org/abs/1909.11854}


\bibitem{CetinEtAl}
Irem Cetin, \i{et al.}, 
\cq{Radiomics Signatures of Cardiovascular Risk Factors 
in Cardiac MRI: Results From the UK Biobank}.
\bibtitle{Frontiers in Cardiovascular Medicine}, 2020.
\biburl{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7667130/}


\bibitem{XiangChen}
Xiang Chen, \i{et al.}, 
\cq{Deep Learning in Medical Image Registration}.
\bibtitle{Progress in Biomedical Engineering}, Volume 3 (2021).
\biburl{https://iopscience.iop.org/article/10.1088/2516-1091/abd37c/pdf}


\bibitem{ChakraChennubhotla}
Chakra Chennubhotla, \i{et al.}, 
\cq{An Assessment of Imaging Informatics 
for Precision Medicine in Cancer}.
\bibtitle{Yearbook of Medical Informatics}, Volume 26, Number 1 (2017), 
pages 110-119.
\biburl{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6250996}


\bibitem{PornpimolCharoentong}
Pornpimol Charoentong, \i{et al.}, 
\cq{Pan-cancer Immunogenomic Analyses Reveal 
Genotype-Immunophenotype Relationships and 
Predictors of Response to Checkpoint Blockade}.
\bibtitle{Cell Reports}, Volume 18, Number 1 (2017), 
\biburl{https://pubmed.ncbi.nlm.nih.gov/28052254/}


\bibitem{YongChen}
Yong Chen, \i{et al.}, 
\cq{Simulation of Avascular Tumor
Growth by Agent-Based Game Model Involving Phenotype-
Phenotype Interactions}.
\bibtitle{Scientific Reports}, Volume 5 (2016).
\biburl{https://www.nature.com/articles/srep17992}


\bibitem{DmitryCherezov}
Dmitry Cherezov, \i{et al.}, 
\cq{Revealing Tumor Habitats from Texture Heterogeneity Analysis 
for Classification of Lung Cancer Malignancy and Aggressiveness}.
\bibtitle{Scientific Reports}, Volume 9 (2019).
\biburl{https://www.nature.com/articles/s41598-019-38831-0}


\bibitem{DavidAClunie}
David A. Clunie, 
\cq{DICOM Structured Reporting}.
\biburl{http://www.dclunie.com/pixelmed/DICOMSR.book.pdf}


\bibitem{ConnorEtAl}
Anthony J. Connor, \i{et al.}, 
\cq{Object-Oriented Paradigms for Modelling Vascular Tumour Growth: A Case Study}.
In \intitle{Fourth International Conference on Advances in System Simulation}, Proceedings (2012).
\biburl{https://people.maths.ox.ac.uk/maini/PKM\%20publications/354.pdf}


\bibitem{JingjingDeng}
Jingjing Deng, 
\cq{Adaptive Learning for Segmentation and Detection}.
Dissertation, University of Swansea, 2017.
\biburl{https://cronfa.swan.ac.uk/Record/cronfa36297}


\bibitem{ShihongDeng}
Shihong Deng, \i{et al.}, 
\cq{Autoregressive Image Interpolation via Context 
Modeling and Multiplanar Constraint}.
In \intitle{2016 Visual Communications and Image Processing} (VCIP), Proceedings, pages 1-4.
\biburl{https://ieeexplore.ieee.org/document/7805448}


\bibitem{DonglinDi}
Donglin Di, \textit{et al.}, 
\cq{Hypergraph Learning for Identification of COVID-19 with CT Imaging}.
\bibtitle{Medical Image Analysis}, Volume 68 (2021).
\biburl{https://pubmed.ncbi.nlm.nih.gov/33285483}


\bibitem{PrashantDogra}
Prashant Dogra, \i{et al.}, 
\cq{Mathematical Modeling in Cancer Nanomedicine: A review}.
\bibtitle{Biomedical Microdevices}, Volume 21 (2019).
\biburl{https://link.springer.com/article/10.1007/s10544-019-0380-2}


%\begin{minipage}{\columnwidth}

\bibitem{FrancesDuane}
Frances Duane, \i{et al.}, 
\cq{A Cardiac Contouring Atlas for Radiotherapy}.
\bibtitle{Radiotherapy and Oncology}, Volume 122 (2017), pages 416-422.
\biburl{https://cdn.mednet.co.il/2019/06/A-cardiac-contouring-atlas-for-radiotherapy.pdf}


\bibitem{WlodzislawDuch}
W\l{}odzis\l{}aw Duch, 
\cq{Neurocognitive Informatics Manifesto}.
\bibtitle{Cognitive Sciences ePrint Archive}, 2009.
\biburl{https://arxiv.org/abs/2101.03609}


\bibitem{IacopoFabiani}
Iacopo Fabiani, \i{et al.}, 
\cq{Micro-RNA-21 (Biomarker) and Global Longitudinal Strain (Functional Marker) in Detection of Myocardial Fibrotic Burden in 
Severe Aortic Valve Stenosis: A pilot study}.
\bibtitle{Journal of Translational Medicine}, Volume 14 (2016).
\biburl{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5002330}

\end{minipage}

\begin{minipage}{.95\columnwidth}

\bibitem{GrazzielaFigueredo}
Grazziela P. Figueredo, \i{et al.},
\cq{On-Lattice Agent-Based Simulation of Populations of Cells Within the
Open-Source Chaste Framework}.
\bibtitle{Interface Focus}, Volume 3 (2013).
\biburl{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3638480}


\bibitem{FinotelloTrajanos}
Francesca Finotello and Zlatko Trajanos,
\cq{Quantifying Tumor-Infiltrating Immune Cells from Transcriptomics Data}.
\bibtitle{Cancer Immunology, Immunotherapy}, Volume 67 (2018), 
pages 1031-1040.
\biburl{https://pubmed.ncbi.nlm.nih.gov/29541787}


\bibitem{FonsecaEtAl}
Carissa G. Fonseca, \i{et al.},
\cq{The Cardiac Atlas Project --- An imaging database for
computational modeling and statistical atlases of the heart}.
\bibtitle{Bioinformatics}, Volume 27, Number 16 (2011). 
\biburl{https://academic.oup.com/bioinformatics/article/27/16/2288/253995}


\bibitem{RezaForghani}
Reza Forghani, \i{et al.},
\cq{Radiomics and Artificial Intelligence for Biomarker and Prediction Model Development in Oncology}.
\bibtitle{Computational and Structural Biotechnology Journal}, Volume 17 (2019), pages 995-1008.
\biburl{https://www.sciencedirect.com/science/article/pii/S2001037019301382}


\bibitem{YuFu}
Yu Fu, \i{et al.},
\cq{Pan-Cancer Computational Histopathology Reveals
Mutations, Tumor Composition and Prognosis}.
\bibtitle{Nature Cancer}, Volume 1 (2020), pages 800-810.
\biburl{https://www.nature.com/articles/s43018-020-0085-8}


\bibitem{GatenbyEtAl}
Robert A. Gatenby, \i{et al.},
\cq{Quantitative Imaging in Cancer Evolution and Ecology}.
\bibtitle{Radiology}, Volume 269, Number 1 (2013), pages 8-15.
\biburl{https://pubmed.ncbi.nlm.nih.gov/24062559}


%% atlas  data sets
\bibitem{GhoshEtAl}
Tarun Kanti Ghosh, \i{et al.},
\cq{Multi-class Probabilistic Atlas-Based
Whole Heart Segmentation Method in
Cardiac CT and MRI}.
\bibtitle{IEEE Access}, 2021.
\biburl{https://arxiv.org/pdf/2102.01822.pdf}


\bibitem{KathleenGilbert}
Kathleen Gilbert, \i{et al.},
\cq{Independent Left Ventricular Morphometric Atlases Show
Consistent Relationships with Cardiovascular Risk Factors: A UK
Biobank Study}.
\bibtitle{Scientific Reports}, 2019.
\biburl{https://eprints.whiterose.ac.uk/157310/1/s41598-018-37916-6.pdf}


\bibitem{GilbertSerra}
Xavier Gilbert Serra,
\cq{Anomaly Detection in Noisy Images}.  
Dissertation, University of Maryland, 2015.
\biburl{https://drum.lib.umd.edu/handle/1903/18119}


\bibitem{RobertJGillies}
Robert J. Gillies, \i{et al.},
\cq{Radiomics: Images Are More than
Pictures, They Are Data}.
\bibtitle{Radiology}, Volume 278, Number 2 (2016).
\biburl{https://pubmed.ncbi.nlm.nih.gov/26579733/}



%%%
\bibitem{ChangGong}
Chang Gong, \i{et al.},
\cq{A Computational Multiscale Agent-Based Model for Simulating Spatio-Temporal Tumour Immune Response to PD1 and PDL1 Inhibition}.
\bibtitle{The Journal of the Royal Society Interface}, Volume 14 (2017).
\biburl{https://pubmed.ncbi.nlm.nih.gov/28931635}


\bibitem{PatrickGrossmann}
Patrick Grossmann, \i{et al.},
\cq{Defining the Biological Basis of Radiomic Phenotypes in Lung Cancer}.
\bibtitle{eLife}, Volume 6 (2017).
\biburl{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5590809/}


\bibitem{StephanGuttinger}
Stephan G\"uttinger,
\cq{The Limits of Replicability}.  
\bibtitle{European Journal for Philosophy of Science}, Volume 10, 
Number 2 (2020).
\biburl{https://core.ac.uk/download/pdf/237399625.pdf}


\bibitem{AkifumiHagiwara}
Akifumi Hagiwara, \i{et al.},
\cq{Variability and Standardization of Quantitative Imaging:
Monoparametric to Multiparametric Quantification, Radiomics, and Artificial Intelligence}.
\bibtitle{Investigative Radiology}, Volume 25, Number 9 (2020).
\biburl{https://journals.lww.com/investigativeradiology/Fulltext/2020/09000/Variability_and_Standardization_of_Quantitative.11.aspx}


\bibitem{SaraHamis}
Sara Hamis, \i{et al.}, 
\cq{Blackboard to Bedside: A Mathematical
Modeling Bottom-Up Approach Toward
Personalized Cancer Treatments}.
\bibtitle{JCO Clinical Cancer Informatics}, 
Volume 3 (2019).
\biburl{https://ascopubs.org/doi/10.1200/CCI.18.00068}


\bibitem{CameronHassani}
Cameron Hassani, \i{et al.}, 
\cq{Myocardial Radiomics in Cardiac MRI}.
\bibtitle{American Journal of Roentgenology}, Volume 214, 
Number 3 (2020).
\biburl{https://www.ajronline.org/doi/pdfplus/10.2214/AJR.19.21986}


\bibitem{AlessaHering}
Alessa Hering, \i{et al.}, 
\cq{Enhancing Label-Driven Deep Deformable
Image Registration with Local Distance Metrics
for State-of-the-Art Cardiac Motion Tracking}.
\biburl{https://arxiv.org/pdf/1812.01859.pdf}


\bibitem{YiHong}
Yi Hong, \i{et al.},
\cq{Application of Standardized Biomedical
Terminologies in Radiology Reporting
Templates}.
\bibtitle{Information Services \& Use}, Volume 33 (2013),
pages 309-323.
\biburl{https://content.iospress.com/download/information-services-and-use/isu708?id=information-services-and-use/isu708}


\bibitem{HoqueEtAl}
Iram Tazim Hoque, \textit{et al.}, 
\cq{A Contour Property Based Approach
to Segment Nuclei in Cervical Cytology Images}.
\bibtitle{BMC Medical Imaging}, Volume 21 (2021).
\biburl{https://bmcmedimaging.biomedcentral.com/track/pdf/10.1186/s12880-020-00533-9.pdf}


\bibitem{IlesEtAl}
Leah M. Iles, \i{et al.}, 
\cq{Histological Validation of Cardiac Magnetic 
Resonance Analysis of Regional and Diffuse
Interstitial Myocardial Fibrosis}.
\bibtitle{European Heart Journal -- Cardiovascular Imaging}, 2015, 
pages 14-22.
\biburl{https://academic.oup.com/ehjcimaging/article/16/1/14/2403445}


%\end{minipage}
%\begin{minipage}{.98\columnwidth}


%%%
\bibitem{MohammadJafarnejad}
Mohammad Jafarnejad, \i{et al.},
\cq{Mechanistically detailed systems biology modeling of the
HGF/Met pathway in hepatocellular carcinoma}.
\bibtitle{npj Systems Biology and Applications}, 2016.
\biburl{https://www.nature.com/articles/s41540-019-0107-2}


\bibitem{DavidJohnson}
David Johnson, \i{et al.},
\cq{Semantically Linking In Silico Cancer Models}.
\bibtitle{Cancer Informatics}, 2014.
\biburl{https://journals.sagepub.com/doi/10.4137/CIN.S13895}

\end{minipage}

\begin{minipage}{.95\columnwidth}


\bibitem{KaleAksoy}
Asl\OldI{} Kale and Selim Aksoy, 
\cq{Segmentation of Cervical Cell Images}.
In \intitle{2010 20th International Conference on Pattern Recognition},  Proceedings.
\biburl{https://ieeexplore.ieee.org/document/5595797}


\bibitem{YildirimKarslioglu}
Yildirim Karslio\u{g}lu, \i{et al.}, 
\cq{Chalkley Method in the Angiogenesis Research and its Automation via Computer Simulation}.
\bibtitle{Pathology -- Research and Practice}, 
Volume 210, Number 3 (2014), pages 161-168.
\biburl{https://pubmed.ncbi.nlm.nih.gov/24359720}


\bibitem{KatherEtAl}
Jakob Nikolas Kather, \i{et al.}, 
\cq{Continuous Representation of Tumor Microvessel Density and
Detection of Angiogenic Hotspots in Histological Whole-Slide Images}.
\bibtitle{Oncotarget}, Volume 6, Number 22 (2015), pages 19163-19176.
\biburl{https://pubmed.ncbi.nlm.nih.gov/26061817}


\bibitem{KathiraveluSharma}
Pradeeban Kathiravelu and Ashish Sharma, 
\cq{MEDIator: A Data Sharing Synchronization Platform for
Heterogeneous Medical Image Archives}.
\bibtitle{SIGKDD 2015 BigCHat Workshop}.
\biburl{https://zenodo.org/record/844842#.YPoMs1NKiis}


\bibitem{AziraKhalil}
Azira Khalil, \i{et al.}, 
\cq{An Overview on Image Registration Techniques for Cardiac
Diagnosis and Treatment}.
\bibtitle{Cardiology Research and Practice}, 2018.
\biburl{https://www.hindawi.com/journals/crp/2018/1437125/}


\bibitem{SteffenKlamt}
Steffen Klamt, \i{et al.}, 
\cq{Hypergraphs and Cellular Networks}.
\bibtitle{PLoS Computational Biology}, 2009.
\biburl{https://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1000385}



\bibitem{MartonKolossvary}
M\'arton Kolossv\'ary, \i{et al.}, 
\cq{Cardiac Computed Tomography Radiomics:
A Comprehensive Review on Radiomic Techniques}.
\bibtitle{Journal of Thorac Imaging}, Volume 33, Number 1 (2018), 
pages 26-34.
\biburl{https://pubmed.ncbi.nlm.nih.gov/28346329/}



\bibitem{LeeStantz}
Chung‐Wein Lee and Keith M. Stantz, 
\cq{Development of a Mathematical Model
to Estimate Intra‐Tumor Oxygen Concentrations
through Multi‐Parametric Imaging}.\bibtitle{BioMedical Engineering OnLine}, Volume 15 (2014).\biburl{https://biomedical-engineering-online.biomedcentral.com/articles/10.1186/s12938-016-0235-5}


\bibitem{HuiLi}
Hui Li, \i{et al.}, 
\cq{Quantitative MRI Radiomics in the Prediction of Molecular Classifications of Breast Cancer Subtypes in the TCGA/TCIA Data Set}.
\bibtitle{NPJ Breast Cancer}, Volume 2016, Number 2.
\biburl{https://www.nature.com/articles/npjbcancer201612.pdf}


\bibitem{LorraineMa}
Lok Wan Lorraine Ma, 
\cq{Mathematical Methods for
2D-3D Cardiac Image Registration}.
Dissertation, University of Ontario Institute of Technology, 2016
\biburl{https://ir.library.dc-uoit.ca/xmlui/bitstream/handle/10155/756/Ma_Lok_Wan_Lorraine.pdf}


\bibitem{LovchikEtAl}
Robert D. Lovchik, \textit{et al.}, 
\cq{Rapid Micro-Immunohistochemistry}.
\bibtitle{Microsystems \& Nanoengineering}, Volume 6 (2020).
\biburl{https://www.nature.com/articles/s41378-020-00205-2.pdf}  


\bibitem{LubnerEtAl}
Meghan G. Lubner, \textit{et al.}, 
\cq{CT Texture Analysis: Definitions,
Applications, Biologic Correlates, and Challenges}.
\bibtitle{RadioGraphics}, Volume 37, Number 5 (2017).
\biburl{https://pubs.rsna.org/doi/full/10.1148/rg.2017170056}  




\bibitem{TimoMakela}
TimoM\"akel\"a, \i{et al.}, 
\cq{A Review of Cardiac Image Registration Methods}.
\bibtitle{IEEE Transactions on Medical Imaging}, 
Volume 21, Number 9 (2002), pages 1011-1021.
\biburl{https://pubmed.ncbi.nlm.nih.gov/12564869/}


\bibitem{CarlosMartinIsla}
Carlos Martin-Isla, \i{et al.}, 
\cq{Image-Based Cardiac Diagnosis With
Machine Learning: A Review}.
\bibtitle{Frontiers in Cardiovascular Medicine}, 2020.
\biburl{https://www.frontiersin.org/articles/10.3389/fcvm.2020.00001/full}



\bibitem{MejinoJr}
Jose L.V. Mejino, Jr, \i{et al.}, 
\cq{FMA-RadLex: An Application Ontology of Radiological Anatomy derived from the Foundational Model of Anatomy Reference Ontology}.
\bibtitle{AMIA Symposium}, 2008, pages 465-469.
\biburl{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC2656009}


\bibitem{OlegMilberg}
Oleg Milberg, \i{et al.}, 
\cq{A QSP Model for Predicting Clinical Responses to Monotherapy,
Combination and Sequential Therapy Following CTLA-4, PD-1,
and PD-L1 Checkpoint Blockade}.
\bibtitle{Frontiers in Cardiovascular Medicine}, 2020.
\biburl{https://www.frontiersin.org/articles/10.3389/fcvm.2020.00001/full}


\bibitem{NagornovKato}
Iurii S. Nagornov and Mamoru Kato, 
\cq{tugHall: A simulator of cancer-cell evolution based on the
hallmarks of cancer and tumor-related genes}.
\bibtitle{Bioinformatics}, Volume 36, Number 11 (2020), pages 
3597-3599.
\biburl{https://pubmed.ncbi.nlm.nih.gov/32170925}


\bibitem{SandyNapel}
Sandy Napel, \i{et al.},
\cq{Quantitative Imaging of Cancer in the Postgenomic Era: Radio(geno)mics, deep learning, and habitats}.
\bibtitle{Cancer}, 
Volume 124 (2018), pages 4633-4649.
\biburl{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6482447}


\bibitem{AnjaNilsen}
Anja Nilsen, \i{et al.},
\cq{Reference MicroRNAs for RT-qPCR Assays in Cervical 
Cancer Patients and Their Application to Studies of 
HPV16 and Hypoxia Biomarkers}.
\bibtitle{Translational Oncology}, 
Volume 12, Number 3 (2019), pages 576-584.
\biburl{https://pubmed.ncbi.nlm.nih.gov/30660934}

\bibitem{OuSchuh}
Yangming Ou and Andreas Schuh,  
\cq{DRAMMS Software Manual}.
\biburl{https://www.cbica.upenn.edu/sbia/software/dramms/_downloads/DRAMMS_Software_Manual.pdf}

\bibitem{YangmingOu}
Yangming Ou, \i{et al.},  
\cq{Validation of DRAMMS among 12 Popular Methods in CrossSubject Cardiac MRI Registration}.
In \intitle{Workshop of Biomedical Image Registration}, 
Proceedings 2012, pages 209-219.
\biburl{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5462118/pdf/nihms861246.pdf}


\end{minipage}

\begin{minipage}{.95\columnwidth}

\bibitem{NikolaosPapanikolaou}
Nikolaos Papanikolaou, \i{et al.},  
\cq{How to Develop a Meaningful Radiomic Signature 
for Clinical Use in Oncologic Patients}.
\bibtitle{Cancer Imaging}, 
Volume 20 (2020).
\biburl{https://cancerimagingjournal.biomedcentral.com/articles/10.1186/s40644-020-00311-4}


\bibitem{IacopoPetrini}
Iacopo Petrini, \i{et al.},  
\cq{ED-B Fibronectin Expression is a Marker of Epithelial-Mesenchymal Transition in Translational Oncology}.
\bibtitle{Oncotarget}, 
Volume 8, Number 3 (2017), pages 4914-4921.
\biburl{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5354880}



\bibitem{PowathilEtAl}
Gibin G. Powathil, \i{et al.},  
\cq{Systems Oncology: Towards patient-specific treatment regimes
informed by multiscale mathematical modelling}.
\bibtitle{Seminars in Cancer Biology}, 
2015, pages 13-20.
\biburl{https://pubmed.ncbi.nlm.nih.gov/24607841}


\bibitem{PuyolEtAl}
Esther Puyol-Ant\'on, \i{et al.},
\cq{A Multimodal Spatiotemporal Cardiac Motion Atlas from MR and Ultrasound Data}.
\bibtitle{Medical Image Analysis}, Volume 40 (2017). 
\biburl{https://www.sciencedirect.com/science/article/pii/S1361841517300890}


\bibitem{ZahraRaisiEstabraghPetersen}
Zahra Raisi-Estabragh and Steffen E. Petersen, 
\cq{Cardiovascular Research Highlights from the UK
Biobank: Opportunities and challenges}.
\bibtitle{Cardiovascular Research}, Volume 116, Number 1 
(2020), pages e12-e15.
\biburl{https://academic.oup.com/cardiovascres/article/116/1/e12/5645361}


\bibitem{StefaniaRizzo}
Stefania Rizzo, \i{et al.},
\cq{Radiomics: The facts and the challenges of image analysis}.
\bibtitle{European Radiology Experimental}, Volume 2 (2018).
\biburl{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6234198/}



\bibitem{FelipeRomero}
Felipe Romero, 
\cq{Philosophy of Science and the Replicability Crisis}.
\bibtitle{Philosophy Compass}, Volume 14, Number 11 
(2019).
\biburl{https://onlinelibrary.wiley.com/doi/full/10.1111/phc3.12633}


\bibitem{AbbasShirinifard}
Abbas Shirinifard, \i{et al.},
\cq{3D Multi-Cell Simulation of Tumor Growth and
Angiogenesis}.
\bibtitle{PLoS One}, 2009.
\biburl{https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0007190}


% lamin ...
\bibitem{SmithEtAl}
Elizabeth R. Smith \textit{et al.}, 
\cq{New Biological Research and Understanding of Papanicolaou's Test}
\bibtitle{Diagnostic Cytopathology}, Volume 46, Number 6 (2018), pages 507-515.
\biburl{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5949091/}


\bibitem{SorensenHorsman}
Brita Singers S{\o}rensen and Michael R. Horsman,
\cq{Tumor Hypoxia: Impact on Radiation
Therapy and Molecular Pathways}.
\bibtitle{Frontiers in Oncology}, 2020.
\biburl{https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0007190}


% look 
\bibitem{JieSu}
Jie Su, \i{et al.}, 
\cq{Automatic Detection of Cervical Cancer Cells by a Two-Level
Cascade Classification System}.
\bibtitle{Analytical Cellular Pathology}, Volume 2016.
\biburl{https://www.hindawi.com/journals/acp/2016/9535027}


\bibitem{TangEtAl}
Jing Rui Tang, \textit{et al.}, 
\cq{Evaluating Nuclear Membrane Irregularity for 
the Classification of Cervical Squamous Epithelial Cells}
\bibtitle{PLOS One}, 2016.
\biburl{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5065206/pdf/pone.0164389.pdf}


\bibitem{GiacomoTarroni}
Giacomo Tarroni, \i{et al.}, 
\cq{Large-scale Quality Control of Cardiac Imaging in Population
Studies: Application to UK Biobank}.
\bibtitle{Nature Scientific Reports}, 2020.
\biburl{https://www.nature.com/articles/s41598-020-58212-2.pdf}


\bibitem{TomaszewskiGillies}
Michal R. Tomaszewski and Robert J. Gillies, 
\cq{The Biological Meaning of Radiomic Features}.
\bibtitle{Radiology}, 2021.
\biburl{https://pubs.rsna.org/doi/pdf/10.1148/radiol.2021202553}



\bibitem{PaulVanLiedekerke}
Paul Van Liedekerke, \i{et al.}, 
\cq{Simulating Tissue Mechanics with Agent-Based Models: Concepts, perspectives and some novel results}.
\bibtitle{Computational Particle Mechanics}, Volume 2 (2015), 
pages 401-444.
\biburl{https://link.springer.com/article/10.1007/s40571-015-0082-3}



\bibitem{MaolinXu}
Maolin Xu, \i{et al.},
\cq{An Analysis of Ki-67 Expression in Stage 1 Invasive Ductal Breast Carcinoma Using Apparent Diffusion Coefficient Histograms}
\bibtitle{Quantitative Imaging in Medicine and Surgery}, 
Volume 11, Number 4 (2021), pages 1518-1531.
\biburl{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7930667}


\bibitem{ZhihuiWang}
Zhihui Wang, \i{et al.}, 
\cq{Accelerating Cancer Systems Biology Research through
Semantic Web Technology}, 
Volume 11, Number 4 (2021), pages 1518-1531.
\bibtitle{Wiley Interdisciplinary Review of Systems Biology Medicine}, Volume 5, Number 2 (2013), pages 135-151.
\biburl{https://pubmed.ncbi.nlm.nih.gov/23188758}


%!!
\bibitem{HadiWiputra}
Hadi Wiputra, \i{et al.}, 
\cq{Cardiac Motion Estimation from Medical Images:
A regularisation framework applied
on pairwise image registration
displacement fields}.
\bibtitle{Nature Scientific Reports}, Volume 10 (2020),
\biburl{https://www.nature.com/articles/s41598-020-75525-4.pdf}


\bibitem{HaoZhang}
Hao Zhang, \i{et al.}, 
\cq{The Human Explanted Heart Program: A translational bridge for
cardiovascular medicine}.
\bibtitle{Biochimica et Biophysica Acta (BBA) -- Molecular Basis of Disease}, Volume 1867, Number 1 (2021).
\biburl{https://www.sciencedirect.com/science/article/abs/pii/S0925443920303434}


\bibitem{XingyuZhang}
Xingyu Zhang, \i{et al.}, 
\cq{Atlas-Based Quantification of Cardiac Remodeling Due to Myocardial Infarction}.
\bibtitle{PLOSOne}, 2014.
\biburl{https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0110243}



\bibitem{AlexZwanenburg}
Alex Zwanenburg, \i{et al.}, 
\cq{The Image Biomarker Standardization Initiative: Standardized Quantitative Radiomics for High-Throughput Image-based Phenotyping}.
\bibtitle{Radiology}, Volume 295, Number 2 (2020).
\biburl{https://pubs.rsna.org/doi/10.1148/radiol.2020191145}

\vfill{}

\end{minipage}
%\end{minipage}



}
\end{thebibliography}

