
\let\oldbibitem\bibitem
%\def\bibitem{\vfill\oldbibitem}


%\vspace{1em}

\vspace{-10pt}

\begin{thebibliography}{99}
\phantomsection \label{References}
\addcontentsline{toc}{section}{References}
{\fontfamily{lmtt}\fontsize{8}{8}\selectfont

\setlength{\parskip}{0pt}
\setlength{\itemsep}{3.75pt}

\vspace{13pt}


\begin{minipage}{\columnwidth}
\bibitem{RaubalAdams}
Benjamin Adams and Martin Raubal, 
\cq{A Metric Conceptual Space Algebra}.
\biburl{https://pdfs.semanticscholar.org/521a/cbab9658df27acd9f40bba2b9445f75d681c.pdf}


\bibitem{RaubalAdamsCSML}
\_\_\_\_\_, %Benjamin Adams and Martin Raubal, 
\cq{Conceptual Space Markup Language (CSML): Towards the Cognitive Semantic Web}.
\biburl{http://idwebhost-202-147.ethz.ch/Publications/RefConferences/ICSC_2009_AdamsRaubal_Camera-FINAL.pdf}


\bibitem{JensAllwood}
Jens Allwood, \cq{Semantics as Meaning Determination with
Semantic-Epistemic Operations}, in 
Jens Allwood and Peter G\"ardenfors, eds.,
\intitle{Cognitive Semantics: Meaning and Cognition}, 
John Benjamis 199, pages 12-28.
\biburl{https://benjamins.com/catalog/pbns.55.02all}


\bibitem{ECL}
Giuseppe Attardi,
\cq{The Embeddable Common Lisp}
\biburl{https://common-lisp.net/project/ecl/static/files/papers/ecl-1995-attardi.pdf}

%ch 8
\bibitem{BechbergerKuhnberger}
Lucas Bechberger and Kai-Uwe K\"uhnberger, 
\cq{A Comprehensive Implementation of Conceptual Spaces}.%s
\biburl{http://ceur-ws.org/Vol-2090/paper4.pdf}

\bibitem{LucasBechberger}
\_\_\_\_\_, %Lucas Bechberger and Kai-Uwe K\"uhnberger, 
\cq{Measuring Relations between Concepts in Conceptual Spaces}.%
\biburl{https://arxiv.org/pdf/1707.02292.pdf}

\bibitem{BechbergerKypridemo}
Lucas Bechberger and Elektra Kypridemo, 
\cq{Mapping Images to Psychological Similarity Spaces Using Neural Networks}.
\biburl{http://ceur-ws.org/Vol-2418/paper3.pdf}


\bibitem{BiskriDescles}
Isma{\"\OldI}l Biskri and Jean-Pierre Descles, 
\cq{Applicative and Combinatory Categorial Grammar 
(from syntax to functional semantics)}
\biburl{https://www.researchgate.net/publication/232754402_Applicative_and_Combinatory_Categorial_Grammar_from_syntax_to_functional_semantics}


%ch 8
\bibitem{BleekerEtAl}
Elli Bleeker, \textit{et al.},
\cq{Between Flexibility and Universality: Combining TAGML
and XML to Enhance the Modeling of Cultural Heritage
Text}
\biburl{http://ceur-ws.org/Vol-2723/short39.pdf}

%ch 8
\bibitem{GregCarlson}
Greg Carlson, 
\cq{Thematic Roles and the Individuation of Events}.
\biburl{https://www.sas.rochester.edu/lin/people/faculty/carlson_greg/assets/pdf/them-roles-events.pdf}

\bibitem{Cazzola}
Walter Cazzola, \textit{et al.},
\cq{Semantic Join Point Models:
Motivations, Notions and Requirements}
\biburl{https://hal.inria.fr/inria-00542782/document}

%ch 8
\bibitem{StuartChalk}
Stuart Chalk,
\cq{SciData: A data model and ontology for semantic representation of scientific data}
\bibtitle{Journal of Cheminformatics}, Volume 8 (2016). 
\biburl{https://jcheminf.biomedcentral.com/articles/10.1186/s13321-016-0168-9}

%ch 8
\bibitem{LucasChampollionC}
Lucas Champollion,
\cq{Covert Distributivity in Algebraic Event Semantics}
\bibtitle{Semantics \& Pragmatics}, Volume 9 (2016), pages 1-65. 
\biburl{https://semprag.org/article/view/sp.9.15}


\bibitem{LucasChampollionO}
\_\_\_\_\_,
\cq{Overt Distributivity in Algebraic Event Semantics}
\bibtitle{Semantics \& Pragmatics}, Volume 9 (2016), pages 1-65. 
\biburl{https://semprag.org/article/view/sp.9.16}


%ch 8
\bibitem{ChampollionDissertation}
\_\_\_\_\_,
\cq{Parts of a Whole: Distributivity as a Bridge Between Aspect and Measurement}
Dissertation, University of Pennsylvania, 2010.
\biburl{https://repository.upenn.edu/cgi/viewcontent.cgi?article=2117&context=edissertations}


\bibitem{ChanninEtAl}
David S. Channin, \i{et al.}, 
\cq{The caBIG Annotation and Image Markup Project}.
\bibtitle{Journal of Digit Imaging}, Volume 23, 
Number 2 (2010), pages 217-225.
\biburl{https://pubmed.ncbi.nlm.nih.gov/19294468/}


\bibitem{DavidAClunie}
David A. Clunie, 
\cq{DICOM Structured Reporting}.
\biburl{http://www.dclunie.com/pixelmed/DICOMSR.book.pdf}



\bibitem{BobCoecke}
Bob Coecke,  
\cq{The Mathematics of Text Structure}.
\biburl{https://arxiv.org/pdf/1904.03478.pdf}


\bibitem{InteractingConceptualSpaces}
Bob Coecke, \i{et al.}, 
\cq{Interacting Conceptual Spaces I:
Gram\-matical Composition of Concepts}.\biburl{https://arxiv.org/pdf/1703.08314.pdf}


%ch 8 
\bibitem{BridgetCopley}
Bridget Copley, \cq{Force Dynamics}.
In Robert Truswell (Ed.), 
\intitle{Oxford Handbook of Event Structure}, Oxford, 2019, pages 103-149.%
\biburl{http://bcopley.com/pubs/force-dynamics}.


%ch 8 (SciXML related)
\bibitem{CopestakeEtAl}
Ann Copestake, \i{et al.},
\cq{An Architecture for Language Processing for Scientific
Texts}.
\biburl{https://abdn.pure.elsevier.com/en/publications/an-architecture-for-language-processing-for-scientific-texts}

%ch 8 
\bibitem{PaulaGudwin}
Suelen M. de Paula and Ricardo R. Gudwin,   
\cq{Evolving Conceptual Spaces for Symbol Grounding in
Language Games}.
\bibtitle{Biologically Inspired Cognitive Architectures},
Volume 14 (2015), pages 73-85.
\biburl{https://www.sciencedirect.com/science/article/pii/S2212683X15000493}


\bibitem{DebusmannEtAl}
Ralph Debusmann, \i{et al.},  
\cq{A Relational Syntax-Semantics Interface Based on Dependency Grammar}
\biburl{https://www.aclweb.org/anthology/C04-1026.pdf}

%ch 8 (Tag)
\bibitem{DekkerEtAl}
Ronald Haentjens Dekker, \i{et al.},
\cq{Parsing a Markup Language that Supports Overlap and Discontinuity}.
\biburl{https://dl.acm.org/doi/abs/10.1145/3395027.3419590}

\bibitem{KeithDevlin}
Keith Devlin,
\cq{Situation Theory and Situation Semantics}
\biburl{http://web.stanford.edu/~kdevlin/Papers/HHL_SituationTheory.pdf}

%ch 8 
\bibitem{DietzeDomingue}
Stefan Dietze and John Domingue,   
\cq{Exploiting Conceptual Spaces
for Ontology Integration}.
\biburl{https://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.141.4434&rep=rep1&type=pdf}


\end{minipage}

\begin{minipage}{\columnwidth}

%ch 8 
\bibitem{AndreasFabri}
Andreas Fabri, \i{et al.},
\cq{On the Design of CGAL, the Computational Geometry Algorithms Library}
\biburl{https://core.ac.uk/download/pdf/210674597.pdf}


% ch 8
\bibitem{Fauconnier}
Gilles Fauconnier, \cq{Mental Spaces: Aspects of Meaning Construction in Natural Language}.
Cambridge, 1994


% ch 8
\bibitem{FauconnierTurner}
Gilles Fauconnier and Mark Turner, \cq{The Way We Think: Conceptual Blending and the Mind's Hidden Complexities}.
Basic Books, 2002


% Gardenfors
\bibitem{JohannesFlieger}
Johannes C. Flieger, 
\cq{Gradable Adjectives and the Semantics of Locatives}.
Dissertation, University of Edinburgh, 2009
\biburl{https://era.ed.ac.uk/bitstream/handle/1842/3995/Flieger2009.pdf?sequence=1&isAllowed=y}


\bibitem{JerryFodor}
Jerry Fodor, 
\cq{Language, Thought and Compositionality}.
\bibtitle{Mind and Language}, Volume 16, Issue 1 (2001)
\biburl{https://onlinelibrary.wiley.com/doi/abs/10.1111/1468-0017.00153}



\bibitem{FriedOstman}
Mirjam Fried and Jan-Ola \"Ostman, 
\cq{Construction Grammar: A thumbnail sketch}
\biburl{https://www.researchgate.net/publication/280291354_Construction_Grammar_A_thumbnail_sketch}


\bibitem{GallegoOrus}
\'Angel J. Gallego and Rom\'an Or\'us, 
\cq{Language Design as Information Renormalization}.
\biburl{https://arxiv.org/abs/1708.01525}


\bibitem{Gardenfors}
Peter \Gardenfors{},  
\cq{Does Semantics Need Reality?}
In Alexander Riegler, \i{et al.}, Eds.,
\intitle{Understanding Representation in the Cognitive Sciences.}, 
pages 209-217.
Springer (Boston), 1999.


\bibitem{GardenforsWeb}
\_\_\_\_\_,
\cq{How to Make the Semantic Web More Semantic}.
\biburl{https://slab.org/tmp/Gardenfors04.pdf}

\bibitem{GardenforsInvariances}
\_\_\_\_\_,
\cq{Primary Cognitive Categories Are Determined by Their Invariances}.
\bibtitle{Frontiers in Psychology}, 2020.
\biburl{https://www.frontiersin.org/articles/10.3389/fpsyg.2020.584017/full}

\bibitem{GardenforsEtAl}
Peter \Gardenfors{}, \i{et al.},
\cq{Event Boards as Tools for Holistic AI}.
\biburl{http://ceur-ws.org/Vol-2418/paper1.pdf}

\bibitem{GardenforsWarglien}
Peter \Gardenfors{} and Massimo Warglien,
\cq{Using Conceptual Spaces to Model Actions and Events}.
\bibtitle{Journal of Semantics}, Volume 29, Issue 4 (2012), pages 487-519.  
\biburl{https://www.researchgate.net/publication/274999478_Using_Conceptual_Spaces_to_Model_Actions_and_Events}


\bibitem{Zenker}
Peter \Gardenfors{} and Frank Zenker,  
\cq{Theory Change as Dimensional Change: Conceptual Spaces 
	Applied to the Dynamics of Empirical Theories}.
\bibtitle{Synthese 190}, Volume 6 (2013), pages. 1039-1058.  
\biburl{http://lup.lub.lu.se/record/1775234}

\bibitem{GabrielGaudreault}
Gabriel Gaudreault, 
\cq{Derivational Event Semantics for Pregroup Grammars}.
Dissertaion, Concordia University, Montreal, 2016.
\biburl{https://spectrum.library.concordia.ca/981873/9/Gaudreault_MA_F2016.pdf}



\bibitem{GayoEtAl}
Jose Emilio Labra Gayo, \i{et al.}, 
\cq{Validating and Describing Linked Data Portals using
Shapes}.%
\biburl{https://arxiv.org/pdf/1701.08924.pdf}

\bibitem{JosephGoguen}
Joseph Goguen, 
\cq{An Introduction to Algebraic Semiotics, with Application to User Interface Design}.
In Nehaniv, C. (ed.), 
\intitle{Computation for Metaphors, Analogy, and Agents}, Springer, 1999, pages 242-9.%
\biburl{https://cseweb.ucsd.edu/~goguen/pps/as.pdf}

\bibitem{GustUmbach}
Helmar Gust and Carla Umbach,
\cq{A Qualitative Similarity Framework for the
Interpretation of Natural Language Similarity
Expressions}.
In Lucas Bechberger, \i{et al.} (Eds.),
\intitle{Concepts in Action -- Representation, Learning, and Application}, 
Springer 2021.
\biburl{http://www.carla-umbach.de/publications/Gust&Umbach_QualitativeSimilarityFramework.pdf}

\bibitem{ThomasHartmann}
Thomas Hartmann,
\cq{Validation Framework for RDF-based Constraint Languages}
Dissertation, Karlsruhe, 2016.
\biburl{https://www.semanticscholar.org/paper/Validation-Framework-for-RDF-based-Constraint-Hartmann/aff416d1e971fb55ea405a1967619263fbe8be9e}


\bibitem{RamsonHirschfeld}
Stefan Ramson and Robert Hirschfeld,
\bibtitle{Active Expressions: Basic Building Blocks for Reactive Programming}.
\biburl{https://arxiv.org/abs/1703.10859}


\bibitem{HovavLevin}
Malka Rappaport Hovav and Beth Levin,  
\cq{The Syntax-Semantics Interface}.
In Shalom Lappin and Chris Fox (Eds.), 
\intitle{The Handbook of Contemporary Semantic Theory},
Wiley 2015, chapter 19, pages 593-624.
\biburl{https://onlinelibrary.wiley.com/doi/pdf/10.1002/9781118882139.ch19}



\bibitem{CorentinJabot}
Corentin Jabot, 
\cq{Strongly-Typed Reflection on Attributes}
\biburl{http://open-std.org/JTC1/SC22/WG21/docs/papers/2019/p1887r0.pdf}


\bibitem{TFlorianJaeger}
T. Florian Jaeger, 
\cq{Redundancy and Reduction: 
Speakers manage syntactic information density}.
\bibtitle{Cognitive Psycholology}, Volume 61 (2010), 
Number 1, pages 23–62.
\biburl{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC2896231/}

\bibitem{WolfgangJeltsch}
Wolfgang Jeltsch, 
\bibtitle{Categorical Semantics for Functional Reactive 
Programming with Temporal Recursion and Corecursion}.
\tinyurl{https://arxiv.org/pdf/1406.2062.pdf}

\bibitem{KloseOstermann}
Karl Klose and Klaus Ostermann,
\cq{A Classification Framework for Pointcut
Languages in Runtime Monitoring}.
\biburl{https://link.springer.com/chapter/10.1007/978-3-642-02571-6_17}

\bibitem{MichaelisLambrech}
Laura A. Michaelis and Knud Lambrech, \cq{Toward a Construction-Based Theory of Language Function: The Case of Nominal Extraposition}
\biburl{https://spot.colorado.edu/~michaeli/documents/Michaelis_Lambrecht_NE_LG.pdf}


\bibitem{LevinHovav}
Beth Levin and Malka Rappaport Hovav,  
\cq{Lexicalized Meaning and Manner/Result Complementarity}.
\biburl{https://web.stanford.edu/~bclevin/barcel11rev.pdf}


%\bibitem{KohliEtAl}
%Mark D. Kohli, \i{et al.},
%\cq{Medical Image Data and Datasets in the Era of Machine
%Learning --- Whitepaper from the 2016 C-MIMI Meeting}
%\bibtitle{Journal of Digit Imaging}, 2017.
%\biburl{https://d-nb.info/1132883164/34}


\bibitem{KorenblumEtAl}
Daniel Korenblum, \i{et al.}, 
\cq{Managing Biomedical Image Metadata for Search and Retrieval
of Similar Images}.
\bibtitle{Journal of Digital Imaging}, Volume 24, Number 4 (2011), 
pages 739-748.
\biburl{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3138941/}


\bibitem{KubotaLevine}
Yusuke Kubota and Robert Levine,
\cq{The Syntax-Semantics Interface of \sq{Respective} Predication:
A unified analysis in Hybrid Type-Logical Categorial Grammar}
\biburl{https://www.asc.ohio-state.edu/levine.1/publications/kl-resp.pdf}

\end{minipage}




%\setlength{\itemsep}{6pt}

%\vspace{1em}
\begin{minipage}{\columnwidth}

%\vspace{3pt}
\bibitem{LangackerIntro}
Ronald Langacker, 
\cq{Cognitive Grammar: A Basic Introduction}.  
Oxford, 2008.



\bibitem{LangackerInteractive}
\_\_\_\_\_, 
\cq{Interactive Cognition: 
Toward a Unified Account of Structure, Processing, and Discourse}.  
In \intitle{International Journal of Cognitive Linguistics}, 
Volume 3, Number 2, 2014.  
\biburl{http://lchc.ucsd.edu/MCA/Mail/xmcamail.2014-08.dir/pdf8jEY9UCVVh.pdf}

\bibitem{LangackerPresent}
\_\_\_\_\_, 
\cq{The English Present: Temporal coincidence vs. epistemic immediacy}.
In Adeline Patard and Frank Brisard, Eds.,
\intitle{Cognitive Approaches to Tense, Aspect, and Epistemic Modality} 
(John Benjamins, 2011). 
\biburl{https://benjamins.com/catalog/hcp.29.06lan}


%ch 8
\bibitem{IanLewin}
Ian Lewin, 
\cq{Using Hand-Crafted Rules and Machine Learning to Infer SciXML Document Structure}.  
\biburl{https://www.semanticscholar.org/paper/Using-hand-crafted-rules-and-machine-learning-to-Lewin/3dd2756e42ae24df0769711c3b7a55249d7b17cf}

\bibitem{LawryTang}
Jonathan Lawry and Yongchuan Tang, 
\cq{Uncertainty Modelling for Vague Concepts: A prototype theory approach}.  
\biburl{https://www.sciencedirect.com/science/article/pii/S0004370209000903}


\bibitem{LewisLawry}
Martha Lewis and Jonathan Lawry, 
\cq{Hierarchical Conceptual Spaces for Concept Combination}.  
\biburl{https://www.sciencedirect.com/science/article/pii/S0004370216300492}

\bibitem{LiCunningham}
Yaoyong Li and Hamish Cunningham, 
\cq{Geometric and Quantum Methods for
Information Retrieval}.  
In \intitle{Association for Computing Machinery Forum}, New York, 
Volume 42, Number 2, 2008, pages 22-32.
\biburl{https://dl.acm.org/doi/10.1145/1480506.1480510}



\bibitem{IlyaMakarov}
Ilya Makarov, \i{et al.},
\cq{Quantum Logic and Natural Language Processing}.  
\biburl{http://ceur-ws.org/Vol-1886/paper_16.pdf}

%ch 8
\bibitem{PeterMcQuilton}
Peter McQuilton, \i{et al.},
\cq{BioSharing: Curated and crowd-sourced
metadata standards, databases and data
policies in the life sciences}.
\bibtitle{Database}, Volume 2016.
\biburl{https://pdfs.semanticscholar.org/504a/e934c99ed5cbd4ea925ec13ebf86f553e251.pdf}


\bibitem{Meichanetzidis}
Konstantinos Meichanetzidis, \i{et al.}, 
\cq{Quantum Natural Language Processing on Near-Term Quantum Computers}
\biburl{https://arxiv.org/abs/2005.04147}


\bibitem{FriederikeMoltmann}
Friederike Moltmann, 
\cq{Parts and Wholes in Semantics}.
Oxford University Press, 1997.\biburl{https://www.researchgate.net/publication/244487318}

%`cite<DanielLRubin>;,  `cite<KohliEtAl>;,

\bibitem{PattanasakMongkolwat}
Pattanasak Mongkolwat, \i{et al.}, 
\cq{The National Cancer Informatics Program (NCIP) Annotation
and Image Markup (AIM) Foundation Model}
\bibtitle{Journal of Digit Imaging}, Volume 27 (2014), pages 692-701.
\biburl{https://europepmc.org/backend/ptpmcrender.fcgi?accid=PMC4391072&blobtype=pdf}



%ch 8 (CRole related)
\bibitem{CarlosMontemayor}
Carlos Montemayor, \textit{et al.}, 
\cq{Implementation, Formalization and Representation: Challenges for the Integrated
Information Theory}.
\bibtitle{Journal of Consciousness Studies}, 
Volume 26, Numbers 1-2 (2019), pages 107-132.
\biburl{http://online.sfsu.edu/barros/publications/publications/files/MontemayorEtAl2019.pdf}


%ch 8 ccg
\bibitem{ErwanMoreau}
Erwan Moreau,
\cq{From Link Grammars to Categorial Grammars}.
In \intitle{Proceedings of Categorial Grammars 2004}, pages 31-45.
\biburl{https://hal.archives-ouvertes.fr/hal-00487053/document}


%ch 8 (IeXML related)
\bibitem{TiagoNunes}{%
Tiago Nunes, \i{et al.},
\q{BeCAS: biomedical concept recognition services and visualization}.\biburl{https://www.ncbi.nlm.nih.gov/pubmed/23736528}}

\bibitem{LJOriordon}
Lee J O'Riordan, \i{et al.},
\cq{A Hybrid Classical-Quantum Workflow for 
Natural Language Processing}.
Machine Learning: Science and Technology, Volume 2 (2021).
\biburl{https://iopscience.iop.org/article/10.1088/2632-2153/abbd2e/pdf}


%ch 8
\bibitem{MatiasOstaVelez}
\MatiasOstaVelez{}, 
\cq{Inference and the Structure of Concepts}.
Dissertation, Ludwig-Maximilians-University, 2020.
\biburl{https://edoc.ub.uni-muenchen.de/27633/7/Osta_Velez_Matias.pdf}

\bibitem{ParadowskiEtAl}
Mariusz Paradowski, \i{et al.},
\cq{Capillary Blood Vessel Tracking Using Polar Coordinates Based Model Identification}.
\bibtitle{Computer Recognition Systems}, Volume 3, pages 499-50.
\biburl{https://link.springer.com/chapter/10.1007/978-3-540-93905-4_59}


\bibitem{ParetiEtAl}
Paolo Pareti, \i{et al.}, 
\cq{SHACL Constraints with Inference Rules
Paolo Pareti}.
In C. Ghidini, \i{et al.} (Eds.),
\intitle{International Semantic Web Conference 2019}, 
pages 539–557.
\biburl{https://www.southampton.ac.uk/~gk1e17/shacl-inference.pdf}

\bibitem{WalterPedriali}
Walter B. Pedriali, 
\cq{The Routes of Sense: Thought, semantic inderdeterminacy and compositionality}.
Dissertation, St. Andrews University, 2011.
\biburl{https://research-repository.st-andrews.ac.uk/handle/10023/3142}

\bibitem{JoeyPollack}
Joey Pollack, \cq{Holism, Conceptual Role, and Conceptual Similarity}.
\biburl{https://www.tandfonline.com/doi/abs/10.1080/09515089.2020.1729973?journalCode=cphp20}


\bibitem{MartinRaubal}
Martin Raubal,
\cq{Formalizing Conceptual Spaces}.
\biburl{http://www.raubal.ethz.ch/Courses/288MR_Spring08_Papers/Raubal_FormalizingConceptualSpaces_FOIS04.pdf}

%ch 8
\bibitem{DietrichRebholzSchuhman}{%
Dietrich Rebholz-Schuhman, \i{et al.},
\cq{IeXML: Towards an annotation framework for biomedical semantic types enabling interoperability of text processing modules}.
\biburl{https://www.semanticscholar.org/paper/IeXML\%3A-towards-an-annotation-framework-for-semantic-Rebholz-Schuhmann-Kirsch/1d72a56b6576117c62f388a5f2193965e4c7e293}}


%ch 8
\bibitem{JohnTRickard}
John T. Rickard,
\cq{A Concept Geometry for Conceptual Spaces}.
\bibtitle{Fuzzy Optimization and Decision Making}, Volume 5 (2006),
pages 311-329. 
\biburl{https://altexploit.files.wordpress.com/2017/06/a-concept-geometry-for-conceptual-spaces.pdf}


%ch 8
\bibitem{BradleyRives}
Bradley Rives, 
\cq{The Empirical Case Against Analyticity: Two Options for Concept Pragmatists}.
\biburl{https://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.188.9556&rep=rep1&type=pdf}


\bibitem{Rossi}
Aur\'elie Rossi, \cq{Applicative and Combinatory Categorial 
Grammar: Analysis of the French Interrogative Sentences}.
\bibtitle{FLAIRS Conference, Association for the Advancement of Artificial
Intelligence}, 2008.
\biburl{https://www.aaai.org/Papers/FLAIRS/2008/FLAIRS08-118.pdf}


\end{minipage}

\begin{minipage}{\columnwidth}

%\end{minipage}

% or https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3138941/pdf/10278_2010_Article_9328.pdf ??

%\bibitem{DanielLRubin}
%Daniel L. Rubin, 
%\cq{Finding the Meaning in Images: Annotation and Image Markup}.
%\bibtitle{Philosophy, Psychiatry, & Psychology}, Volume 18, Number 4 (2011), pages 311-318.
%\biburl{https://web.stanford.edu/group/rubinlab/pubs/18.4.rubin.pdf}

\bibitem{RubinSupekar}
Daniel L. Rubin and Kaustubh Supekar, 
\cq{Annotation and Image Markup: Accessing and Interoperating 
with the Semantic Content in Medical Imaging}.
\bibtitle{Intelligent Systems}, Volume 24, Number 1 (2009), pages 57-65.
\biburl{https://web.stanford.edu/group/rubinlab/pubs/Rubin-IEEEIntelSys-2009.pdf}


%ch 8
\bibitem{CJRupp}{%
C. J. Rupp, \i{et al.},
\q{Flexible Interfaces in the Application of Language Technology to an eScience Corpus}.
\biburl{https://www.cl.cam.ac.uk/~sht25/papers/Rupp_et_al.pdf}}

%ch 8 (CRole)
\bibitem{DanRyder}
Dan Ryder, 
\cq{Problems of representation II: Naturalizing content}.
In \intitle{The Routledge Companion to Philosophy of Psychology}, 
Routledge 2009, pages 251-279.
\biburl{https://www.semanticscholar.org/paper/Problems-of-representation-II\%3A-naturalizing-content-Ryder/1073bf288423e3e9b1940628cb2deb7db8b8fae2}



\bibitem{VahidSalari}
Vahid Salari, \i{et al.}, 
\cq{Parametrized Quantum Circuits of Synonymous
Sentences in Quantum Natural Language
Processing}.\biburl{https://assets.researchsquare.com/files/rs-220713/v1_stamped.pdf}


%ch 8 (SciXML related)
\bibitem{SateliWitte}
Bahar Sateli and Ren\'e Witte,
\cq{Semantic Representation of Scientific
Literature: Bringing claims, contributions
and named entities onto the Linked Open
Data cloud}.
\bibtitle{PeerJ Computer Science}, 2015.
\biburl{https://peerj.com/articles/cs-37.pdf}



\bibitem{Schafmeister}
Christian Schafmeister and Alex Wood,
\cq{Clasp Common Lisp Implementation and Optimization}.
\biburl{https://dl.acm.org/doi/10.5555/3323215.3323223}


%ch 8 (IeXML related)
\bibitem{PedroSernadela}
Pedro Sernadela and Jos\'e Luís Oliveira,
\cq{A Semantic-Based Workflow for Biomedical Literature Annotation}
\bibtitle{Database}, Volume 2017.
\biburl{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5691355/}

% AIM
\bibitem{SchaerEtAl}
Roger Schaer, \i{et al.},
\cq{Web-Based Tools for Exploring the Potential of Quantitative Imaging
Biomarkers in Radiology: 
Intensity and Texture Analysis on the ePAD Platform}.
In Adrien Depeursinge, \i{et al.} (Eds), 
\intitle{Biomedical Texture Analysis: Fundamentals, 
Tools, and Challenes}, Academic Press, 2017.
\biburl{http://bigwww.epfl.ch/publications/schaer1701.pdf}


%ch 8
\bibitem{FrankAndreasSposito}
Frank Andreas Sposito,
\cq{What Do Data Curators Care About? Data quality, user trust, and the data
reuse plan}
\biburl{http://library.ifla.org/1797/1/S06-2017-sposito-en.pdf}

%ch 8
\bibitem{GregorStrle}
Gregor Strle, \cq{Semantics Within: The Representation of Meaning Through Conceptual Spaces}.  
Dissertation, Novi Gorici, 2012.\biburl{http://www.ung.si/~library/doktorati/interkulturni/25Strle.pdf}

%ch 8
\bibitem{TammaroEtAl}
Anna Maria Tammaro, \i{et al.}, 
\cq{Data Curator's Roles and Responsibilities:
An International Perspective}
\bibtitle{Libri}, Volume 69, Issue 2 (2019).
\biburl{https://www.degruyter.com/document/doi/10.1515/libri-2018-0090/html}

\bibitem{MiriamTaverniers}
Miriam Taverniers, \cq{Subjecthood and the Notion of Instantiation}.
\biburl{https://semanticsarchive.net/Archive/DU0OGRkO/Taverniers-2005-Subjecthood-PREPRINT.pdf}


%ch 8
\bibitem{ChrisTaylor}
Chris F. Taylor, \i{et al.},
\cq{Promoting Coherent Minimum Reporting Guidelines for Biological and Biomedical Investigations: The MIBBI project}.
\bibtitle{Nature Biotechnology}, Volume 26 (2008), pages 
889-896.
\biburl{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC2771753/}

\bibitem{teleaVission}
Alexandru Telea and Jarke J. van Wijk,
\cq{VISSION: An Object Oriented Dataflow System for Simulation and Visualization}.
\biburl{https://pure.rug.nl/ws/portalfiles/portal/3178139/1999ProcVisSymTelea.pdf}



%ch 8
\bibitem{SimoneTeufel}
Simone Teufel and Min-Yen Kan
\cq{Robust Argumentative Zoning for Sensemaking
in Scholarly Documents}.
In R. Bernardi, \i{et al.} (Eds.) 
\intitle{NLP4DL/AT4DL} (Advanced Language Technologies for Digital Libraries) 2009, 
pages 154-170.
\biburl{http://people.cs.pitt.edu/~litman/courses/nus062615/readings/TeufelKan.pdf}


%ch 8
\bibitem{TeufelEtAl}
Simone Teufel, \i{et al.}
\cq{An Annotation Scheme for Discourse-Level Argumentation in Research Articles}.
\bibtitle{Ninth Conference of the European Chapter of the Association for Computational Linguistics}, 1999, pages 110-117.
\biburl{https://www.aclweb.org/anthology/E99-1015/}


\bibitem{UrbanGrzelinska}
Roman Urban and Megdalena Grzelinska, 
\cq{A Potential Theory Approach to an Algorithm of Conceptual
Space Partitioning}.  In 
\intitle{Cognitive Studies}, Volume 1 (2017).
\biburl{https://ispan.waw.pl/journals/index.php/cs-ec/article/download/cs.1310/3065}


\bibitem{JuanUriagereka}
Juan Uriagereka, 
\cq{Syntactic Anchors: On Semantic Structuring}.
Cambridge University Press, 2008.
\biburl{https://assets.cambridge.org/97805218/65326/frontmatter/9780521865326_frontmatter.pdf}


\bibitem{KrisVerlaenen}
Kris Verlaenen, 
\cq{Middleware for Advanced Service Configuration: a Policy-Based
Approach}.
Dissertation, Leuven, 2008.
\biburl{https://www.cs.kuleuven.be/publicaties/doctoraten/cw/CW2008_07.pdf}



%ch 8
\bibitem{RalfVogel}
Ralf Vogel, \cq{Polyvalent Verbs}.
Dissertation, Humbolt University, 1998.
\biburl{https://edoc.hu-berlin.de/bitstream/handle/18452/15160/Vogel.pdf?sequence=1}



\bibitem{vanTrijp}
Remi van Trijp, 
\cq{Cognitive vs. Generative Construction
Grammar: The case of coercion and
argument structure}.  
\bibtitle{Cognitive Linguistics}, Volime 26, Issue 4 (2015), pages 613-632.
\biburl{https://www.degruyter.com/document/doi/10.1515/cog-2014-0074/html}


\bibitem{WarglienEtAl}
Massimo Warglien, Peter \Gardenfors{}, and Matthijs Westera,
\cq{Event Structure, Conceptual Spaces and the
Semantics of Verbs}.
\bibtitle{Theoretical Linguistics}, Volume 37 (2012), pages 159-193.  
\biburl{https://iris.unive.it/retrieve/handle/10278/37082/27662/semantics_of_verbs.pdf}

\bibitem{FrankZenker}
Frank Zenker,
\cq{From Features via Frames to Spaces: Modeling Scientific Conceptual Change Without Incommensurability or Aprioricity}.
In Thomas Gamerschlag, \i{et al.} (Eds.), 
\intitle{Frames and Concept Types: Applications in Language and Philosophy}, 
Springer, 2014, pages 69-89.  
\biburl{https://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.901.7852&rep=rep1&type=pdf}
\end{minipage}{\columnwidth}



\vfill{}




}
\end{thebibliography}
