
\let\oldbibitem\bibitem
%\def\bibitem{\vfill\oldbibitem}


%\vspace{1em}

\vspace{-10pt}

\begin{thebibliography}{99}
\phantomsection \label{References}
\addcontentsline{toc}{section}{References}
{\fontfamily{lmtt}\fontsize{8}{8}\selectfont

\setlength{\parskip}{0pt}
\setlength{\itemsep}{3.75pt}

\vspace{13pt}



\bibitem{EnriqueMartinezBerti}
Enrique Martinez Berti, \i{et al.}, 
\cq{Dual Quaternions as Constraints in 4D-DPM Models
for Pose Estimation}.
\bibtitle{Sensors}, Volume 17, 2017, 
\biburl{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5579524/}


%\bibitem{ChakraChennubhotla}
%Chakra Chennubhotla, \i{et al.},
%\cq{An Assessment of Imaging Informatics for Precision Medicine in Cancer}.
%\biburl{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6250996/}


\bibitem{DmitryCherezov}
Dmitry Cherezov, \i{et al.}, 
\cq{Revealing Tumor Habitats from
Texture Heterogeneity Analysis
for Classification of Lung Cancer
Malignancy and Aggressiveness}.
\bibtitle{Scientific Reports}, Volume 9, 2019.
\biburl{https://www.nature.com/articles/s41598-019-38831-0}


\bibitem{AnthonyJConnor}
Anthony J. Connor, \textit{et al.}, 
\cq{Object-Oriented Paradigms for Modelling Vascular Tumour Growth: A Case Study}.
\bhref{https://people.maths.ox.ac.uk/maini/PKM\%20publications/354.pdf}


\bibitem{PrashantDogra}
Prashant Dogra, \textit{et al.}, 
\cq{Mathematical Modeling in Cancer Nanomedicine: A review}  
\biburl{https://link.springer.com/article/10.1007/s10544-019-0380-2}



%% angiogenesis data fields ...
\bibitem{MarieLaureBoizeau}
Marie-Laure Boizeau, \textit{et al.}, 
\cq{Automated Image Analysis of In Vitro
Angiogenesis Assay}.
\bibtitle{Journal of Laboratory Automation}, 
Volume 18, pages 411-415.
\biburl{https://journals.sagepub.com/doi/pdf/10.1177/2211068213495204}


%% angiogenesis data fields ...
\bibitem{CharalamposNDoukas}
Charalampos N. Doukas, \textit{et al.}, 
\cq{Automated Angiogenesis Quantification through Advanced Image
Processing Techniques}.
\biburl{https://pubmed.ncbi.nlm.nih.gov/17946107/}


\bibitem{JosefEhling}
Josef Ehling, \textit{et al.}, 
\cq{Micro-CT Imaging of Tumor Angiogenesis: 
Quantitative Measures Describing Micromorphology and
Vascularization}.
\bibtitle{Biophysical Imaging and Computational Biology}, 
Volume 184, Number 2 (2014), pages 431-441.
\biburl{https://www.sciencedirect.com/science/article/pii/S0002944013007268}


%% WSI.  Include?
\bibitem{Farahani}{%
Farahani N, \textit{et al.}, 
\cq{Whole Slide Imaging in Pathology: Advantages, limitations, and emerging perspectives}.
\biburl{https://www.dovepress.com/whole-slide-imaging-in-pathology-advantages-limitations-and-emerging-p-peer-reviewed-article-PLMI}}


\bibitem{GrazzielaPFigueredo}
Grazziela P. Figueredo, \textit{et al.}, 
\cq{On-Lattice Agent-Based Simulation of Populations of Cells Within the
Open-Source Chaste Framework}.
\biburl{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3638480/}


% NE Protein Expression Is Altered in Many Human tumors
\bibitem{EdgarGFischer}
Edgar G. Fischer, 
\cq{Nuclear Morphology and the Biology of Cancer Cells}.
\bibtitle{Acta Cytologica}, Volume 64 (2020), pages 511-519. 
\biburl{https://www.karger.com/Article/Pdf/508780}


\bibitem{DavidJuncker}
David Juncker, \textit{et al.}, 
\cq{Multipurpose Microfluidic Probe}.
\bibtitle{Nature Materials}, Volume 4, Issue 8 (2005), pages 622-628.
\biburl{https://pubmed.ncbi.nlm.nih.gov/16041377/}



\bibitem{AdityaKashyap}
Aditya Kashyap, \i{et al.}, 
\cq{Quantitative Microimmunohistochemistry for the Grading of Immunostains on Tumour Tissues}.
\bibtitle{Nature Biomedical Engineering}, Volume 3 (2019), pages 478-490.
\biburl{https://www.nature.com/articles/s41551-019-0386-3}




\bibitem{JakobNikolasKather}
Jakob Nikolas Kather, \textit{et al.}, 
\cq{Continuous Representation of Tumor Microvessel 
Density and Detection of Angiogenic Hotspots in 
Histological Whole-Slide Images}.
\biburl{https://www.oncotarget.com/article/4383/text/}


\bibitem{HuiLi}
Hui Li, \i{et al.}, 
\cq{Quantitative MRI Radiomics in the Prediction of Molecular Classifications of Breast Cancer Subtypes in the TCGA/TCIA Data Set}.
\bibtitle{NPJ Breast Cancer}, Volume 2016, Number 2.
\biburl{https://www.nature.com/articles/npjbcancer201612.pdf}


\bibitem{YangLi}
Yang Li, \i{et al.}, 
\cq{4DComplete: Non-Rigid Motion Estimation Beyond the Observable Surface}.
\biburl{https://arxiv.org/abs/2105.01905}


\bibitem{PaulVanLiedekerke}
Paul Van Liedekerke, \textit{et al.}, 
\cq{Simulating Tissue Mechanics with Agent-Based Models: Concepts, perspectives and some novel results}.
\biburl{https://link.springer.com/article/10.1007/s40571-015-0082-3}


\bibitem{LovchikEtAl}
Robert D. Lovchik, \textit{et al.}, 
\cq{Rapid Micro-Immunohistochemistry}.
\bibtitle{Microsystems \& Nanoengineering} Volume 6 (2020).
\biburl{https://www.nature.com/articles/s41378-020-00205-2.pdf}  



\bibitem{SandyNapel}
Sandy Napel, \textit{et al.}, 
\cq{Quantitative Imaging of Cancer in the Postgenomic Era: Radio(geno)mics, deep learning, and habitats}.
\biburl{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6482447/}


% biomarkers ...
\bibitem{JamesOConnor}
James O'Connor, \textit{et al.}, 
\cq{Imaging tumour hypoxia with oxygen-enhanced MRI
and BOLD MRI}.
\bibtitle{British Journal of Radiolology}  
Volume 92 (2019).
\biburl{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6540855/pdf/bjr.20180642.pdf}


\bibitem{ThomasMPearce}
Thomas M. Pearce, \textit{et al.}, 
\cq{Integrated Microelectrode Array and Microfluidics for Temperature Clamp 
of Sensory Neurons in Culture}.
\bibtitle{Lab on a Chip}, 2005, Issue 5, pages 97-101.
\biburl{https://pubs.rsc.org/en/content/articlehtml/2005/lc/b407871c}


\bibitem{QasaimehEtAl}
Mohammad A. Qasaimeh, \textit{et al.}, 
\cq{Microfluidic Probes for Use in Life Sciences and Medicine}.
\bibtitle{Lab on a Chip}, 2013, Issue 1.
\burl{https://pubs.rsc.org/en/content/articlelanding/2013/lc/c2lc40898h}



\bibitem{DanielLRubin}
Daniel L. Rubin, \textit{et al.}, 
\cq{Medical Imaging on the Semantic Web: Annotation and Image Markup}.
\biburl{http://cedarweb.vsp.ucar.edu/wiki/images/d/d9/R_19.pdf}



\bibitem{KentaShinha}
Kenta Shinha, \textit{et al.}, 
\cq{A Microfluidic Probe Integrated Device for
Spatiotemporal 3D Chemical Stimulation in Cells}
\bibtitle{Micromachines}, Volume 11, Issue 7 (2020).
\biburl{https://www.mdpi.com/2072-666X/11/7/691}



\bibitem{AbbasShirinifard}
Abbas Shirinifard, \textit{et al.}, 
\cq{3D Multi-Cell Simulation of Tumor Growth and
Angiogenesis} 
\biburl{https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0007190}


\bibitem{MatveySprindzuk}
Matvey Sprindzuk, \textit{et al.}, 
\cq{Computer-aided Image Processing of Angiogenic
Histological Samples in Ovarian Cancer} 
\biburl{https://core.ac.uk/download/pdf/8701857.pdf}



\bibitem{IoannisValavanis}
Ioannis Valavanis, \textit{et al.}, 
\cq{A Novel Image Analysis Methodology for the Evaluation
of Angiogenesis in Matrigel Assays and Screening
of Angiogenesis-Modulating Compounds}. 
\biburl{https://link.springer.com/content/pdf/10.1007\%2F978-3-319-23868-5_5.pdf}



\bibitem{XuPrince}
Chenyang Xu and Jerry L. Prince, 
\cq{Snakes, Shapes, and Gradient Vector Flow}.
\bibtitle{Transactions on Image Processing}, 
Volume 7, Number 3 (1998), pages 359-369.
\biburl{https://pubmed.ncbi.nlm.nih.gov/18276256/}


\bibitem{YangForan}
Lin Yang and David J. Foran, 
\cq{Deformable Models and their Application 
in Segmentation of Imaged Pathology Specimens}.
In Jasjit S. Suri and Aly A. Farag, \intitle{Deformable Models} 
(Springer 2007), pages 75-94.
\biburl{https://link.springer.com/chapter/10.1007/978-0-387-68343-0_3}

\bibitem{EdyWijaya}
Edy Wijaya, \i{et al.},
\cq{Surface Plasmon Resonance-Based Biosensors: From the development of different
SPR structures to novel surface functionalization strategies}.
\bibtitle{Current Opinion in Solid State and Materials Science}, 
Volume 15, Issue 5 (2011), pages 208-224.
\biburl{http://www.ffh.bg.ac.rs/wp-content/uploads/2017/05/Wijaya.pdf}







\vfill{}




}
\end{thebibliography}
