
\let\oldbibitem\bibitem
%\def\bibitem{\vfill\oldbibitem}

%\pagebreak{}

%\vspace{1em}

%\vspace{27pt}

\begin{thebibliography}{99}
\phantomsection \label{References}
\addcontentsline{toc}{section}{References}
{\fontfamily{lmtt}\fontsize{8}{8}\selectfont

\setlength{\parskip}{0pt}
\setlength{\itemsep}{3.75pt}

\vspace{5pt}


%\begin{minipage}{\columnwidth}


\bibitem{KhalidBelhajjame}{%
Khalid Belhajjame, \textit{et al.},
\cq{Workflow-Centric Research Objects:  First class citizens in scholarly discourse}.	
\biburl{https://users.ox.ac.uk/~oerc0033/preprints/sepublica2012.pdf}}


\bibitem{CrengutaBogdan}{%
Crenguta Bogdan, \textit{et al.},
\cq{Towards a Clinical Trial Ontology Using a Concern-Oriented-Approach}.
\bibtitle{IRPPS Working Papers}, Volume 10 (2006).
\biburl{https://www.movetothecloud.it/irpps/e-pub/index.php/wp/article/view/10/78}}

%% text
\bibitem{BretonnelCohenHunter}{%
Kevin Bretonnel Cohen and Lawrence E. Hunter, 
\cq{Text Mining for Translational Bioinformatics}.
\bibtitle{PLOS Computational Biology}, Volume 9, Issue 4 (2013).
\biburl{https://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1003044}}


\bibitem{CanhamOhmann}{%
Steve Canham and Christian Ohmann,
\cq{A Metadata Schema for Data Objects in Clinical Research}.
\bibtitle{Trials}, Volume 17 (2016).
\biburl{https://trialsjournal.biomedcentral.com/articles/10.1186/s13063-016-1686-5}}


\bibitem{CORD}{%
\cq{COVID-19 Open Research Dataset (CORD-19)}. 2020. Version 2020-03-13. Retrieved from https://pages.semanticscholar.org/coronavirus-research. Accessed 2020-03-20. doi:10.5281/zenodo.3715506
\biburl{https://pages.semanticscholar.org/coronavirus-research}}


\bibitem{SoniaDifrancesco}{%
Sonia Difrancesco, \textit{et al.},
\cq{Sociodemographic, Health and Lifestyle, Sampling, and Mental Health Determinants of 24-Hour Motor Activity Patterns: Observational Study}.
\bibtitle{Journal of Medical Internet Research}, Volume 23, Number 2 (2021).
\biburl{https://www.jmir.org/2021/2/e20700}}


\bibitem{Eyer}{%
	Lud\"ek Eyer, \textit{et al.},
	\cq{Nucleoside analogs as a rich source of antiviral agents active against arthropod-borne flaviviruses}.
	\biburl{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5890575}}


\bibitem{FifiMocco}{%
Johanna T Fifi and J Mocco,
\cq{COVID-19 related stroke in young individuals}.
\bibtitle{The Lancet}, Volume 19 (2020).
\biburl{https://www.thelancet.com/journals/laneur/article/PIIS1474-4422(20)30272-6/fulltext}}

%% text
\bibitem{HolgerFrohlich}
Holger Fr\"ohlich, \textit{et al.}, 
\cq{From hype to reality: data science enabling personalized medicine}.
\bibtitle{BMC Medicine}, Volume 16 (2018).
\biburl{https://bmcmedicine.biomedcentral.com/articles/10.1186/s12916-018-1122-7}


%% text; workflows
\bibitem{ObiLGriffith}{%
Obi L. Griffith, \textit{et al.},
\cq{Text-mining clinically relevant cancer biomarkers for 
curation into the CIViC database}. 
\bibtitle{Genome Medicine}, Volume 11 (2019).
\biburl{https://genomemedicine.biomedcentral.com/articles/10.1186/s13073-019-0686-y}}


\bibitem{AS}{%
Andreas J\"onsson,
\cq{AngelCode Scripting Library}, 
\biburl{http://www.angelcode.com/angelscript/}}


\bibitem{MarittKirst}{%
Maritt Kirst, \textit{et al.},
\cq{Sociodemographic Data Collection for Health Equity Measurement: 
A mixed methods study examining public opinions}. 
\bibtitle{International Journal for Equity in Health}, Volume 12 (2013).
\biburl{https://equityhealthj.biomedcentral.com/articles/10.1186/1475-9276-12-75}}


%%%%
\bibitem{LiMinLiu}{%
Li-Min Liu, \textit{et al.},
\cq{A New Software Development Methodology for Clinical Trial Systems}. 
\bibtitle{Advances in Software Engineering}, Volume 2013.
\biburl{https://www.hindawi.com/journals/ase/2013/796505}}


%\bibitem{LucyLuWang}{%
%Lucy Lu Wang, \textit{et al.},
%\cq{CORD-19: The COVID-19 Open Research Dataset}. 
%\bibtitle{ArXiv}, 2020.
%\biburl{https://arxiv.org/pdf/2004.10706.pdf}}

\bibitem{AaronMOrkin}{%
Aaron M. Orkin, \textit{et al.},
\cq{Reporting of Sociodemographic Variables in Randomized Clinical Trials}. 
\bibtitle{JAMA Network Open}, Voume 4, Number 6 (2021).
\biburl{https://jamanetwork.com/journals/jamanetworkopen/fullarticle/2780555}}


\bibitem{JohnSMcIlwain}{%
John S. McIlwain, 
\cq{Clinical Trial Management Systems (CTMS) System Selection Considerations}. 
\biburl{https://velos.com/wp-content/uploads/Clinical-Trial-Management-Systems-System-Selection-Considerations-Whitepaper-1.pdf}}


\bibitem{ShelbyMeyer}{%
Shelby Meyer, \textit{et al.},
\cq{Sociodemographic Diversity in Cancer clinical Trials: 
New findings on the effect of race and ethnicity}. 
\bibtitle{Contemporary Clinical Trials Communications}, Voume 21 (2021).
\biburl{https://www.sciencedirect.com/science/article/pii/S245186542100020X}}


\bibitem{RossWPaterson}{%
Ross W Paterson, \textit{et al.}, 
\cq{The Emerging Spectrum of COVID-19 Neurology: 
Clinical, radiological and laboratory findings}, 
\bibtitle{Brain}, Volume 143, Number 10 (2020), pages 3104-3120. 
\biburl{https://academic.oup.com/brain/advance-article/doi/10.1093/brain/awaa240/5868408}}


\bibitem{ESIP}{%
Mark A. Parsons and Ruth Duerr,
\cq{Data Identifiers, Versioning, and Micro-citation}.
\biburl{https://www.thelancet.com/action/showPdf?pii=S1473-3099\%2820\%2930086-4}}


\bibitem{PhilipROPayne}{%
Philip R. O. Payne,
\cq{Translational Informatics: Enabling high-throughput research paradigms}.
\bibtitle{Physiology Genomics}, Volume 39 (2009), pages 131-140.
\biburl{https://journals.physiology.org/doi/pdf/10.1152/physiolgenomics.00050.2009}}


\bibitem{SamirAbuRumeileh}{%
Samir Abu‐Rumeileh, \textit{et al.}, 
\cq{Guillain-Barr\'{e} Syndrome Spectrum Associated with 
COVID-19: An up-to-date systematic review of 73 cases}, 
\bibtitle{Journal of Neurology}, Volume 268, Number 4 (2020), pages 1133-1170. 
\biburl{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7445716}}


\bibitem{EnarReilent}{%
	Enar Reilent,
	\cq{Whiteboard Architecture for the Multi-agent Sensor Systems}.
	\biburl{https://www.thelancet.com/action/showPdf?pii=S1473-3099\%2820\%2930086-4}}


\bibitem{SaytaSSahoo}{%
Sayta S Sahoo, \textit{et al.}, 
\cq{Trial prospector: matching patients with cancer research studies using an automated and scalable approach}. 
\bibtitle{Cancer Informatics}, Volume 13 (2014), pages 157-166. 
\biburl{https://pubmed.ncbi.nlm.nih.gov/25506198}}


\bibitem{Shi}{%
Heshui Shi, \textit{et al.},
\cq{Radiological findings from 81 patients with COVID-19 
pneumonia in Wuhan, China: a descriptive study}.
\biburl{https://www.thelancet.com/action/showPdf?pii=S1473-3099\%2820\%2930086-4}}


%% text
\bibitem{MichaelSimmons}
Michael Simmons, \textit{et al.}, 
\cq{Text Mining for Precision Medicine: Bringing structure to EHRs
and biomedical literature to understand genes and health}.
\bibtitle{Advances in Experimental Medicine and Biology}, 
2016, pages 139-166.
\biburl{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5931382}


\bibitem{AyushSinghal}
Ayush Singhal, \textit{et al.}, 
\cq{Text Mining for Precision Medicine: Automating disease-mutation relationship extraction from biomedical literature}.
\bibtitle{Journal of the American Medical Informatics Association}, Volume 23, Issue 4 (2016), pages 766-772.
\biburl{https://academic.oup.com/jamia/article/23/4/766/2201020}


%%%%
\bibitem{MichaelSouillard}
Michael Souillard, \textit{et al.}, 
\cq{A Flexible Framework for Managing Temporal Clinical Trial Data}.
\biburl{http://citeseerx.ist.psu.edu/viewdoc/summary?doi=10.1.1.75.9238}


\bibitem{GentleSunderShrestha}
Gentle Sunder Shrestha, \textit{et al.}, 
\cq{Precision Medicine for COVID-19: A call for better clinical trials}.
\bibtitle{Critical Care}, Volume 24 (2020).
\biburl{https://ccforum.biomedcentral.com/articles/10.1186/s13054-020-03002-5}


\bibitem{TrifanOliveira}{%
Alina Trifan and Jos\'e Lu\'{\OldI}s Oliveira,  
\cq{FAIRness in Biomedical Data Discovery}, 
\bibtitle{12th International Conference on Health Informatics}, 
Proceedings (2019), pages 159-166. 
\biburl{https://www.scitepress.org/Papers/2019/75764/75764.pdf}}


\bibitem{JohanVanSoest}
Johan Van Soest, \i{et al.}, 
\cq{Towards a semantic PACS: Using Semantic Web Technology to Represent Imaging Data}.
\bibtitle{Studies in Health Technology and Informatics}, Volume 205 
(2014), pages 166-179.
\biburl{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5119276}


%%%%
\bibitem{KrisVerlaenen}
Kris Verlaenen, 
\cq{Middleware for Advanced Service Configuration: a Policy-Based
Approach}.
Dissertation, Leuven, 2008.
\biburl{https://www.cs.kuleuven.be/publicaties/doctoraten/cw/CW2008_07.pdf}


\bibitem{LucyLuWang}
Lucy Lu Wang, \i{et al.}, 
\cq{CORD-19: The Covid-19 Open Research Dataset}.
\bibtitle{ArXiv}, 2020. 
\biburl{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7251955}


\bibitem{HetongZhou}
Hetong Zhou, \i{et al.}, 
\cq{The Landscape of Cognitive Function in Recovered COVID-19 Patients}.
\bibtitle{Journal of Psychiatric Research}, Volume 128 (2020), pages 98-102. 
\biburl{https://www.sciencedirect.com/science/article/abs/pii/S0022395620308542}


\bibitem{ZigmanSuchsland}
Monica L. Zigman Suchsland, \i{et al.}, 
\cq{Patient-Centered Outcomes Related to 
Imaging Testing in US Primary Care}.
\bibtitle{Journal of the American College of Radiology}, 
Volume 16, Number 2 (2019), pages 156-163. 
\biburl{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7050575}



\vfill{}

%\end{minipage}


}
\end{thebibliography}
