
\hoctitle{Chapter 3: Patient-Centered Research 
Methodology for Bioimaging and Covid-19}


\section{Introduction}

\p{This chapter will touch on research methodology and 
clinical trial design in light of Patient-Centered paradigms 
and Precision Medicine.  We will focus in particular 
on bioimaging/radiology, on trial architecture 
(particularly \visavis{} Covid-19) and on text and data mining.}

\p{After examining how Precision Medicine 
effects requirements for bioimaging software, 
we will consider patient-centered priorities 
in the context of clinical trials.  The goal 
of incorporating more granular patient-specific 
data within clinical observations in general 
translates over to clinical trials in particular, 
with trial-specific data models needing to 
incorporate patient-centered details 
at several stages, including recruitment
of patients for trials, information management 
while trials are being conducted, and 
subsequent follow-up studies and/or analyses.}

\p{This chapter will conclude by examining 
text and data mining techniques oriented toward 
biomedical publications and data sets, on the 
premise that text and data mining represent a 
computationally sophisticated methodology in 
their own right.  We will focus on the 
case-study of \Cnineteen{}, a large corpus 
of open-access Covid-related articles.}


\section{Precision Medicine and Bioimaging}

\p{Patient-centered research in the radiological 
context focuses on improving the precision of 
diagnostic-imaging techniques and corresponding 
clinical interventions.  Indeed, the goal of contemporary 
radiology is not only to confirm a diagnosis, 
but also to extract cues from 
medical images that suggest which course of 
treatment has the highest probability of 
favorable outcomes.  A related 
goal is curating collections of diagnostic 
images so as to improve our ability to 
identify such diagnostic and prognostic cues, potentially 
using Machine Learning and/or Artificial 
Intelligence applied to large-scale 
image repositories.}

\p{The goal of building \q{searchable} image repositories 
has inspired projects such as the Semantic Dicom Ontology 
(\SeDI{})\footnote{See \bhref{https://bioportal.bioontology.org/ontologies/SEDI}.} and the \ViSion{} \q{structured 
reporting} system.\footnote{See \bhref{https://epos.myesr.org/esr/viewing/
index.php?module=viewing_poster&task=&pi=155548}.}  
As explained in the context of \SeDI{}: 
\q{if a user has a CT scan, and wants to retrieve the [corresponding] radiation treatment plan ... he has to search for the 
RTSTRUCT object based on the specific CT scan, and from there 
search for the RTPLAN object based on the RTSTRUCT object.  This is an inefficient operation because all RTSTRUCT [and] RTPLAN files for the patient need to be processed to find the correct treatment 
plan} \cite[page 1]{JohanVanSoest}.  Even relatively simple queries such as 
\q{display all patients with a
bronchial carcinoma bigger than 50 cm$^3$} cannot 
be processed by \PACS{} systems: \q{although there are various powerful clinical applications to process image data and image data series to create significant clinical analyses, none of these analytic results can be merged with the clinical data of a single patient.}\footnote{See 
\bhref{https://semantic-dicom.com/starting-page/}.}  These 
limitations partly reflect the logistics of how 
information is transferred between clinical institutions 
and radiology labs.  In response, and in an effort 
to advance the science 
of diagnostic image-analysis, organizations such as 
the Radiological Society of North America 
(\RSNA{}) have curated open-access data sets encompassing 
medical images as well as image-annotations (encoding feature 
vectors) that can serve as reference sets and test 
corpora for investigating analytic methods.  Such 
repositories are designed to integrate data from 
multiple hospitals and multiple laboratories --- bypassing 
the conventional data flows wherein radiological 
information is shared between clinicians 
and radiologists, but is not also merged into broad-spectrum 
corpora.}

\p{This renewed focus on patient outcomes 
has important consequences for the scope and 
requirements of diagnostic-imaging software.  
In particular, the domain of radiological applications 
is no longer limited to \PACS{} workstations 
where pathologists perform their diagnostic analysis, 
with the results transferred back to the referring institution 
(and subsequently available only through that institution's 
medical records, if at all).  In the older,  
conventional workflow, radiographic images are requested by 
some medical institution for diagnostic purposes.  
Relevant information is therefore shared between 
two end-points: the institution which prescribes 
a diagnostic evaluation and the radiologist or 
laboratory which analyzes the resulting images.  
Building radiographic data repositories complicates 
this workflow because a third entity becomes 
involved --- the organization responsible 
for aggregating images and analyses is generally 
distinct from both the prescribing institution and 
the radiologists themselves.  As a result, both radiologists and prescribing 
institutions, upon participation in the formation 
of the target repository, must identify which image 
series and which patient data are proper candidates 
for the relevant repository.}

\p{For a concrete example, \RSNA{} has announced the 
forthcoming publication of an open-access image 
repository devoted to 
Covid-19.\footnote{See \bhref{https://www.rsna.org/covid-19}.}  
This repository is being curated in collaboration with 
multiple European, Asian, and South American organizations 
so as to collect data from hospitals treating 
Covid-19 patients.  Such a collaboration requires 
protocols both for data submission and for patient privacy 
and security.  As this example demonstrates, 
these kinds of data-sharing initiatives present 
new requirements for radiological software, which must 
not only allow for the presentation, annotation, and 
analysis of medical images, but also for participation 
in data-sharing initiatives adhering to rigorous 
modeling and operational protocols.}

\p{Simultaneously, the science of diagnostic imaging 
is also expanding as new image-analytic techniques 
prove to be effective at detecting signals 
within image data, often complementing the work 
of human radiologists.  The proliferation of 
image-analysis methodologies places a new emphasis 
on \textit{extensibility,} where radiological 
software becomes more powerful and flexible 
because new analytic modules may be plugged in 
to a central \PACS{} system.  A good example of 
this new paradigm is \CaPTk{}, which we 
will discuss below.  The \CaPTk{} project
provides a central application 
which supplies a centralized User Interface and 
takes responsibility for acquiring and loading 
radiographic images.  The \CaPTk{} core application is 
then paired with multiple \q{peer} applications 
which can be launched from \CaPTk{}'s main window, 
each peer focused on implementing specific 
algorithms so as to transform and/or to extract feature vectors 
from images sent between \CaPTk{} and its plugins.}

\p{Both the patient-outcomes focus in building image 
repositories and the integration of novel 
Computer Vision algorithms depend, at their core, 
on rigorous data sharing.  Taking the 
\RSNA{} Covid-19 repository as a case study for 
promoting research into post-diagnostic outcomes, 
this repository is possible because an international 
team of hospitals and institutions have agreed to 
pool radiological data relevant to SARS-CoV-2 infection 
according to a common protocol.  Taking \CaPTk{} as a 
case-study in multi-modal image analysis, this 
system is likewise possible because analytic modules 
can be wrapped into a plugin mechanism which allows 
many different algorithms to be bundled into a common 
software platform.  Of course, these two areas 
of data-sharing overlap: one mission of repositories 
such as the \RSNA{}'s is to permit many different 
analyses to be performed on the common image 
assets.  The results of these analyses then become 
additional information which enlarges the 
repository proportionately.  If \CaPTk{} modules 
are used to analyze the \RSNA{} Covid-19 images, 
for example, there needs to be a mechanism for 
exporting the resulting data outside the \CaPTk{} 
system, so that the analyses may be integrated into 
the repository either directly or as a supplemental 
resource.}
  
\p{This example demonstrates how software such as 
\CaPTk{} may be extended to support the curation 
of image repositories dedicated to Patient Outcomes 
and Comparative Effectiveness Research (\CER{}), insofar 
as analytic data generated by (for example) \CaPTk{} components 
can acquire the capability to share data according 
to repository protocols.  A further level of 
integration between \CaPTk{} and \CER{} initiatives 
(again, staying with \CaPTk{} as a 
representative example of bioimaging applications in general) 
can be achieved if one observes that clinical 
outcomes may be part of the analytic parameters 
used by \CaPTk{} modules.  As presently constituted, 
\CaPTk{} analytic tools are focused on extracting 
quantitative (or quantifiable) features from 
image themselves, without considering additional 
patient-centered context.  There is no technical 
limitation, however, which would prevent the 
\CaPTk{} system from sharing more detailed clinical 
information with its modules, allowing these 
analytic components to cross-reference image features 
with clinical or patient information.  This 
then raises general questions about sharing 
clinical data \i{as well as} information 
derived from bioimage analysis, which we 
will review over the course of this chapter.}

\subsection{The Basic Synthesis Between Bioimaging and Precision Medicine}
\p{\noindent{}Patient-centered research in 
the radiological context has several dimensions, 
including analysis of the rationales for diagnostic 
imaging in the first place: how well does image-based 
diagnostics actually correlate with improved patient 
outcomes?  How can we quantify the experience of 
image-based testing itself (e.g., to identify 
factors such as cost, discomfort, and 
radiation danger which can rank some tests 
as less desirable than others, as one parameter 
to consider when deciding whether to prescribe 
imaging, and which modality)?  These were 
among the questions addressed by 
the Patient-Centered Outcomes Research Institute's 
(\PCORI{}'s) \q{Patient-Centered Research for Standards 
of Outcomes in Diagnostic Tests} (\PROD{}) study, 
which also established a useful protocol for how 
medical institutions could provide reports 
on the experience and effectiveness of imaging 
from a patient's as well as clinician's perspective.}

\p{Assuming diagnostic imaging of a given 
modality \textit{is} 
appropriate, an additional priority should then 
be to structure the diagnostic workflow --- the 
image procurement, analysis, and data/metadata sharing 
protocols --- to maximize the probability 
that subsequent clinical interventions are 
chosen which promote favorable outcomes on 
multiple patient-centered criteria, including 
quality of life and patient engagement.  In 
the best case scenario, the goal of radiology is 
not only to confirm a diagnosis, 
but also to extract cues from 
medical images that suggest which course of 
treatment has the highest probability of 
favorable treatment outcomes.}

\p{While most radiologists and pathologists 
would probably agree with this assessment 
--- that Precision Medicine can be a \q{game-changer} 
in bioimaging fields such as radiology --- 
there are technological and operational 
challenges to making patient-centered 
perspectives a central feature of diagnostic-imaging 
methodology.  Effectively cross-referencing 
imaging and outcomes data requires integrating 
heterogeneous information obtained at different 
times and places.  Some clinical data is associated 
with each patient at the time that a radiological 
(or other imaging) study is prescribed.  The 
images themselves, and subsequent diagnostic  
reports, provide layers of data that exist prior to the initiation 
of a course of treatment (at least insofar as a 
clinical intervention is chosen in response 
to radiological findings).  Moreover, a rigorous 
data-integration protocol would need to incorporate 
information emerging \textit{after} the treatment 
starts: descriptions and assessments of clinical outcomes, 
and, potentially, new data garnered by applying 
different image-analysis techniques.  
Ideally, image analysis can be powerful enough 
not only to identify a pathology, but to 
classify diagnoses into clusters based on 
recommended course of treatment.  In order 
for analytic techniques to achieve this 
level of detail, however, it is necessary 
to arrive at a feedback loop where known clinical 
outcomes are associated with prior images, 
so that developers have those outcomes available 
as a further dimension of clinical data 
that may be statistically cross-referenced 
with image analysis.}


\p{The \PROD{} 
study demonstrates that experiential 
factors should be evaluated --- both in 
terms of testing itself (and its risks/costs) 
and in terms of post-diagnostic quality of 
life --- as part of the data modeling 
treatment outcomes, and the comparative 
effectiveness of a selected course of treatments 
compared to alternative diagnostic 
methods and/or clinical interventions.  
From the perspective of standard 
data models, initiatives to cross-reference 
imaging and outcomes data include several 
Semantic Web ontologies, such as the Semantic Dicom Ontology 
(\SeDI{}) and the \ViSion{} \q{structured 
reporting} system (both referenced earlier). 
The purpose of these ontologies is to 
standardize the terms through which 
radiographic procedures, analyses, and 
recommendations are described --- more 
precisely or predictably than older 
technologies such as \DICOM{} headers, 
\DICOMRT{}, and the \RadLex{} lexicon.  
By properly aligning image metadata 
spanning multiple patients, it is possible 
to create \q{searchable} image archives such 
that images can be selected or classified 
within a larger image collection, 
yielding image series or patient cohorts 
that can be studied through the lens of 
predictive modeling or patient-centered 
outcomes.  Projects such as \SeDI{} 
implement \q{semantic} \PACS{} workstations 
where the space of known images is defined 
by a particular \PACS{} system, but analogous 
techniques could be used to construct 
larger-scale image corpora as well, for 
research purposes, data mining, or as 
test-beds for code and algorithms.}  

\p{However, making interop work across distinct software 
ecosystems add development complexity: the 
requirements for implementing novel analytic 
methods are not only to compose executable 
code making the methods computationally realizable, 
but to package that code into a functional unit that 
can interoperate with other clinical and imaging 
software.  This problem, in turn, engenders 
various software-engineering techniques and frameworks.  
A good example is the Cancer Imaging 
Phenomics Toolkit (\CaPTk{}), developed 
at the Center for Biomedical Image Computing %
and Analytics (\CBICA{}) at 
the University of Pennsylvania Perelman School of 
Medicine, which is an extensible platform for implementing 
analytic modules as peers to a central \PACS{} system.  
In particular, \CaPTk{} provides an implementation 
(apparently the only \Cpp{}-based implementation) 
of \CWL{}, using this workflow model in 
conjunction with the \Qt{} Reflective Programming 
system to implement workflows connecting the 
central \CaPTk{} application with its analytic 
extensions.\footnote{No native \sC{} or \sCpp{} 
libraries are described on the \sCWL{} website 
among the tools and parsers available for \sCWL{}, 
but \sCaPTk{} is mentioned on a corresponding discussion 
thread concerning \sCpp{} libraries.  It seems 
therefore that the \sCaPTk{} \q{utilities} repository 
provides the de-facto standard \sCpp{} implementation of 
\sCWL{}, at least according to the \sCWL{} group 
themselves.}   In effect, \CaPTk{} achieves a 
workflow and messaging protocol for what they 
term \q{native,} \q{standalone} applications, 
yielding an extensible architecture through 
which new image-analysis techniques can be 
integrated into an underlying \PACS{} system.} 
 
\p{Certain comparisons can be made 
between \CaPTk{}, whose architectural 
innovations are centered on workflow 
management and multi-application networking, 
and \SeDI{}, whose novel features 
focus on data alignment and integration.  
Both of these projects expand the analytic 
capabilities of diagnostic-imaging 
systems by promoting common data and 
code representations, enlarging the 
space of metadata available for query-evaluation 
and/or the range of quantitative techniques 
available for image analysis.  Both rely 
on a canonical description format 
(\CWL{}, in the case of \CaPTk{}, and 
a novel \RDF{} ontology, in the case of \SeDI{}) 
which is not widely implemented by other 
\PACS{} systems.  Their concerns also overlap 
insofar as different analytic methods generate 
different kinds of image data, which need to be 
integrated into the total space of data 
available for a \PACS{} system and/or an image 
repository.  While the data-integration 
approaches chosen by these two projects are 
specific to the respective software applications which 
is their main result, both \SeDI{} and \CaPTk{} 
point to evident limitations in the scope 
of current diagnostic imaging software: 
failure to properly integrate image metadata 
(including clinical and outcomes data) into a 
multi-patient space optimized for query 
evaluation and data mining; and failure to 
integrate many diverse image-analysis 
methodologies into a common execution framework.}

\p{One take-away from this overview of 
\SeDI{} and \CaPTk{} is that new diagnostic 
imaging software can incorporate some version 
of the data models and protocols implemented 
by these two projects.  On a broader level, however, 
the concrete examples of \SeDI{} and \CaPTk{} 
point to limitations in current 
frameworks such as \DICOM{}.  The integrative logic of 
\SeDI{} and \CaPTk{} is based on specific 
data structures --- \DICOM{} headers and 
\CWL{}, respectively --- and arose out of 
practical limitations in existing \DICOM{} 
software.  The \SeDI{} and \CaPTk{} solutions 
may be a methodological guide for related 
projects, but neither is a general-purpose 
framework for solving all data and code 
integration problems (not to imply that 
such a general-purpose solution exists).  
Integration problems are not exhausted by 
deriving solutions in one specific area: 
for example, merging \DICOM{} metadata 
into \RDF{} graphs may successfully align 
data structures conforming to current 
\DICOM{} specifications, but does not 
guarantee integration of novel extensions or 
supplements to \DICOM{}.  Much as \DICOMRT{} 
extended \DICOM{} to incorporate radiation-therapy 
recommendations, predictive modeling and  
patient-centered Comparative Effectiveness reach 
could easily lead to new data standards as 
researchers seek to integrate imaging data 
with treatment plans and outcomes evaluation.}


\p{Because \CaPTk{} is extensible as part of 
its essential design, it is both technologically 
and philosophically consistent with 
\CaPTk{}'s structure to introduce extensions 
which focus on the analytic convergence 
or cross-referencing between image-analysis 
and outcomes data; and to implement data-sharing 
protocols among \CaPTk{} modules which model 
clinical and outcomes information alongside 
image data.  In this sense, \CaPTk{} is a 
logical starting point for the design 
and situating of hybrid radiological/outcomes 
software in a larger computational 
context, as will be detailed below.}


\subsection{Multi-Application Networks in the Context of 
Scientific Research Data}
\p{Architecturally, the pattern of organization 
just described --- semi-autonomous applications 
linked together (often by virtue of being common 
extensions to an overarching \q{core} software 
platform) is 
analogous to the collection of software components 
that may share access to a data repository or 
a research-data corpus, include a corpus of 
medical/diagnostic images.  The purpose of 
research data archives --- particularly when 
they embrace contemporary open-access standards 
such as \FAIR{} (Findable, Accessible, Interoperable, 
Reusable) \cite{TrifanOliveira}  
and the Research Object 
Protocol\footnote{see \bhref{http://www.researchobject.org/scopes/}} --- is to promote reuse and reproduction of 
published data and findings, such that multiple subsequent research 
projects may be based on data originally published 
to accompany one book or article.  As a result, it is 
expected that numerous projects may overlap in their 
use of a common underlying data set, which potentially 
means a diversity of software components implementing 
a diversity of analytic techniques, each offering a unique 
perspective on the underlying data.  In addition to 
providing diverse analytic methods, 
research-oriented software transforms the ecosystem 
where scientific data and academic books/articles 
are published and explored.  From a reader's point of 
view, open-access data sets present an interactive, 
multi-media experience which supplements reading 
article texts.  Indeed, in recent years, publishing houses 
have embraced the notion (albeit more of a future 
vision than a present reality) that conventional 
publications are only one part of a larger 
package (e.g. a \q{Research Object Bundle}), 
which may contain data, computer code, and/or 
interactive graphics alongside text-based formats 
such as \PDF{}.  At the same time, from 
a scientist's point of view, open-access research 
data offers a starting point for their own 
investigations, or a contretemps with which to 
reinforce or contrast their own findings.}
%\input{pics/about}

\p{All of this means that scientists preparing 
academic papers are not only finalizing text 
descriptions but also, often, curating data, 
graphics, or code that demonstrates their work 
in an interactive, multi-media fashion 
(such assets are often presented to readers 
via \q{supplemental material,} \q{additional 
files,} or \q{data availability} sections 
on web pages showing article texts or abstracts).  
Scientists can support multi-media exploration 
of their research by presenting data in 
file formats used by data-visualization software; 
they can also assert more fine-grained control 
over data visualization by implementing 
custom software.  One benefit of 
custom data-set software is the possibility 
of using \textit{microcitations} to 
connect research data (and the \GUI{} 
components where this data is visualized) 
to publication texts.\footnote{Microcitations 
are independently citeable smaller units of 
a data set, such as an individual record, 
a table column, or one table in a multi-table 
collection; we will discuss microcitations 
further in the next section.}  
Microcitations enable application-level interoperability 
between document viewers and data-set 
applications.  For instance, individual table columns 
can be associated with specific scientific concepts 
or statistical parameters that are described 
in the article text.  
This interop between data sets and 
\PDF{} viewers is an example of 
multi-application networking --- both the 
data-set application and the \PDF{} software 
need to be implemented or extended with 
the capacity to execute microcitation-based 
workflows.  Moreover, data-set applications can provide 
(through their type system and implementation 
protocol) one form of structural model and 
formal elaboration of research theories,  
methodology, or experimental design.  
Defining an annotation schema for data sets can potentially 
be an organic outgrowth of software-development methodology 
--- viz., the engineering steps, 
such as implementing unit tests, which are essential 
to deploying a commercial-grade application.}

\p{Implementing a robust research-data software 
framework involves integrating multiple scientific 
applications, but also (ideally) extending these 
applications with features specifically 
of interest to those conducting or reviewing 
research using published data sets and/or 
described in academic literature: for 
instance, capabilities to download data sets 
from open-access scientific portals; to 
parse microcitation formats; and to interoperate 
with document viewers.  This review of data-publishing technology is 
relevant to radiology and to Patient-Centered 
Outcomes because it typifies the emerging ecosystem 
where scientific research and open-access data 
is being disseminated.  Open-access data 
publishing --- especially within the emerging 
frameworks being advocated and developed 
by publishers and research institutions 
themselves --- is conducive to a software 
engineering paradigm that favors the implementation 
of autonomous software agents which, 
their autonomy notwithstanding, can interoperate to the degree 
that they are collectively oriented to a shared data source.  
Such a multi-application network requires integration 
not only at the level of data structures, but also 
at the level of Human-Computer Interaction and 
inter-application messaging --- in the optimal 
case users can switch between applications 
based on each components' respective capabilities.  
In sum, the \CaPTk{} architecture --- consisting 
of numerous autonomous, stand-alone, native 
applications federated into a decentralized 
but unified platform --- is similar logistically 
to the kinds of application networks 
appropriate for the technology supporting 
archives of research data (including 
diagnostic-imaging repositories).}

\p{Given this architectural correlation, we 
would argue that the \CaPTk{} architecture can be used 
as a prototype for implementing multi-application 
networks such as those applicable to 
research data repositories.  Initiatives such as Research Objects and 
\FAIR{} advocate for a technological infrastructure 
characterized by a diverse software ecosystem 
paired with open-access research data sets.  
Scientific data repositories, linked to 
academic publishing platforms, have been engineered 
to help scientists locate and re-use data sets 
which are relevant to their research projects.  
Although formats such as Research Objects have been 
standardized over the last decade, there has not 
been a comparable level of attention given to 
formalizing how multiple software applications 
should interoperate when manipulating 
overlapping data.  The Common Workflow Language 
(\CWL{}), which has been explicitly included in the 
Research Object 
model,
documents one layer of inter-application messaging, 
including the encoding of parameters via command-line 
arguments; \CaPTk{} provides a \Cpp{} implementation of 
\CWL{} and uses it to pass initial data between 
modules.  Serializing larger-scale data structures 
is of course a generic task of canonical encoding 
formats such as \JSON{}, \XML{}, \RDF{}, and 
Protocol Buffers --- not to mention text or binary 
resources serialized directly from runtime objects 
via, for instance, \textbf{QTextStream} and \textbf{QDataStream.}  
This means that some level of inter-application 
communications is enabled via \CWL{}, and 
that essentially any computationally tractable 
data structure can be encoded via formats such 
as \XML{}.  These solutions, however, are 
sub-optimal: \XML{} (as well as \JSON{} and analogous 
formats) is limited because it takes additional 
development effort to compose the code that marshals 
data between runtime and serial formats.  
Similarly, although \CWL{} can model information 
passed between applications, it provides 
only an indirect guide for programmers implementing 
each application's \q{operational semantics} --- 
viz., the procedures which must be executed 
before and after the event wherein data is 
actually passed between endpoints.}

\p{In the context of \CaPTk{}, for example, 
integrating peer modules with the \CaPTk{} core 
application involves more than simply 
ensuring that these endpoints communicate 
via a standardized data-serialization format: 
the plugins must be \textit{registered} 
with the core application, which affects the 
core in several areas, including the build/compile 
process and construction of the main \GUI{} 
window.  Modeling the interconnections between 
semi-autonomous modules, as \CaPTk{} demonstrates, 
therefore requires more detail than simply 
modeling their shared data encodings; it 
is furthermore necessary to represent all 
procedural and User Interface requirements 
in each component that may be affected by 
the others.  Despite the standardization 
efforts that have been invested in 
Research Objects and the Common Workflow Language, 
we contend that this fully detailed 
protocol for multi-application interop has not 
yet been rigorously formalized.}


\p{Rigorous models of application networks among semi-autonomous 
components acquire an extra level of complexity precisely 
because of this intermediate status: protocol definitions 
have to specify both the functional interdependence 
and the operational autonomy of different parts of 
the application network.  Although 
one application does not need detailed 
knowledge of the other's internal procedure 
signatures (which would break encapsulation), 
a rigorous messaging protocol can be developed 
by specifying requirements on the relevant 
procedures implemented by each application.  
Developers can then explicitly state that 
a given set of procedures implements a given 
protocol (the multi-application documentation 
thereby has more detailed information about 
application-specific procedures than each 
application has \visavis{} its peers).  The 
functional interdependence between applications can 
accordingly be modeled by defining protocols which 
must be satisfied by procedure-sets internal 
to each end-point --- the relevant information 
from an integrative standpoint is not the 
actual procedures involved, but confirmation 
that the relevant procedure sets adhere 
to the relevant multi-procedural protocol.\footnote{Reviewing the source code and documentation 
for \CaPTk{} confirms that multi-application 
messaging along these lines is implicitly adopted 
by \CaPTk{}; see for example 
\bhref{https://www.med.upenn.edu/cbica/assets/user-content/images/captk/2018\_ISBI\_CaPTk .0404.Part2.pdf}, particularly 
the material starting on the 30th slide of that presentation.}} 

\section{Precision Medicine in Trial Design}
\p{\noindent{}Data-sharing 
initiatives need to pay particular attention to 
the logistics of hosting/accessing data in 
contexts where granular patient-specific information is important, 
such as immunoprofiling.  Questions which should be addressed include 
(1) where data is to be hosted; (2) how participating 
institutions should submit data to a central repository; 
(3) how participating institutions and/or outside investigators 
should access previously-deposited data; (4) how to 
ensure anonymization of patient-specific records; (5) how to ensure 
that different labs used by different hospitals are utilizing 
compatible protocols, so that results from multiple labs/hospitals 
can be seamlessly merged in a shared data commons; 
(6) how to ensure proper alignment between software employed 
at different institutions; and (7) how to incorporate data 
curated within the context of a multi-institutional data-sharing initiative 
into scientific papers documenting 
research findings.  Each of these areas of concern 
are technically demanding because of the complex and 
heterogeneous nature of immunological profiles.}

\p{As a case-study in clinical-trial software 
engineering, consider again the proposals 
in Shrestha \textit{et al.} \cite{GentleSunderShrestha} 
which we reviewed last chapter.  As these authors 
recommend, Covid-19 trials should be designed to focus on 
specific patient groups which are more likely to benefit from the interventions 
that form the basis of the relevant clinical trials.  Moreover, 
toward the goal of applying precision medicine to Covid-19 clinical practice, 
it should be possible to construct a quantifying domain of patient-profile signals
(antecedent to trial commencement) 
to quantify the statistical probability that a given treatment will have a 
favorable patient outcome in relation to all the prior data in a patient's 
profile.  Since researchers assume that 
certain factors in a patient's profile 
will be statistically correlated with favorable outcomes in conjunction 
with specific treatment plans, part of the trial's purpose 
is to determine which parts of the patient profile 
are, in fact, statistically relevant.}

\p{In practical terms, then, setting up Covid-19 trials would involve 
defining patient-selection criteria and implementing systems to 
screen for patients who may be good candidates for different trials.  
This would require two steps: (1) constructing a format where trial criteria 
can be rigorously notated; and (2) implementing software at each 
participating hospital to search for good candidates to register in each trial.  
The trial-specific software would need to query each hospital's 
clinical and/or diagnostic records.  Because patient-specific factors 
for determining trial eligibility would cover a broad spectrum of 
data types --- from sociodemographics and 
medical history to domain-specific lab/image results --- the screening 
software would, therefore, need to integrate such heterogeneous data sources.}

\p{Given the sheer scale of the SARS-CoV-2 pandemic, 
there are likely to be many candidates for almost any Covid-19 
trial.  However, because of the extent of the pandemic, 
governments and hospitals have had to establish treatment 
protocols rather haphazardly.  As a result, there has been  
a fair amount of trial and error as opposed to a \textit{systematic} 
framework for evaluating diagnostic regimens 
and treatment protocols.  For example, rather than 
have one or two canonical SARS-CoV-2 antigen tests, 
used to measure virus antibody levels in patients, the US Centers for Disease Control recommends 
or has authorized a large list of 
assays performed by many different companies, using 
many different biochemical methods.\footnote{\textit{See}, for example, 
\bhref{https://www.fda.gov/medical-devices/coronavirus-disease-2019-covid-19-emergency-use-authorizations-medical-devices/vitro-diagnostics-euas#individual-antigen}.}}

\p{Because the format of data resulting from immunoassays depends 
on the specific biochemical mechanism which (within each 
assay) yields quantitative data, a broad spectrum of 
antigen tests requires a diverse array of data formats 
which need to be integrated.  As such, whenever 
Covid-19 immunoassays are considered 
as critical factors in immunological profiles for mapping 
patients to appropriate Covid-19 clinical trials, querying for good 
trial candidates means querying across a 
wide spectrum of structurally different data types that 
correspond to this broad array of antigen tests --- specifically 
to the mechanisms through which laboratory instruments generate 
quantifiable data and to the computational procedures which process 
such data.  Here is a good example of why specialized custom software 
is necessary: given the heterogeneity of Covid-19 data, 
synthesizing all this information calls for 
integrative procedures implemented directly 
in programming languages such as \Cpp{} 
(rather than query languages such as \SQL{}).}

\subsection{Software Alignment for Covid Phylogeny Studies}% across Multiple Populations}
\p{Similar to immunological studies, discussed above,
analysis of SARS-CoV-2 mutations is yet another area  
where software alignment can prove to be important.   
Studies suggest that variations in the 
viral strain causing Covid-19 symptoms may be partly 
responsible for divergent immunological responses to 
the virus across the patient population.\footnote{\textit{See} for instance Osman Shabir, M.Sc., 
``The Phylogenetic Tree of the SARS-CoV-2 Virus,'' 
News Medical,   
\bhref{https://www.news-medical.net/health/The-Phylogenetic-Tree-of-the-SARS-CoV-2-Virus.aspx}; the author identifies one region in particular 
where ``[c]hanges within this region may account for the differences in 
immune responses to SARS-CoV-2.''}  If one 
patient 
responds 
either less favorably or more favorably than the average patient-response 
to a 
given treatment, clinicians need to assess whether this 
difference can be explained solely by the patient's 
prior immunological profile or whether the patient has 
been exposed to a genetically divergent viral strain.%  
%The idea of an \q{average} or \q{typical} response to 
%treatment is of course only relative to a single 
%strain of the disease.
}

\p{Modeling SARS-CoV-2 evolution across the globe is a 
massive project.  There have been over 41 million Covid-19 cases 
worldwide, in virtually every nation on earth, so a 
complete phylogenetic picture of SARS-CoV-2 in 
humans would need to pool data from many different 
healthcare systems.  
%Dearlove, \textit{et al.}, 
Yet, even technically 
detailed analysis of the phylogeny of SARS-CoV-2, such as that 
conducted by Dearlove \textit{et al.} (as 
reported at the end of 2020) 
only considered 27,977 patients (about 0.1\% of 
global cases), with almost half from the 
United Kingdom \cite{BethanyDearlove}.  
Hence, achieving something resembling a holistic picture of 
SARS-CoV-2 mutations and how they might affect clinical 
treatments, would require many parallel studies analogous 
to that of Dearlove \textit{et al.}.}

\p{This then raises questions of study alignment: because calculating 
viral phylogeny requires making technical decisions about how genetic 
sequences should be acquired and analyzed, decisions which 
may vary among research teams, spanning many healthcare institutions.  
For example, Dearlove \textit{et al.} describe several computational 
steps which they had performed 
both to normalize each SARS-CoV-2 genome sequence in their 
data set for cross-comparison and to run predictive 
simulations (used to estimate whether divergence between 
sequence-pairs are the result of localized, random mutations or, 
conversely, an indication that SARS-CoV-2 is evolving into 
further distinct strains).    
Clustering SARS-CoV-2 genomes into variants --- that 
is, identifying which mutations are random and which 
appear to be propagating to subsequent viral generations 
--- involves making computational and biological 
assumptions, such as how to statistically 
marshal genomic data so as to quantify the prevalence of a 
mutation, and how to estimate whether a particular mutation confers 
an adaptive benefit to the viral agent (e.g., an 
ability to elude antibodies targeting structural proteins).}

\p{Given that modeling viral phylogeny requires 
certain computational assumptions and biological 
guesswork, data from multiple studies can only be 
reliably integrated if there is some degree of 
alignment across their methodology.  As such, 
research teams should document their protocols 
in a manner that permits assessment as to whether 
protocol differences might compromise the 
resulting data.  One way to achieve this is to 
model the protocol itself as a datatype in a programming 
language such as \Cpp{}.  For each study, such as 
Dearlove \textit{et al.} cited above, there would then 
be a \Cpp{} object encapsulating all details of 
the researchers' protocols and computational workflows.  
Assuming that research into SARS-CoV-2 phylogeny could be centralized 
into a publication archive, then their associated protocol-objects 
could be aggregated into a protocol database.  The purpose 
of such a database would be to establish a composite picture 
of SARS-CoV-2 evolution by synthesizing data from multiple 
studies and/or multiple countries.  Protocol-alignment would 
be one part of a common framework to quantify the 
epidemiological significance of SARS-CoV-2 mutations.}

\p{%Thus far, only a few SARS-CoV-2 mutations have warranted 
%further analysis, assigned names such as \q{P4715L} and 
%\q{D614G} (Dearlove \textit{et al.}, p. 4).  Several other 
%mutations are responsible for the differences between 
%Type A-C SARS-CoV-2 strains.  
In short, a holistic 
global picture of SARS-CoV-2 must represent 
SARS-CoV-2 mutations which have been deemed 
phylogenetically and/or clinically significant (i.e., having 
potential either to influence the overall evolution of 
Covid-19 and/or to have some bearing on clinical treatments), 
and must \textit{also} represent divergent SARS-CoV-2 strains.  These data-points 
would then be the basis of further details such as: 
when did a given strain and/or mutation first appear?  Is 
the strain/mutation geographically localized?  What is the 
proportion of different strains/mutations in a geographic 
area?  Is there evidence that different strains/mutations 
affect a patient's immunological response to Covid-19 and/or 
the effectiveness of vaccines, antibody regimens, steroids, 
or other clinical interventions?  How can genetic mutations within 
the SARS-CoV-2 virus be correlated with structures in the spike 
proteins encoded by the viral genes?  This last question points 
to the importance of integrating genomic data with \ThreeD{} molecular 
models.  Whereas data structures modeling the viral genome 
are composed of nucleotides --- and, at a higher scale, Open Read 
Frames (\ORF{}s) --- data structures describing the biophysics of 
glycoproteins involve \ThreeD{} geometry and chemical bonds.  Analyzing how 
\makebox{SARS-CoV-2} genes 
affect the production of glycoproteins, therefore, requires 
annotating and cross-referencing nucleotide/\ORF{} data structures 
with molecular models encoded in formats 
such as Protein Data Bank (\PDB{}).}

\p{Assuming that a synthesis of SARS-CoV-2 genomic 
research  is based on a \Cpp{} protocol object model, 
as suggested above, one can similarly develop \Cpp{} data 
types to model SARS-CoV-2 strains and mutations.  The 
trio of protocol, strain, and mutation objects could 
then serve as the basis of a unified Object-Oriented 
framework for representing SARS-CoV-2 evolution across 
the world.  This would allow the results of different studies to 
be compared, so as to build a composite global profile 
of SARS-CoV-2 phylogeny.  
We are not aware of Object-Oriented models 
proposed as representational devices 
for Covid Phylogeny, but this form of 
software design would be consistent with code 
developed in contexts such as oncology, for 
example the computational simulation of 
tumor growth, which we will discuss next chapter.  
Covid-Phylogeny Object Models 
could serve as a nexus for merging temporal and 
geographical data concerning the epidemiology of \makebox{SARS-CoV-2} 
mutations with genomic data demonstrating  
which mutations are significant, as well as clinical 
data tracking correlations between mutations and treatment outcomes.  
Supporting \makebox{large-scale} multi-trial data integration would, therefore, 
also introduce new requirements for clinical trial \makebox{software}.
}

\subsection{Customizing Clinical Trial Management Software}
\p{Once trials embrace heterogeneous data models
(which require special-purpose software for accessing 
some of the trial data),  Clinical Trial Management Systems 
(\CTMS{}) requirements become 
more complex.  In these situations, \CTMS{}s may need 
to model and in some cases replicate complex computational 
workflows, such as those employed by Dearlove \textit{et al.} 
for calculating SARS-CoV-2 genomic sequences from patients' blood samples.  
The \CTMS{} software may also need to interoperate 
with domain-specific applications, as in bioimaging and 
image analyses, signal processing (e.g., for \EKG{} analysis), 
Flow Cytometry, biochemical assays, genomic analysis, 
epidemiological modeling and so forth.  If possible, such 
applications should be configured or extended to work 
with the clinical trial software.  For instance, if a \DICOM{} 
(Digital Imaging and Communications in Medicine) client 
is used to study an image derived from a specific trial 
--- e.g., a radiological scan of a Covid-19 patient's lungs 
--- the \DICOM{} software could be provided with a plugin 
that would show trial information in a separate window, 
which could then be juxtaposed with the main-image 
view.    
In this context, software alignment means that 
all institutions participating in a trial could use 
the \textit{same} plugins, so that the trial's central 
\CTMS{} system could interoperate with special-purpose 
software in a consistent manner.  This would also 
aid in establishing, as part of the trial design, 
protocols for depositing special-purpose data assets  
(such as \FCS{} or \DICOM{} files) alongside 
clinical data and \eCRF{}s.}

\p{A further benefit of \CTMS{} customization is that 
custom software adds flexibility for trial design.  
By definition, trials allow researchers to test 
biomedical hypothesis in a controlled manner.  
Trials are, therefore, defined around the premise that 
observational information resulting from the trial 
is empirically significant, revealing something new 
about what the trial was designed to investigate.  
For instance, a Covid-19 trial might assess how 
well patients with varying prior immunological 
profiles respond to monoclonal antibody (\mAb{}) treatments.  
The relevant observations in this case derive from 
the subsequent course of the disease for each 
patient, as well as potential adverse reactions, but there are, however, 
inherent complicating factors, such as: (1) were patients receiving other 
treatments as well? (2) for patients who recover, how do 
we know that the antibodies expedited that recovery? 
(3) how quickly was the recovery? and (4) did patients continue 
to suffer from Covid-related symptoms even when they 
were no longer infectious?}

\p{In addition to these post-treatment observations,
situational details specific to the trial ---  
such as each patient's \mAb{} dosage level, 
prior Covid-19 risk factors, or viral-load change 
over time --- need to be incorporated into the trial's unique 
data models.  Moreover, a comprehensive investigation could well incorporate both 
information about the patient's unique immunological profiles and the 
nature of the SARS-CoV-2 variant/strain found in the patient.}

\subsubsection{Toward Fine-Grained Sociodemographic Models}
\p{Patient-centric data could likewise include sociodemographic information 
about the patient, supplemented by epidemiological 
metrics, such as contact tracing: 
was the patient living or working in an environment 
where they were likely to have been exposed to the virus?  If not, 
how did they contract it?}

\p{Flexibility in trial design is important because 
the correct protocols for modeling and integrating 
both pre-treatment and post-treatment data need to be 
worked out for each trial, depending on the trial's 
goals and logistics.  Designers need to identify, 
for example, what dimensions of patients' immunological 
and sociodemographic profiles are likely to be 
consequential when analyzing treatment outcomes.  It is important for trial designers 
to model sociodemographic data attentively.  
Indeed, biomedical research has increasingly been criticized in recent years for bias
toward certain populations (e.g., white, middle-class non-seniors), leading to the 
unavoidable consequence that certain racial, age, and socioeconomic 
categories will be vastly under-represented in trial cohorts. This results in
uncertainties as to how well trial results carry over to populations at large --- 
that is, populations characterized by a heterogeneous mix of demographic factors. 
Trial designers can mitigate these concerns by demonstrating 
sociodemographic diversity among trial participants.}

\p{Demonstrating sociodemographic 
diversity, however, 
calls for transparency about how sociodemographic 
details are represented.  The process of grouping 
patients into ethnic/racial and/or socioeconomic 
strata can be equivocal at times.  For example, if a trial 
participant is a graduate student at the University of 
Chicago, should their socioeconomic status be assessed 
on the basis of their own income or that of their parents?  
If their zip code places them on 
the South Side of Chicago, a region with both a prestigious 
campus and pockets of extreme poverty, should they be 
demographically classified alongside residents 
of that neighborhood?  What about a varsity linebacker 
who appears to be in excellent health before a Covid-19 infection?  
Should his status as an athlete be taken to indicate 
being extremely fit prior to the disease, or might 
his background as a football player intimate a potential history of 
brain trauma which may compound his neurological damage due to 
Covid-19?}

\p{In short, sociodemographic data can
be notoriously imprecise. It is well-known that patients of lower socioeconomic status have higher Covid-19 infection rates and mortality rates than 
patients of higher socioeconomic status,
but this disparity may
be explained by several causal factors: more infectious workplaces, inferior post-infection treatment, poorer state of health before the onset of Covid, and so forth.  
Teasing apart these factors demands fine-grained
analysis of the individual patient's 
pre-Covid history; sociodemographic generalizations can exclude
important details. For example, for purposes of analysis, in the case of a graduate student with
middle-class parents but no health insurance of their own, how should we quantify their degree
of access to health care? How well does geographic location serve as a proxy for socioeconomic
status?}

\p{The case of a middle-class student living in a well-off near-campus corner of an otherwise
impoverished neighborhood suggests that geospatial metrics (such as zip code or congressional
district) are imperfect proxies for wealth; but other factors --- such as air/water pollution or the
risk of being the victim of a crime --- may be statistically correlated among geographically proximate
residents even if they have otherwise divergent sociological profiles.
These examples illustrate that the value of sociodemographic data is proportionate to the level
of statistical detail with which the data may be analyzed.  Instead of a broad and vague designation, such as \q{low income,} one may want 
to derive more detailed subclasses, incorporating
information about patients' employment, access to health care, physical fitness, and so forth. Two
patients with similar income levels, for instance, may have different 
levels of access to health care 
(depending
on factors such as whether the patients have employer-based insurance or geographic proximity
to healthcare facilities) or different levels of exposure to 
Covid-19 in the workplace, depending on the nature of their job.
Even if a trial does not quantify 
granular sociodemographic assessments --- such as patients' 
workplace conditions and access to health care, which might 
serve as a more accurate  
estimation of how socioeconomic status causally affects 
disease outcomes --- subsequent researchers may determine 
ways to analyze or add on to data generated by a trial (e.g., 
through follow-up studies of enrolled patients), 
so as to make such sociodemographic 
granularity part of the quantifiable framework.}

\subsubsection{Measuring Cognitive and Neurological Effects}  
\p{Similar interpretive issues of interpretation also apply to post-treatment 
observations.  How should researchers decide which observations 
qualify as clinically significant 
consequences of Covid-19?  
We have seen that as the pandemic has unfolded, 
a fair number of cases have been cited in the professional literature 
describing Covid-19 patients who suffer certain
cognitive/neurological effects, such as muscular fatigue or weakness, 
mental confusion or poor concentration (sometimes referred to as \q{brain fog}), 
or symptoms of GuillainBarr\'{e} syndrome spectrum. 
Almost certainly, some 
of these symptoms may be the product of cognitive/neurological effects due 
to SARS-CoV-2.  
At the same time, Covid-19 patients --- 
even those who fight off the infection 
successfully or who test positive but remain asymptomatic
--- may find their lives so disrupted by the pandemic 
that this may (indirectly) cause cognitive and neurological problems.
For instance, prolonged inactivity 
(for a typically active person), which commonly occurs as the result of  
a quarantine, may contribute to poor concentration and other 
diminished forms of mental acuity.  Given the fact that most 
people's lives during the pandemic are not \q{normal,} 
it may be difficult to establish 
which symptoms experienced by a patient are actually biological effects of
the disease itself or, alternatively, 
indirect consequences of  
lifestyle restrictions.  
This sort of ambiguity also applies to potential adverse 
side-effects of Covid-19 treatment.  How long after
a treatment is administered should a patient's 
symptoms be considered potential side-effects of
the therapy itself or, alternatively, the result of 
nagging uncertainties and a 
disrupted lifestyle imposed by the pandemic?}

\p{The fact that these questions have no predetermined answers indicates 
that reporting protocols, which give some structure to this kind 
of amorphous and \textit{ad hoc} patient data, need to be considered as 
an integral part of trial design.  
Specific parameters should be established for the post-treatment 
and post-recovery window of time, where patients' symptoms might be noted as 
potential effects of the disease or of the administered therapies themselves; 
moreover these symptoms should be verified and classified according to the 
trial design itself lest they could be lost altogether from the 
medical reporting process.  The methodology 
for doing so should be rigorous but also flexible, because 
it is hard to predict \textit{a priori} the range of 
patients' responses to both diseases and treatments.  For 
example, because SARS-CoV-2 was initially believed to  
affect lung functioning primarily, the risk of long-term 
cognitive/neurological damage was not widely anticipated when 
considering treatment over the course of Covid-19 infection.  
Consequently, because tests of a cognitive/neurological/physiological/radiographic 
(except for basic lung scans, with respect to radiology) 
had not been a common facet of early Covid-19 trials/observational 
studies, there were no 
corresponding data structures included in those studies for capturing this full spectrum of neuropsychological and neurological data.}

\p{Systematically tracking Covid-19's 
cognitive/neurological deficits would entail neurological, laboratory, neuropsychological and radiographic tests to understand the full extent of their cognitive and neurological impairments. For example, the use of
\MRI{}s when considering Covid-related ischemic  
stroke \cite{RossWPaterson}, \cite{FifiMocco}, 
the use of electrophysiological tests, cerebrospinal 
fluid tests (\CSF{}), or the \MRC{} 
(Medical Research Council) Scale for muscle-strength test when considering 
Covid-related 
Guillain-Barr\'{e} symptoms \cite{SamirAbuRumeileh}, 
or the use of neuropsychological tests, such as Trail Making Test 
(\TMT{}), Sign Coding Test (\SCT{}), 
Continuous Performance Test (\CPT{}), and Digital Span Test 
(\DST{}) --- which measure a patients executive abilities (letter and number recognition mental flexibility, visual scanning, and motor function) and sustained and selective attention, along with other cognitive and neurological functioning --- when considering 
cognitive/neuropsychological impairments after a serious bout with 
Covid-19 \cite{HetongZhou}.}

\p{These cognitive, neurological, physiological, laboratory, 
and radiographic data 
structures thereby become 
an integral part of the information relevant to trial evaluation, 
because they document symptoms 
which are presumptively attributable to Covid-19.  
However, in practice, prior to clinicians having been alerted to 
the fact that Covid-19 
may cause lingering cognitive/neuro\-logical damage, %physiological or neurological data 
Covid-19 trials were not designed to 
incorporate neurological or cognitive 
data in a systematic manner.  This scenario points to how 
trial data models in Covid-19 studies can benefit from 
a built-in capacity to be redesigned impromptu while the 
trial is ongoing so as to accommodate new and emerging 
information, such as debilitating cognitive or 
neurological impairment, as discussed above.}

\p{%As is seen above, the example of Covid-19 and its 
%associated neurological/cognitive damage illustrates 
%the larger point that a trial's data model should be both 
%rigorous and flexible.
The example of neurological/cognitive damage 
attributable to Covid-19 illustrates the larger point that 
clinical trials' data models should be flexible 
and suitable to become more fine-grained over time.     
%associated illustrates 
%the larger point that a trial's data model should be both 
%rigorous and flexible.  
%In fact, any trial-related data should be considered 
%a starting point for subsequent analysis, which will render the 
%data more precise and fine-grained.  What this does is augment the 
%data's value while also refining the trial's data model.
Fully accounting for all relevant observational details, such as impaired cognitive 
and neurological functioning as in the case above, may not be feasible 
during an initial analysis of trial data.  
Trial data should, therefore, be modeled within
a framework which supports the relatively free-form aggregation of new information and 
new observations (such as a graph database) rather than the rigid schema of relational 
tables \textit{ab initio}.  
In keeping with the way in which clinical data emerges in an \textit{ad hoc} way 
during the longevity of a clinical trial, 
custom \CTMS{} software would then allow each trial to expose its data models 
in a procedural, Object-Oriented fashion, using trial-specific software as a Reference Implementation illustrating how trial data is structured and 
curated.}

\subsubsection{Aggregating Trial Data via Graph Models}
\p{Consider how patient profiles usually consider the 
medications each patient is taking --- any patient (a node) could in principle be 
connected to any medication (another node); some patients 
may be taking \textit{no} medications, others may take just \textit{one}, and some may  
take \textit{two or more}.  Also, connections between patients and medications 
can be the basis of further details that emerge over time 
(and are registered in the graph) inasmuch as medications are prescribed 
to patients by a specific doctor at a specific time, in a specific 
dosage, in response to specific diagnostic tests, and so forth.  
In short, information can \q{fan out} from the patient-to-medication 
connection in a relatively free-form manner.  In general, then, as a 
subset of overall patient profiles, information about 
medication evinces the structural features which are, in many 
contexts, optimally represented via free-form labeled graphs.    
Meanwhile, patient profiles may also 
consider medical history, which can be modeled as a graph with detailed 
logical and temporal inter-node connections.  According to this 
representational strategy, each patient's history is a series of 
events and observations which are temporally ordered --- it is 
possible to query or traverse the graph in a manner which takes 
before/after relations 
into account --- and where there are also logical or causal connections 
defined between nodes.  For instance, an edge might assert that 
a given medication was prescribed to a patient (an event) \textit{because of} 
the results of a given lab test (an observation).  In these examples, different sorts of clinical data --- sociodemographic, 
pharmacological, medical-history --- are modeled according to different 
sorts of graph structures (hypernodes, nonschematic labeled edges, temporalized 
graphs, and so forth).}


\p{A useful data-integration case-study is the University of Pennsylvania's Carnival project (which achieves 
data integration by adopting property-graph databases, illustrating 
the flexibility of graph models in a way that we can 
also apply to trial design).  Carnival synthesizes heterogeneous biomedical data  
by translating information from disparate sour\-ces into a common 
property-graph representation and then querying this 
data with the Gremlin Virtual Machine.  Gremlin is a 
\q{step-based} virtual machine where \q{steps} between 
potential focus elements in a property graph play the role 
of primitive processing instructions; querying and traversing 
property graphs involves executing a series of Gremlin 
steps.\footnote{The theoretical foundations of step-based Virtual Machines 
are presented in Marko Rodriguez, 
``Stream Ring Theory,'' February 14, 2019 (\bhref{https://zenodo.org/record/2565243#.X3vzqS4pDeQ}).} 
Most Gremlin implementations are based on the Java programming language and 
the Java Virtual Machine 
(\JVM{}), so that queries 
themselves are written in a \JVM{} language (Groovy, in the 
case of Carnival).  The challenge 
for any database engine which employs a relatively complex data-representation 
strategy --- such as a hypergraph, property-graph, tuple-store (a 
collection of records with varying numbers of fields) or a multi-dimensional 
(possibly sparse) array --- is to efficiently map 
the high-level data structures manipulated within the database itself 
to the lower-level memory units which are stored to disk.  Lower-level 
data structures are typically modeled via simpler database constructions 
such as key-value stores, memory cells, or relational tables, 
so there must be a translation pipeline between high-level 
structures (properties, hypernodes, hyperedges, and so forth) and low-level   
points (record cells, shared memory address, key-value values, etc.)}


\subsection{Representing Trial Data via Object Models}
\p{As a concrete example of data-modeling principles proposed 
in the prior section, consider how the Object-Oriented models 
for Covid Phylogeny could serve as a nexus for integrating SARS-CoV-2 phylogenetic 
data across multiple studies and healthcare systems.  
Such an Object Model may be extended in different 
ways for different clinical trials examining a whole range 
of Covid-19 treatments.  For a given antibody regimen, for instance, scientists need 
to quantify how well the antibodies disable 
Covid-19 spike proteins directly and/or how well the antibodies block 
the virus's ability to attach to human cells.  These measurements 
generate data which indicate how well a patient's 
immune response to Covid-19 is boosted by the 
administered antibodies, information which is usually 
delivered in special-purpose formats such as \FCS{} or 
fluorescence images.  A Covid-19 software ecosystem 
would then need to ensure that such immune-response 
data can be effectively parsed and integrated into Object Models 
describing how SARS-CoV-2 is evolving around the 
globe.  Such data
integration modeling would allow researchers to reliably assess in each 
individual patient their immune response to the particular acquired 
SARS-CoV-2 strain/variant \visavis{} their personal immunological 
profile, and to competently track both current and 
emerging SARS-CoV-2 strains throughout the population.}


\p{These sorts of flexible Object Models can then facilitate trials designed 
according to the novel protocol proposed by Shrestha \textit{et al.}, 
discussed above, where each trial would study a 
preselected (non random) cohort of patients 
for whom both pre-treatment immunoprofiling data and post-treatment 
outcomes data would be available, so as to compare multiple trials 
against one another.  Object Models customized for each trial 
would generate a data framework through which 
the causal relations between patient profiles and treatment 
outcomes would be investigated.  Customized trial software 
would, accordingly, provide a Reference Implementation demonstrating 
each trial-specific Object Model.  If adopted for multiple trials conducted 
across multiple clinics/hospitals, trials' 
data models may help doctors better understand which 
aspects of patient profiles are particularly 
significant when matching Covid-19 patients to the most 
salutary treatment.}  


\section{Text and Data Mining via CORD-19}

\p{\noindent{}\lCnineteen{} is a collection of research articles 
about Covid-19 which was developed (starting 
in Spring 2020) in conjunction with a White 
House \q{call to action} to spur Covid-19 research.  
This White House initiative was described as a 
\q{call to action ... to develop new text and data mining techniques that can help the science community answer high-priority scientific questions related to COVID}.\footnote{See \href{https://www.whitehouse.gov/briefings-statements/call-action-tech-community-new-machine-readable-covid-19-dataset/}{https://www.whitehouse.gov/briefings-statements/call-action-tech-community-new-machine-readable-covid-19-dataset/}}  As raw data for this initiative, the US government helped  
spearhead a consortium of industry and academic 
institutions, headed by the Allen Institute for AI Research, 
who curated a \q{machine-readable Coronavirus literature collection} 
which includes article metadata and (in most cases) 
publication text  
for over 56,000 coronavirus research papers.  This 
corpus is paired with links to publisher portals 
(including Springer Nature, 
Wiley, Elsevier, the American Society for Microbiology, and the New England Journal of Medicine) providing full open access to \Covid{}-related 
literature; these resources collectively constitute 
\Cnineteen{} (the \q{Covid-19 Open Research Dataset}).}

\p{The \Cnineteen{} 
collection was formulated with the explicit goal 
of promoting both text mining and data mining solutions 
to advance coronavirus research.  This means that 
\Cnineteen{} is intended to be used both as a document 
archive for text mining and as a repository for 
finding and obtaining coronavirus data for subsequent 
research.  The White House announcement directly requests 
institutions to develop \textit{additional} technologies 
which would help scientists and jurisdictions to 
take advantage of \Cnineteen{} as it was initially 
published.  In short, \Cnineteen{} was released with the 
explicit anticipation that industry and academia would 
augment the underlying data by layering on additional 
software.}

\p{Despite the obvious benefit to researchers, the 
health-care community, and the public at large 
in publishers choosing to release a substantial 
quantity of Covid-19 related literature in 
Open-Access fashion, \Cnineteen{} is not without 
certain limitations.  These largely stem from 
how the articles are encoded into an ostensibly 
(\JSON{}-based) machine-readable format.  To be 
fair, the problems we identify here reflect the 
current authors' own personal assessments of 
the \Cnineteen{} corpus; they are not broad 
criticisms which have been asserted by researchers 
working directly with \Cnineteen{} or discussed in 
peer-reviewed literature.  With that caveat, however, 
we assert that certain issues deserve mention: 

%\vspace{-2em}
\begin{description}
	
\item[Transription Errors]  
Transcription errors can cause the machine-readable 
text archive to misrepresent the structure 
and content of documents, hindering text-mining 
technology that targets the archive.  In \Cnineteen{}, 
for instance, there are cases of scientific notation and terminology 
being improperly encoded.  As a concrete example, \colorq{2{\textquotesingle}-C-ethynyl} is encoded in \Cnineteen{} as \colorq{2 0 -C-ethynyl}, 
which could stymie text searches 
against the \Cnineteen{} corpus (see \cite{Eyer} for 
the human-readable publication where this error is 
observed; the corresponding index in the corpus is 9555f44156bc5f2c6ac191dda2fb651501a7bd7b.json).

\item[Poorly Indexed Research Data]  Although 
\Cnineteen{} provides a structured representation 
of a large collection of research 
\textit{papers}, there is no easy-to-use tool 
for finding research \textit{data} 
through \Cnineteen{}.

\item[Poorly Integrated Research Data]  The 
research data which \textit{can} be 
accessed through \Cnineteen{} evinces 
a wide variety of technical fields 
and formats, with distinct software 
requirements; as a result, it is a 
difficult task to merge and integrate 
different data sets related to 
\Covid{}.  At present, \Cnineteen{} 
does not include any software tools 
or computer code that would facilitate 
data integration.   

\item[Disconnect Between Text Data and Publisher Portals]  
Although most of the \Cnineteen{} manuscripts represent 
peer-reviewed literature which can be accessed through 
document portals (for instance, the 
National Center for Biotechnology Information website), 
the \Cnineteen{} archival schema does not represent 
these links (except indirectly via Document Object 
Identifiers).  As such, there is no easy way for 
researchers to find and read publications which have been 
flagged by text-mining algorithms as being potentially 
of interest to them.  Furthermore, there is no direct 
mechanism to enlarge the \Cnineteen{} corpus with papers 
newly added to publisher portals.
\end{description}}

\p{To clarify the final comment: the Allen Institute for AI, which 
curated \Cnineteen{}, encourages publishers to contribute new 
(or newly-available) articles to the corpus.  However, integration 
with \Cnineteen{} is not developed as a formal step 
in the publication workflow.  In particular, publishers 
are not themselves generating machine-readable document infosets 
that can be integrated with the \Cnineteen{} schema (which, 
in turn, causes transcriptions errors and other problems 
as just outlined).}



\p{With respect to text mining, an immediate problem arises 
in \Cnineteen{}'s archive-construction methodology: 
especially, how the text was parsed from \PDF{} files.  
This is a process 
which almost inevitably causes imprecise or inaccurate text representation, which can degrading the quality of 
the archive unless manual or automated corrections are made.  In particular, the \Cnineteen{} library evinces  
transcription errors, as mentioned above (especially in relation to 
technical or scientific phrases and terminology); 
scientific notation in particular may be improperly 
encoded.  Moreover, there is no 
semantic marking identifying that (say) the \colorq{2 0 -C-ethynyl} 
text segment has a specific technical meaning.  These 
errors or limitations arise in part from unavoidable 
anomalies which occur when reading texts from \PDF{} files 
rather than from machine-readable, structured 
formats such as \XML{}.}
 
\p{It is also worth observing that the \JSON{} format used 
for encoding \Cnineteen{} manuscripts presents some 
logistical challenges for any operations related to 
text-mining or to cross-referencing publications and 
data sets.  In particular, \Cnineteen{} makes 
partial use of \q{standoff annotation}; specifically, 
document features such as citations and references are 
notated through character offsets into the paragraph where 
they appear.  As a result, accurately reading these document 
elements requires synthesizing data points parsed from several 
distinct objects in the \JSON{} code, which is only feasible given 
a client library built to interface with the \Cnineteen{} files 
in accord with their specific schema.  Such a client 
library would implement convenience procedures to handle 
recurring tasks, such as obtaining the full bibliographic 
reference affixed to a given location in a manuscript.}

\p{With respect to \textit{data} mining in the \Cnineteen{} 
context, the limitations in the currently available raw 
\Cnineteen{} data are even more pronounced than in the 
context of text mining.  In particular, 
neither the article 
metadata nor the full open-access document collections have 
any mechanism for actually obtaining data published 
alongside research papers, or even identifying which papers 
have accompanying data in the first place.  The Springer 
Nature collection which was originally one component within \Cnineteen{} illustrates the limitations of this relatively unstructured 
data-publishing approach (this following analysis will 
focus on Springer Nature, but the problems identified 
are no less pronounced on the other \Cnineteen{} portals 
--- 
if anything, because Springer Nature 
allows readers to browse articles in \HTML{} within the 
web portal directly, one can ascertain whether research data 
exists for an article without downloading and reading 
it; with other \Cnineteen{} resources it is actually 
harder to locate supplemental data when available).  
Initially, the Springer Nature portal 
encompassed 43 articles, 
of which 15 were accompanied by research data that 
could be separately downloaded (this number does 
not include papers that document research 
findings only indirectly, via tables or graphics 
printed inline with the text).  Collectively 
these articles referenced over 30 distinct data 
sets (some papers were linked to multiple 
data sets), forming a data collection which could 
be a valuable resource for \Covid{} research --- 
not only through the raw data made available 
but as a kernel around which new coronavirus data 
could accumulate.  However, there is currently no 
mechanism to make this overall collection available 
as a single resource.\footnote{As \Cnineteen{} has 
evolved, the publisher-specific sections therein 
appear to be merged into portals such as 
Springer Nature directly, so our above comments 
based on isolating Springer Nature articles are 
probably more applicable to the original 
archive design than the current technology.  However, 
insofar as the current portal simply defers to 
publisher-specific search features, we would argue that 
accessing Covid-19 data sets through \Cnineteen{} 
is if anything more difficult than before.}}

\p{This problem demonstrates, among other things, 
how document-metadata formats such as 
the Research Object protocol are limited in applying 
only to \textit{single} articles.  As a result, there is no 
commensurate protocol for publishing \textit{groups} 
of articles which are tied to groups of data sets unified 
into an integral whole.  Open-access \Covid{} papers also 
reveal limitations of exiting online document portals, 
especially with respect to how publications are 
linked to data sets.  In particular, there is no clear indication that a 
given paper is associated with downloadable data; usually 
readers ascertain this information only by reading or 
scrolling down to a \q{supplemental materials} or 
\q{data availability} addendum near the end of the article.  
Moreover, because the Springer Nature portal (and similar 
publisher resources) aggregates 
papers from multiple sources, there is no consistent 
pattern for locating data sets; each journal or 
publisher has their own mechanism for alerting readers 
to the existence of open-access data and allowing them 
to download the relevant data sets.}

\subsection{Data Integration within CORD-19}
\p{Aside from the issues which are likely to hinder text and data mining 
across \Cnineteen{}, the 
collective group of \Covid{} data sets also illustrates 
the limitations of information spaces pieced 
together from disconnected raw data files with little 
additional curation.  The files included in this 
group of data sets encompass a wide array of file types 
and formats, including \FASTA{} (which stands for Fast-All, 
a genomics format), \SRA{} (Sequence Read Archive, for 
\DNA{} sequencing), \PDB{} (Protein Data Bank,  
representing the \ThreeD{} geometry of protein 
molecules), \MAP{} (Electron Microscopy Map), \EPS{} 
(Embedded Postscript), and \CSV{} (comma-separated values).  
There are also tables represented in Microsoft Word 
or Excel formats.  Although these various formats are 
reasonable for storing raw data, not all of them 
are actually machine-readable; in particular, 
the \EPS{}, Word, and Excel files need manual processing 
in order to use the information they provide in a 
computational manner.  A properly curated data collection 
would need to unify disparate sources 
into a common machine-readable representation (such as \XML{}).}

\p{Going further, productive data curation should also 
aspire to \textit{semantic} integration, unifying disparate 
sources into a common data model.  For example, multiple 
spreadsheets among the Springer Nature \Covid{} data sets 
hold sociodemographic and epidemiological information relevant 
to modeling the spread of the disease.  These different 
sources could certainly be integrated into a canonical 
social-epidemiology-based representational paradigm which 
recognizes the disparate data points which might be 
relevant for tracking the spread of \Covid{} (with the 
potential to unify data from many countries and 
jurisdictions).}

\p{This is not only an issue of data
\textit{representation} (viz., how data is physically 
laid out), but also of data types and computer code.  
According to the Research Object protocol, 
data sets should include a code base 
which provides convenient computational access to the 
published data.  In the case of \Covid{}, this entails 
creating a sociodemographic and epidemiological code 
library optimized for \Covid{} information, which would 
be the primary access point for researchers seeking to 
use the data which has been published in conjunction with 
the 43 manuscripts examined here that were aggregated 
on Springer Nature, along with any other coronavirus 
research which comes online.  Similar comments 
apply not only to tabular data represented in spreadsheet 
or \CSV{} form, but to more complex molecular or 
microscopy data that needs specialized scientific software 
to be properly visualized.}

\p{Considering the overall space of \Covid{} data, it is 
unavoidable that some files require special applications 
and cannot be directly merged with the overall collection.  
For instance, there is no coherent semantics for 
unifying Protein Data Bank files with sociodemographics 
and epidemiology; files of the former type have specific scientific 
uses and can only be understood by special-purpose software.  
Nevertheless, a well-curated data-set collection can 
make using such special-purpose data as convenient as 
possible.  In the case of Protein Data Bank, a downloadable 
\Covid{} archive can include source code for \IQmol{}, a 
molecular-visualization application that supports 
\PDB{} (among other file formats) and has few 
external dependencies (so it is relatively easy to 
build from source).}

\p{Indeed, a curated \Covid{} archive 
might include an enhanced version of software 
such as that \IQmol{} prioritizes 
\Covid{} research, with the goal of integrating biomolecular 
and social-epidemiological data as much as possible.  
For example, as \Covid{} potentially mutates in different 
ways in different geographic areas, it will be important 
to model the connections between \q{hard} scientific 
\Covid{} information and sociodemographics.  
As the pandemic evolves, genomic and biochemical information 
may be linked to particular strains of virus, which 
in turn are linked to sociodemographic profiles: certain 
strains will be more prevalent in certain populations.  
Consequently, models of \Covid{} variants will need to be 
formulated and then integrated with both chemical/molecular 
data and sociodemographic/epidemiological data.  Different 
\Covid{} strains then form a bridge linking these different 
sorts of information; researchers should be able to pass 
back and forth from molecular or genomic visualizations of 
\Covid{} to social-epidemiological charts and tables based 
on viral strains.  Ideally, capabilities for this 
sort of interdisciplinary data integration would be 
provided by a \Covid{} archive as enhancements to applications, 
such as \IQmol{}, that scientists would use to study the 
published data.}

\p{It is worth noting that a data-mining platform requires 
\textit{machine-readable} open-access research data, 
which is a more stringent requirement than simply publishing 
data alongside which can be understood by domain-specific 
software.  For example, radiological imaging can be a source 
of \Covid{} data insofar as patterns of lung 
scarring, such as \q{ground-glass opacity}, is a leading 
indicator of the disease.  Consequently, diagnostic 
images of \Covid{} patients are a relevant kind of 
content for inclusion in a \Covid{} data set 
(see \cite{Shi} as a case-study).  However, 
diagnostic images are not in themselves 
\q{machine readable.}  When medical imaging is 
used in a quantitative context (e.g., applying 
Machine Learning for diagnostic pathology), 
it is necessary to perform Image Analysis to convert the raw data 
(viz., in this case, radiological graphics) into 
quantitative aggregates (for instance by using image 
segmentation to demarcate geometric boundaries and 
then defining diagnostically relevant features, such 
as opacity, as a scalar field over the segments).  
In short, even after research data is openly published 
by article authors, it may be necessary to perform 
additional analysis on the data for it to be 
a full-fledged component of a 
machine-readable information space.\footnote{%
This does not mean that diagnostic images (or 
other graphical data) should not be placed in a 
data set; only that computational reuse of such 
data will usually involve certain numeric 
processing, such as image segmentation.  
Insofar as this subsequent analysis is performed, 
the resulting data should wherever possible 
be added to the underlying image data as a 
supplement to the data set.}} 

\p{Another concern in developing an integrated \Cnineteen{} 
data collection is that, logistically speaking, 
not all \Covid{} data is practical 
to reuse as a downloadable package.  This is especially 
true for genomics; several of the aforementioned 
43 coronavirus papers included data published via 
online data banks capable of hosting data sets that 
are too large for an ordinary computer.  In these 
situations scientists formulate queries or 
analytic scripts that are sent remotely to the online 
repositories, so that researchers access the actual 
published data only indirectly.  Nevertheless, access to 
these data sets can still be curated as part of 
a \Covid{} package; in particular, computer code 
can be provided which automates the process of 
networking with remote genomics archives through the 
accession numbers and file-formats which those archives 
recognize.}

\p{As a final point on the topic of integrating 
disparate \Cnineteen{} research data, note that 
an overarching framework for indexing \Covid{} data 
sets would also facilitate the process of cross-referencing 
article text and research data.  In particular, 
the annotation system employed for 
\Cnineteen{} could profitably be enhanced 
by a system of \textit{microcitations} that apply 
to portions of manuscripts \textit{as well as} data sets.  
In the publishing context, a microcitation is defined as a 
reference to a partially isolated fragment of a larger 
document, such as a table or figure illustration, or a 
sentence or paragraph defining a technical term, 
or (in mathematics) the statement/proof of a definition, axiom, 
or theorem.  In data publishing, \q{data citations} are 
unique references to data sets in their entirety or to 
smaller parts of data sets.  A data microcitation is then a 
fine-grained reference into a data set: for example, 
\q{the precise data records actually used in a study} (as 
defined by the Federation of Earth Science Information Partners; 
see \cite{ESIP}), 
one column in a spreadsheet, or one statistical parameter in a 
quantitative analysis.}

\p{Ideally, the text-mining and 
data-mining notions of microcitation should be combined into a unified 
framework.  In particular, text-based searches against 
the \Cnineteen{} corpus should also try to find matches in the 
data sets accompanying articles within the corpus.  As a concrete example, 
a concept such as \q{expiratory flow} appears in \Cnineteen{} 
both as a table column in research data and as a medical concept 
discussed in research papers; a unified microcitation framework 
should therefore map \textit{\color{drp}{expiratory flow}} as a keyphrase 
to both textual locations and data set parameters.  
Similarly, a concept such as 
\textit{\color{drp}{2{\textquotesingle}-C-ethynyl}} (mentioned earlier 
in the context of transcription errors) 
should be identified both as a phrase in 
article texts and as a molecular component 
present within compounds whose scientific 
properties are investigated through \Cnineteen{} 
research data, so that a search for this 
concept can trigger both publication and 
data-set matches. 
Implementing this kind of unified search mechanism requires that data 
sets be \textit{annotated} with techniques similar to 
those used for marking up Natural Language techniques.}


\p{Considering the inter-disciplinary nature of \Covid{} research, 
it is unavoidable that different scientists will need 
different sorts of specialized software to analyze the 
kinds of information relevant to their research.  For 
instance, the 
computational techniques applicable to diagnosing 
coronavirus infection are scientifically very different 
from those used for genomic or epidemiological studies 
of the disease; it is impractical to expect 
pathologists to use the same software as bioinformaticians 
studying the pathogen, or for either to use the same 
software as virologists modeling the (potential or observed) 
spread of the disease.  In short, even if 
scientists from disparate disciplines start with a 
common pool of raw data, they will need to 
analyze this data through a diverse set of 
supplemental computational tools, which will vary 
not only across disciplines but also in terms of 
the software and laboratory facilities available 
to different researchers through their institutions.  
In this sense it is impossible to unify all 
\Cnineteen{} data into a \textit{fully} self-contained 
information space.}

\p{Nevertheless, committing to \q{standalone} data publishing 
remains a valuable goal even in a context where published 
data sets will invariably migrate to different 
digital ecosystems.  Although scientists may use 
external digital tools \textit{when necessary} to 
perform certain calculations, or when interfacing with 
laboratory equipment, we strongly recommend that 
the degree of variation across different domain-specific extensions to 
\Cnineteen{} be greatly minimized.  
Ideally, that is, the version of \Cnineteen{} 
(along with its supporting technology) 
found in a biomedical setting should be as 
similar as possible to that found in a 
biochemical context, or a health-policy 
context.  In the absence of 
any initiative to limit this drift, \Cnineteen{} 
could easily devolve into a federation of 
separate resources which have no interconnection 
apart from their nominal focus on \Covid{}.}


\p{This section has highlighted limitations of data 
sets published in conjunction with coronavirus articles made 
available as open-access resources on Springer Nature 
(and, by extension, \Cnineteen{}).  
The central point here is to argue for a distinct data-curation 
stage in the publication process, with data curators 
playing a role distinct from that of both 
authors and editors.\footnote{%
The point here is not to critique the work of individual 
authors; curating data sets according to exacting 
scientific standards demands a separate vein of 
expertise which typically lies outside researchers' 
disciplinary scope.  The point is rather that 
publishers should recognize data curation as a 
distinct process and skill-set complementary 
to both writing and editing research works.}  
Moreover, the discussion has hopefully highlighted problems 
with current data-sharing paradigms, even those such 
as the Research Object and \FAIR{} initiatives which are 
explicitly devoted to improving how open-access data sets are 
published.  \Cnineteen{} exposes several 
lacunae in the Research Object protocol, for example, 
which point to the need for a more detailed extension 
of this protocol.  In particular, an enhanced protocol 
should encompass: 

\begin{enumerate}[leftmargin=3pt, itemsep=4pt,topsep=11pt]
\item{} A canonical framework for archiving collections 
of data sets, not only single data sets (and not only 
groups of data sets published with a single research 
paper).  For example, all data sets published alongside 
the 43 Springer Nature articles could be unified into a 
single collection.

\item{} A code base accompanying data-set collections 
designed to help research unify the information provided.  
Curating the overall collection would involve pooling 
disparate data into common representation, and 
implementing computer code which deserializes and processes 
the unified data accordingly.  For instance, \CSV{}, 
\EPS{}, and Microsoft Word/Excel tables could be migrated 
to \XML{}, \JSON{}, or 
a more complex common format.  Customized computer code could then 
be implemented specifically to parse and merge the 
information present in single data sets within the 
overall collection.  This implementation would 
reciprocate the Research Object goal of unifying 
code and data, but again would operate at the level 
of an aggregate of research projects rather than a 
single Research Object.

\item{}  A unified data-set collection should 
be self-contained as much as possible, and should be 
built around a foundation where advanced computing 
capabilities are available in a transparent, 
standalone fashion, without requiring tools 
outside the collection itself.  One way to 
achieve this is by gravitating 
toward components that can provide 
features such as scripting and data persistence 
through components that can be shared 
in pure source-code fashion, 
such as the WhiteDB database engine 
\cite{EnarReilent} and the AngelScript 
scripting language \cite{AS}.   

\item{}  A unified data-set collection should also provide 
prototyping and remote-access tools to interface with 
web-based information spaces that host data sets 
too large to be individually downloaded.  Ideally, 
these would include simulations of remote services, which 
would help scientists understand the design of 
the remote archives and how to interface with them.
These simulations could function analogously to 
(for instance) 
PurpleData, a prototyping tool for Google's BigData 
developed by Verily (the Alphabet subsidiary developing 
an online \Covid{} portal for remote diagnostics 
and disseminating public information about the pandemic). 

\item{}  Finally, a unified research portal should  
influence the design of the web portals where associated 
texts are published.  It should be easy for readers to 
identify which articles have supplemental data files and 
to download those files if desired.  Moreover, 
textual links should be established between publication 
content and data sets --- for instance, a plot or 
diagram illustrating statistical or equational distributions 
should link to the portion of the data set from which that 
quantitative data is derived.
\end{enumerate}}

\p{This discussion has used the \Covid{} crisis as a 
lens through which to examine data-publishing limitations 
in general.  Such limitations are not specific to coronavirus in particular.  
However, the nearly unprecedented urgency of this epidemic 
reveals how both the scientific and publishing industries are still struggling 
to develop technologies and practices which keep pace 
with the intersecting needs of systematic research 
and public policy.  An optimistic projection is 
that the crisis will spur momentum toward a more 
sophisticated data-sharing paradigm --- perhaps a 
generalization of the Research Object protocol 
toward data-set collections.}

\subsection{Reviewing the CORD-19 Document Model}

\p{In order to discuss the possibilities 
and limitations of \Cnineteen{} (and potentially 
other document corpora with a similar design) it 
is worth examining how \Cnineteen{} encodes textual 
data in greater detail.  This discussion has ramifications 
outside of \Cnineteen{} itself, 
insofar as \Cnineteen{} hopefully points to 
gaps in current publishing technologies.  These gaps need to be 
addressed if publishers are to curate open-access corpora 
which truly leverage the digital and interactive 
technology available to us with modern software.}

\p{The basis of \Cnineteen{}'s infrastructure 
is a \JSON{} scheme which describes the 
document hierarchy of research articles encoded 
within the corpus.  Apart from metadata 
(consisting of basic details such as document title and authors' 
names) and bibliographic entries, all document 
content according to this schema is divided into paragraphs 
(implicitly the documents are divided into sections 
as well, but sections are notated as properties 
of the paragraphs they contain, not as a separate 
level in the hierarchy).   
Each paragraph encoding contains an underlying string 
vector (a stream of characters) and, separate and apart from 
that, character \q{spans} which point to 
references (such as Named Entites), citations, and 
equations.  This indicates that the \Cnineteen{} encoding 
uses \q{standoff annotation,} where any content 
modifying the interpretation assigned to portions of 
the main text is notated with a series of data 
structures described apart from the main text itself.}

\p{Standoff text-encoding systems may be contrasted with \XML{} 
or \HTML{}, where \q{tags} are mixed with character 
data.  For example, consider a span of text which 
quotes from another document: in \HTML{}, the 
special status of the quoted text may be 
marked by surrounding the text with \textbf{<quote>} 
start and end tags.  Syntactically, this markup system 
has the effect that tags and text are seen side-by-side: any 
content governed by the \textbf{<quote>} (i.e., the text of 
the quote itself) is printed immediately after the 
begin-tag, and the quotation ends when the last character 
is followed by an end-tag (i.e., \textbf{</quote>}).}

\p{Apart from such syntactic details, the distinction 
between tag-based markup and standoff annotation 
determines the \q{semantics} of the document, insofar 
as tags form a document hierarchy.  Continuing the 
\textbf{<quote>} example, the text-span inside the 
quote tags is represented as a \textit{child element} 
of the quote, whereas the quote itself may be a child 
element of a larger-scale entity (such as a paragraph).  
In effect, the paragraph \textit{contains} a quote, 
and the quote \textit{contains} a string of characters.  
Such nested levels of containment provide the structure 
through which hierarchical documents (formats 
such as \XML{} and \HTML{}) are interpreted.}

\p{To see the contrast with \textit{standoff} annotation, 
if one were to describe a document using a standoff annotation 
system, the notation that a particular 
span of characters belongs to a quotation would 
not be marked-up amidst the characters themselves.  
Instead, the quotation-designation would use numeric indices to 
declare that the character at a certain position in the 
main text begins a quotation, and some later character 
in the text ends that quotation.  When serializing 
documents with standoff annotation, all the characters 
in a document are typically represented as one 
character-stream, and any notation describing markup applied 
to spans within that character stream is asserted afterward, 
using indexes into the stream to demarcate element boundaries.}

\p{The \JSON{} schema used for \Cnineteen{} is not 
entirely standoff, because there is a document hierarchy 
(for example, a publication's abstract is modeled as a sibling 
element to the main body text, so abstracts and the main text represent 
an intermediate hierarchical level, contained within the overall 
document and containing individual paragraphs).  However, 
\Cnineteen{} uses in effect a standoff-annotation system 
for each paragraph, so there is no hierarchical level 
smaller than paragraphs themselves, except implicitly; after the 
text (viz., the character stream) there are subsequent notations
of spans within the paragraph (each span description is considered 
a child of the paragraph itself, as is the paragraph text).}

\p{This arrangement has consequences for text mining algorithms, which 
may be strengths or weaknesses in different contexts.  
One consequence is that the raw text is all grouped together 
in one place --- algorithms do not have to tie together child 
nodes of disparate \XML{} elements to derive a beginning-to-end 
sequence of the text belonging to any paragraph.  Instead, it 
is simply necessary to read all data in the 
\q{text} field of the relevant \q{paragraph} 
object.  The character-sequence in this text may 
contain words and sentences, but potentially other 
strings of symbols (such as chemical formulae) 
which are not explicitly marked.  This may or may not 
be desirable.  It could potentially complicate 
\NLP{} tasks, because the language-processing 
components will be fed not only sequences of English 
words but also, sometimes interspersed among ordinary 
words, technical symbol-sequences such as 
\colorq{2{\textquotesingle}-C-ethynyl} (an 
example used earlier in this chapter).  
Standoff annotations may or may not be 
effective in marking the boundaries of such 
extra-lexical sequences; certainly we 
cannot rely on Named Entity detectors to 
properly identify and demarcate the boundaries 
of all uses of technical terminology or special 
symbols (again, the limitations of automated 
annotation are discussed earlier in this chapter).}

\p{In discussing standoff annotation it is also 
worth considering how the text of \Cnineteen{} 
publications was obtained.  According to 
\Cnineteen{} documentation, most full-text 
transcriptions in the corpus were obtained from 
\PDF{} files, via a pipeline using \TEI{} (Text 
Encoding Initiative) \XML{} as an intermediate 
representation.  Necessarily, then the 
encoded text is only an approximate representation of 
the original:  

\begin{displayquote}
To provide accessible and canonical structured full text, 
we parse content from PDFs and associated paper documents.
The full text is presented in a JSON schema designed 
to preserve most relevant paper structures 
such as paragraph breaks, section headers, and 
inline references and citations. ... We recognize that 
converting between PDF or XML to JSON is lossy.
However, the benefits of a standard structured format, 
and the ability to reuse and share annotations
made on top of that format have been critical to the
success of CORD-19. ... 
Though we have made the structured full text
of many scientific papers available to researchers
through CORD-19, a number of challenges prevent 
easy application of NLP and text mining techniques 
to these papers.  First, the primary distribution 
format of scientific papers --- PDF --- is not
amenable to text processing. The PDF file format
is designed to share electronic documents rendered
faithfully for reading and printing, not for 
automated analysis of document content.  Paper content
(text, images, bibliography) and metadata extracted
from PDF are imperfect and require significant
cleaning before they can be used for analysis.
Second, there is a clear need for more scientific
content to be made easily accessible to researchers.
Though many publishers have generously made
COVID-19 papers available during this time, there
are still bottlenecks to information access. ... 
Lastly, there is no standard format for 
representing paper metadata.  Existing schemas like 
... JATS[,] Crossref [or] Dublin Core have
been adopted as representations for paper metadata.
However, there are issues with these standards; they
can be too coarse-grained to capture all necessary
paper metadata elements, or lack a strict schema. 
... Without solutions to the above problems, NLP
on COVID-19 research and scientific research in
general will remain difficult. \cite[page 6]{LucyLuWang}
\end{displayquote}

As an example of these \NLP{} issues, 
consider the challenge of demarcating all 
named entities, particularly technical 
character-sequences (such as chemical 
formulae) which are not ordinary lexemes.  
Whether or not authors explicitly mark up 
such sequences (they may well do so in that 
formulae or equations are often typeset 
differently than normal text) this markup is 
not preserved in \PDF{} versions of articles.  
As the authors of the last-cited article point 
out, many (roughly 38\%) of papers in \Cnineteen{} 
are also available in the \JATS{} (Journal Article Tag Suite) 
format, which is a more precise text encoding 
than \PDF{}.  However, even in this context \JATS{} 
does not compel authors to explicitly notate 
textual entities such as special terms or 
character-sequences --- in fact \JATS{} 
does not truly have an obvious structure or 
set of alternative structures for identifying
what would normally be considered annotation-worthy  
text spans or named entities; the closest correlates 
are probably the generic \textbf{<kwd>} (keyword) and 
\textbf{<abbrev>} (abbreviation) tags as well 
as discipline-specific options such as 
\textbf{<chem-struct>} (for chemical structures) 
and \textbf{<disp-formula>} (for mathematical expressions).  
In short, building a corpus such as \Cnineteen{} for 
rigorous text-mining is made more difficult because 
authors and publishers do not publish texts in 
formats which are optimized for text mining in the 
first place; the acknowledged limitations of 
\Cnineteen{} reflect problems of industry 
practice, not programming lacunae that could 
be alleviated with more sophisticated \NLP{} algorithms.}

\p{Having acknowledged these limitations, a discussion of 
document corpora could then reasonably pivot from 
the empirical goal of curating useful text archives from 
currently published text to examining how more 
sophisticated corpora may be published in the future.  
It is reasonable, for example, to propose 
that full-text publications be released 
\textit{both} in reader-friendly \PDF{} form 
\textit{and} in machine-readable forms such as 
\JATS{}.  This is not just an abstract proposal; 
indeed, the text of this very book has been prepared 
using a novel document-generation system 
which creates both machine-readable structured text 
and \PDF{} output, moreover with cross-referencing 
between them; notably, the positions of discursively 
important textual markers, such as sentence boundaries, 
are mapped to \PDF{} screen coordinates (the code library 
for the book includes document-generation code as well as 
the data set of coordinate positions generated 
as part of the book's publication workflow).  
In particular, it is reasonable for authors 
and editors to manually introduce textual 
annotations for content such as named entities, 
keywords, important technical terms, and other 
content which should be targeted by \NLP{} engines 
separate and apart from ordinary lexemes with 
their conventional natural-language semantics.  
Typically such specialized terms/lexemes would 
be marked up in any case because they may require 
distinct fonts or styling than their surroundings.  
It is also reasonable to manually define sentence 
boundaries via simple rules (e.g. two following spaces 
mark the end of a sentence; a single space, such as 
that following an abbreviation, indicates situations 
where a character such as a period, which could potentially mark the 
end of a sentence, is actually playing a different discursive role).}

\p{By following simple rules of document content-entry and 
lexicography, certain \NLP{} tasks, such as sentence-boundary 
and Named Entity recognition, can be optimized --- eliminating 
the need for probabilistic algorithms and relying instead 
on much less sophisticated, but more accurate, markup-parsing 
logic.  If sentence boundaries and Named Entities are 
explicitly annotated in machine-readable text encodings, then 
extracting these features is not really an issue of 
\q{Natural Language Processing} as such.  
On the other hand, \AI{}-driven analysis of document corpora 
would still require \NLP{} for other aspects of 
parsing documents; it is unreasonable to expect authors, 
for instance, to manually notate sentence parse-graphs.  
This then suggests the question of where the boundary 
lies between discursive structures which might reasonably 
be left to authors or editors to manually notate (e.g. 
sentence boundaries) and those which in practice could 
only be obtained via \NLP{} (such as part-of-speech 
tags).  Related to this question is how best to 
model \NLP{} structures, such as the trees or graphs 
representing the syntax of natural-language sentences.  
We will consider this question in subsequent chapters 
in the context of Conceptual Space Theory.}

